---
title: " "
output:
  word_document:
    reference_docx: null
    fig_width: 6.5
    fig_height: 3.5
    toc: false
params:
  report_data: NULL
  selected_sites: "All sites"
  date_from: NULL
  date_to: NULL
  crf_csv_path: NULL
  screening_xlsx_path: NULL
  # TSC-specific user-entered fields
  meeting_date: NULL
  report_date: !r format(Sys.Date(), "%d %B %Y")
  prepared_by: ""
  reviewed_by: ""
  protocol_version: ""
  trial_summary: NULL          # named list: objectives, design, n, eligibility, interventions, primary_outcome, secondary_outcomes, funder
  general_info_overrides: NULL # named list to override any field in the General Report Information table
  funder_update: ""
  amendments_substantial: NULL     # data.frame: date, description, status
  amendments_non_substantial: NULL # data.frame: date, description, status
  custom_sections: NULL        # list of list(title, content, position) — positions: after_general_info, after_recruitment, after_screening, after_safety, end_of_report
  charts_dir: NULL             # directory containing pre-rendered PNGs (optional; otherwise rendered on the fly)
  completeness_style: "heatmap" # "heatmap", "flat", or "both"
  completeness_rate: "pct_expected" # "pct_due" or "pct_expected"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(knitr)
library(dplyr)
library(flextable)
library(officer)

# ── Consistent typography across the whole report ────────────────────────────
# Forces every flextable to render in Arial and removes the mixed font issue
# that happens when Word substitutes Aptos/Calibri for unspecified runs.
# Also sets consistent line spacing and padding on every table.
flextable::set_flextable_defaults(
  font.family    = "Arial",
  font.size      = 10,
  padding.top    = 4,
  padding.bottom = 4,
  padding.left   = 5,
  padding.right  = 5,
  line_spacing   = 1.15,
  text.align     = "left",
  border.color   = "#BFBFBF"
)

# Load shared flat completeness helper (copied alongside Rmd by reports_server)
if (file.exists("flat_completeness.R")) source("flat_completeness.R")

rd  <- params$report_data
kpi <- if(!is.null(rd$kpis)) rd$kpis else list()

# Safe accessor: NULL / length-0 → fallback
safe <- function(x, fallback = "") if (is.null(x) || length(x) == 0) fallback else x

# Render charts if not pre-supplied
if (is.null(params$charts_dir)) {
  # Try a few likely locations for tsc_charts.R (robust to folder layout)
  charts_script_candidates <- c(
    "tsc_charts.R",                                                         # cwd
    file.path(dirname(knitr::current_input(dir = TRUE)), "tsc_charts.R"),   # same folder as Rmd
    file.path(dirname(knitr::current_input(dir = TRUE)), "..", "tsc_charts.R") # parent (e.g. Rmd in rmd/, script at top level)
  )
  charts_script <- charts_script_candidates[file.exists(charts_script_candidates)][1]
  if (is.na(charts_script)) stop("Could not locate tsc_charts.R. Tried: ",
                                 paste(charts_script_candidates, collapse = ", "))
  source(charts_script, local = FALSE)
  charts <- render_all_tsc_charts(rd)
} else {
  charts <- list(
    cumulative = file.path(params$charts_dir, "cumulative.png"),
    monthly    = file.path(params$charts_dir, "monthly.png"),
    site       = file.path(params$charts_dir, "site.png"),
    open_sites = file.path(params$charts_dir, "open_sites.png")
  )
}

# Helper to insert custom sections at a given anchor
render_custom_sections <- function(position) {
  cs <- params$custom_sections
  if (is.null(cs) || length(cs) == 0) return(invisible(NULL))
  for (s in cs) {
    if (!is.null(s$position) && s$position == position &&
        !is.null(s$title) && nzchar(s$title)) {
      # Render as a proper second-level heading so it fits the document style
      cat("\n\n## ", s$title, "\n\n", sep = "")
      # Support simple paragraph breaks — split on double newline
      content <- s$content %||% ""
      if (nzchar(content)) {
        parts <- strsplit(content, "\n\n", fixed = TRUE)[[1]]
        for (p in parts) {
          # Preserve single-line breaks within a paragraph as hard breaks
          cat(p, "\n\n", sep = "")
        }
      }
    }
  }
}
`%||%` <- function(a, b) if (is.null(a)) b else a

# Flextable helpers — produce proper Word tables that handle multi-paragraph cells
# and look like the template (navy header band, bordered, readable).

tonic_navy_ft <- "#1B4F6B"

# Two-column label:value table. Renders multi-paragraph values correctly.
kv_table <- function(rows, label_width = 2.2, value_width = 4.0,
                     header_row = NULL) {
  df <- data.frame(
    Field = names(rows),
    Value = vapply(rows, function(x) {
      if (is.null(x) || length(x) == 0) ""
      else if (is.character(x) && !nzchar(x)) ""
      else as.character(x)
    }, character(1)),
    stringsAsFactors = FALSE
  )
  ft <- flextable(df)
  ft <- set_header_labels(ft, Field = "", Value = "")
  ft <- delete_part(ft, part = "header")  # no column headers for key:value tables
  if (!is.null(header_row)) {
    # Add a single merged header row at the top with the supplied label
    ft <- add_header_row(ft, values = header_row, colwidths = 2)
    ft <- bg(ft, part = "header", bg = tonic_navy_ft)
    ft <- color(ft, part = "header", color = "white")
    ft <- bold(ft, part = "header")
    ft <- align(ft, part = "header", align = "left")
    ft <- fontsize(ft, part = "header", size = 11)
    ft <- padding(ft, part = "header", padding = 6)
  }
  ft <- bold(ft, j = 1, part = "body")
  ft <- bg(ft, j = 1, bg = "#F1F5F9", part = "body")
  ft <- color(ft, j = 1, color = tonic_navy_ft, part = "body")
  ft <- border_outer(ft, border = fp_border(color = "#CBD5E1", width = 0.5))
  ft <- border_inner(ft, border = fp_border(color = "#E2E8F0", width = 0.5))
  ft <- fontsize(ft, size = 10, part = "body")
  ft <- padding(ft, padding = 5, part = "body")
  ft <- width(ft, j = 1, width = label_width)
  ft <- width(ft, j = 2, width = value_width)
  ft <- valign(ft, valign = "top", part = "body")
  # Convert \n in the Value column into proper line breaks inside cells
  for (i in seq_len(nrow(df))) {
    if (grepl("\n", df$Value[i], fixed = TRUE)) {
      parts <- strsplit(df$Value[i], "\n", fixed = TRUE)[[1]]
      # Interleave chunks with hard line breaks
      chunks <- list()
      for (k in seq_along(parts)) {
        chunks[[length(chunks) + 1]] <- as_chunk(parts[k])
        if (k < length(parts)) {
          chunks[[length(chunks) + 1]] <- as_chunk("\n")  # flextable renders \n as soft break
        }
      }
      ft <- compose(ft, i = i, j = 2, value = do.call(as_paragraph, chunks))
    }
  }
  ft
}

# Render a generic data.frame as a Word table with TONIC styling
tonic_ft <- function(df, widths = NULL) {
  ft <- flextable(df)
  ft <- bg(ft, part = "header", bg = tonic_navy_ft)
  ft <- color(ft, part = "header", color = "white")
  ft <- bold(ft, part = "header")
  ft <- fontsize(ft, part = "header", size = 10)
  ft <- fontsize(ft, part = "body", size = 10)
  ft <- border_outer(ft, border = fp_border(color = "#CBD5E1", width = 0.5))
  ft <- border_inner(ft, border = fp_border(color = "#E2E8F0", width = 0.5))
  ft <- padding(ft, padding = 5)
  ft <- valign(ft, valign = "top", part = "body")
  if (!is.null(widths)) {
    for (i in seq_along(widths)) ft <- width(ft, j = i, width = widths[i])
  } else {
    ft <- autofit(ft)
  }
  ft
}

# Empty-state placeholder: a bordered one-column box explaining that
# the section is to be completed manually. Looks much better than an
# empty markdown table followed by italic text.
manual_placeholder <- function(columns, message, widths = NULL) {
  # Show headers for the columns that would be filled, then a single
  # italicised row saying what's missing. This signals intent: "here's
  # where X goes" rather than "nothing here".
  df <- as.data.frame(
    setNames(
      lapply(columns, function(c) ""),
      columns
    ),
    stringsAsFactors = FALSE
  )
  df[1, 1] <- message  # inject message into first cell
  ft <- flextable(df)
  ft <- bg(ft, part = "header", bg = tonic_navy_ft)
  ft <- color(ft, part = "header", color = "white")
  ft <- bold(ft, part = "header")
  ft <- fontsize(ft, part = "header", size = 10)
  ft <- padding(ft, part = "header", padding = 5)
  if (length(columns) > 1) {
    ft <- merge_h(ft, i = 1, part = "body")
  }
  ft <- italic(ft, part = "body")
  ft <- color(ft, color = "#6b7c8d", part = "body")
  ft <- fontsize(ft, size = 10, part = "body")
  ft <- padding(ft, part = "body", padding = 8)
  ft <- align(ft, part = "body", align = "left")
  ft <- border_outer(ft, border = fp_border(color = "#CBD5E1", width = 0.5))
  ft <- border_inner(ft, border = fp_border(color = "#E2E8F0", width = 0.5))
  if (!is.null(widths)) {
    for (i in seq_along(widths)) ft <- width(ft, j = i, width = widths[i])
  } else {
    # Distribute 6.5" evenly across columns
    w <- 6.5 / length(columns)
    for (i in seq_along(columns)) ft <- width(ft, j = i, width = w)
  }
  ft
}

# Heatmap-style table for per-site per-month recruitment — cells
# colour-coded by how the actual compares to the monthly target.
hm_ft <- function(hm) {
  months_u <- unique(hm$month_label[order(hm$month)])
  sites_u  <- unique(hm$site_name)
  wide <- data.frame(Site = sites_u, stringsAsFactors = FALSE)
  # Also capture monthly_target per site for colour decisions
  targets <- sapply(sites_u, function(s) {
    r <- hm[hm$site_name == s, ]
    if (nrow(r) > 0) r$monthly_target[1] else 2
  })
  # Raw numeric matrix for colour logic (parallel to wide)
  num_mat <- matrix(NA_integer_, nrow = length(sites_u), ncol = length(months_u))
  colnames(num_mat) <- months_u
  rownames(num_mat) <- sites_u
  for (m in months_u) {
    vals <- sapply(sites_u, function(s) {
      r <- hm[hm$site_name == s & hm$month_label == m, ]
      if (nrow(r) > 0) as.integer(r$actual[1]) else NA_integer_
    })
    wide[[m]] <- ifelse(is.na(vals), "\u2014", as.character(vals))
    num_mat[, m] <- vals
  }

  ft <- flextable(wide)
  ft <- bg(ft, part = "header", bg = tonic_navy_ft)
  ft <- color(ft, part = "header", color = "white")
  ft <- bold(ft, part = "header")
  ft <- fontsize(ft, part = "header", size = 9)
  ft <- padding(ft, part = "header", padding = 4)
  ft <- align(ft, j = 2:ncol(wide), part = "all", align = "center")
  ft <- bold(ft, j = 1, part = "body")
  ft <- color(ft, j = 1, color = tonic_navy_ft, part = "body")
  ft <- fontsize(ft, part = "body", size = 9)
  ft <- padding(ft, part = "body", padding = 4)
  ft <- border_outer(ft, border = fp_border(color = "#CBD5E1", width = 0.5))
  ft <- border_inner(ft, border = fp_border(color = "#E2E8F0", width = 0.5))
  ft <- width(ft, j = 1, width = 2.0)
  per_mo <- (6.5 - 2.0) / length(months_u)
  for (k in seq_along(months_u)) ft <- width(ft, j = k + 1, width = per_mo)

  # Colour cells per (site, month) vs monthly target
  for (i in seq_along(sites_u)) {
    for (k in seq_along(months_u)) {
      v <- num_mat[i, k]
      tgt <- targets[i]
      bg_col <- if (is.na(v)) "#F8FAFC"
                else if (v >= tgt) "#D4F5EC"
                else if (v > 0)    "#FEF3DC"
                else               "#FDE8E8"
      fg_col <- if (is.na(v)) "#CBD5E1"
                else if (v >= tgt) "#0F6E56"
                else if (v > 0)    "#8A5A0D"
                else               "#991B1B"
      ft <- bg(ft, i = i, j = k + 1, bg = bg_col, part = "body")
      ft <- color(ft, i = i, j = k + 1, color = fg_col, part = "body")
    }
  }
  ft
}
```

```{r cover-page}
# Cover page rendered as a borderless flextable spanning full width.
# Word respects this reliably; raw HTML tags don't render in Word output.
cover_df <- data.frame(
  x = c(
    "[Trial logo]",
    "TONIC",
    "A randomised trial comparing early parenteral nutrition vs standard nutritional care in adults undergoing emergency laparotomy.",
    "Trial Registration: ISRCTN 59200516 · IRAS 328678",
    "",
    "Trial Steering Committee Report"
  ),
  stringsAsFactors = FALSE
)

cover_ft <- flextable(cover_df) |>
  delete_part(part = "header") |>
  align(align = "center", part = "body") |>
  border_remove() |>
  width(j = 1, width = 6.5) |>
  padding(padding = 4, part = "body")

# Row-specific styling
cover_ft <- color(cover_ft, i = 1, color = "#94A3B8")          # logo placeholder muted
cover_ft <- fontsize(cover_ft, i = 1, size = 10)

cover_ft <- bold(cover_ft, i = 2)                              # TONIC title
cover_ft <- color(cover_ft, i = 2, color = tonic_navy_ft)
cover_ft <- fontsize(cover_ft, i = 2, size = 40)
cover_ft <- padding(cover_ft, i = 2, padding.top = 18, padding.bottom = 10)

cover_ft <- bold(cover_ft, i = 3)                              # full trial title
cover_ft <- fontsize(cover_ft, i = 3, size = 14)
cover_ft <- color(cover_ft, i = 3, color = "#2C3E50")
cover_ft <- padding(cover_ft, i = 3, padding = 6)

cover_ft <- fontsize(cover_ft, i = 4, size = 11)               # registration
cover_ft <- color(cover_ft, i = 4, color = "#6b7c8d")

cover_ft <- bold(cover_ft, i = 6)                              # TSC Report subtitle
cover_ft <- color(cover_ft, i = 6, color = tonic_navy_ft)
cover_ft <- fontsize(cover_ft, i = 6, size = 22)
cover_ft <- padding(cover_ft, i = 6, padding.top = 16, padding.bottom = 20)

cover_ft
```

```{r cover-meta}
kv_table(list(
  `Date of TSC Meeting` = if (!is.null(params$meeting_date)) format(as.Date(params$meeting_date), "%d %B %Y") else "",
  `Date of Report`      = params$report_date,
  `Report prepared by`  = params$prepared_by,
  `Report reviewed by`  = params$reviewed_by
))
```

\newpage

# Table of Contents

1. Trial Summary
2. General Report Information
3. Recruitment Details
4. Flow diagram of participants
5. Screening data
6. Data Completeness
7. Protocol Deviations
8. Safety
9. Pilot Progress Criteria
10. Summary of Amendments

\newpage

# 1. Trial Summary

```{r trial-summary}
ts <- params$trial_summary
if (is.null(ts)) ts <- list()
kv_table(
  list(
    Objectives                    = safe(ts$objectives),
    `Trial design`                = safe(ts$design),
    `Total number of participants`= safe(ts$n_participants, as.character(safe(kpi$trial_target, "898"))),
    `Eligibility criteria`        = safe(ts$eligibility),
    Interventions                 = safe(ts$interventions),
    `Primary outcome measure`     = safe(ts$primary_outcome),
    `Secondary outcome measures`  = safe(ts$secondary_outcomes),
    Funder                        = safe(ts$funder, "National Institute for Health and Care Research, Health Technology Assessment Programme (NIHR \u2013 HTA) \u2014 NIHR155875")
  ),
  header_row = "TONIC Trial"
)
```

**Figure 1: Trial schema**

*[Trial schema figure to be inserted manually if required]*

\newpage

# 2. General Report Information

```{r general-info}
gi <- if (is.null(params$general_info_overrides)) list() else params$general_info_overrides
total_rand <- safe(kpi$total_randomised, 0)
trial_tgt  <- safe(kpi$trial_target, 898)
pct_rec    <- if (is.numeric(trial_tgt) && trial_tgt > 0 && is.numeric(total_rand))
              sprintf("%.1f%%", 100 * as.numeric(total_rand) / as.numeric(trial_tgt)) else "—"

kv_table(list(
  `Start date of Grant`                  = safe(gi$grant_start,       "01 June 2024"),
  `End date of Grant`                    = safe(gi$grant_end,         "28 February 2028"),
  `Date trial opened to recruitment`     = safe(gi$recruitment_open,  "01 April 2026"),
  `Date first participant was randomised`= safe(gi$first_randomised,  "01 April 2026"),
  `End date for the pilot phase`         = safe(gi$pilot_end,         "September 2026"),
  `Current end date for recruitment`     = safe(gi$recruitment_end,   "June 2028"),
  `Number of participants randomised`    = as.character(total_rand),
  `% Target recruitment`                 = sprintf("%s (of %s planned)", pct_rec, trial_tgt),
  `Protocol version number`              = safe(params$protocol_version, "—")
))
```

**Figure 1a: Project timeline**

```{r fig-gantt}
if (!is.null(charts$gantt) && file.exists(charts$gantt)) {
  knitr::include_graphics(charts$gantt)
}
```

**Table 1a: Progress against original protocol schedule**

```{r schedule-drift}
# Original protocol planned recruitment to open Mar 2025.
# Actual open date from params (default 01 Apr 2026).
# Show drift context so TSC can see the full history.
actual_open_str <- safe(gi$recruitment_open, "01 April 2026")
actual_first_str <- safe(gi$first_randomised, "01 April 2026")
actual_open  <- tryCatch(as.Date(actual_open_str,  format = "%d %B %Y"), error = function(e) NA_Date_)
actual_first <- tryCatch(as.Date(actual_first_str, format = "%d %B %Y"), error = function(e) NA_Date_)
today <- Sys.Date()

planned_open  <- as.Date("2025-03-01")   # original protocol planned open
planned_first <- as.Date("2025-03-01")

months_behind_open  <- if (!is.na(actual_open))
  round(as.numeric(difftime(actual_open, planned_open, units = "days")) / 30.44, 1) else NA
months_behind_first <- if (!is.na(actual_first))
  round(as.numeric(difftime(actual_first, planned_first, units = "days")) / 30.44, 1) else NA

# Months elapsed in recruitment so far (against original plan)
planned_months_elapsed <- round(as.numeric(difftime(today, planned_open, units = "days")) / 30.44, 1)
actual_months_elapsed  <- if (!is.na(actual_open))
  round(as.numeric(difftime(today, actual_open, units = "days")) / 30.44, 1) else NA

drift_tbl <- data.frame(
  Milestone = c("Recruitment opens",
                "First participant randomised",
                "Months elapsed in recruitment"),
  `Original protocol` = c(format(planned_open, "%b %Y"),
                           format(planned_first, "%b %Y"),
                           sprintf("%s months", planned_months_elapsed)),
  `Actual` = c(if (!is.na(actual_open))  format(actual_open,  "%b %Y") else "\u2014",
               if (!is.na(actual_first)) format(actual_first, "%b %Y") else "\u2014",
               if (!is.na(actual_months_elapsed)) sprintf("%s months", actual_months_elapsed) else "\u2014"),
  `Variance` = c(
    if (!is.na(months_behind_open))  sprintf("%.1f months behind", months_behind_open)  else "\u2014",
    if (!is.na(months_behind_first)) sprintf("%.1f months behind", months_behind_first) else "\u2014",
    if (!is.na(actual_months_elapsed)) sprintf("%.1f months less", planned_months_elapsed - actual_months_elapsed) else "\u2014"
  ),
  check.names = FALSE, stringsAsFactors = FALSE
)

ft <- tonic_ft(drift_tbl, widths = c(2.5, 1.4, 1.4, 1.2))
ft <- align(ft, j = 2:4, align = "center", part = "all")
# Highlight variance column in amber/red where negative drift
for (i in seq_len(nrow(drift_tbl))) {
  v <- drift_tbl$Variance[i]
  col <- if (grepl("behind|less", v)) "#D97706" else "#0F6E56"
  ft <- color(ft, i = i, j = 4, color = col, part = "body")
  ft <- bold(ft, i = i, j = 4, part = "body")
}
ft
```

```{r custom-after-general}
render_custom_sections("after_general_info")
```

`r if (nzchar(safe(params$funder_update))) paste0("# Funder Update \u2013 Extension request\n\n", params$funder_update, "\n")`

\newpage

# 3. Recruitment Details

**Table 1: Projected site/recruitment figures vs actual**

```{r recruitment-summary-table}
sf <- rd$schedule_full
if (!is.null(sf) && nrow(sf) > 0) {
  cur <- as.Date(format(Sys.Date(), "%Y-%m-01"))

  # Show ALL months of the protocol schedule so the TSC/DMC can see
  # monthly targets across the full recruitment window. Past months show
  # both target and actual; future months show target only with actuals
  # blanked.
  full <- sf
  is_future <- full$month_date > cur

  monthly_actual <- full$monthly_actual
  cum_actual     <- full$cumulative_actual
  monthly_actual[is_future] <- NA
  cum_actual[is_future]     <- NA

  pct_vs_target <- ifelse(
    !is_future & full$cumulative_target > 0,
    paste0(round(100 * cum_actual / full$cumulative_target), "%"),
    "\u2014"
  )

  # Display helpers — dashes instead of NAs for future rows
  ma_disp <- ifelse(is.na(monthly_actual), "\u2014", as.character(monthly_actual))
  ca_disp <- ifelse(is.na(cum_actual),     "\u2014", as.character(cum_actual))

  rec_tbl <- data.frame(
    Month           = full$month_label,
    `Monthly target`= full$monthly_target,
    `Cum. target`   = full$cumulative_target,
    `Monthly actual`= ma_disp,
    `Cum. actual`   = ca_disp,
    `% vs target`   = pct_vs_target,
    check.names = FALSE, stringsAsFactors = FALSE
  )
  ft <- tonic_ft(rec_tbl, widths = c(1.1, 0.9, 0.9, 1.0, 0.9, 1.7))
  ft <- align(ft, j = 2:6, align = "center", part = "all")

  # Highlight the current month
  current_row <- which(full$month_date == cur)
  if (length(current_row) > 0) {
    ft <- bg(ft, i = current_row, bg = "#E6F9F5", part = "body")
    ft <- bold(ft, i = current_row, part = "body")
  }

  # De-emphasise future rows
  future_rows <- which(is_future)
  if (length(future_rows) > 0) {
    ft <- color(ft, i = future_rows, color = "#94A3B8", part = "body")
  }

  ft
} else {
  cat("*Recruitment schedule data not available.*")
}
```

**Figure 2: Projected recruitment vs actual recruitment**

```{r fig-cumulative}
if (!is.null(charts$cumulative) && file.exists(charts$cumulative)) {
  knitr::include_graphics(charts$cumulative)
}
```

**Figure 3: Projected open centres vs actual open centres**

```{r fig-open-sites}
if (!is.null(charts$open_sites) && file.exists(charts$open_sites)) {
  knitr::include_graphics(charts$open_sites)
}
```

**Table 1b: Projected vs actual open centres by month**

```{r centres-open-table}
sf <- rd$schedule_full
sites_df <- rd$site_status

if (!is.null(sf) && nrow(sf) > 0) {
  cur <- as.Date(format(Sys.Date(), "%Y-%m-01"))

  # Projected open centres per month: defined in the protocol schedule.
  # We assume sf has a column called target_open_sites OR site_target;
  # fall back to deriving from monthly_target if neither exists.
  proj_col <- NULL
  for (cand in c("target_open_sites", "site_target", "projected_sites", "open_sites_target")) {
    if (cand %in% names(sf)) { proj_col <- cand; break }
  }
  projected_open <- if (!is.null(proj_col)) sf[[proj_col]] else {
    # Fallback: ramp 2 new sites per month until 24, derived from protocol pattern
    pmin(24L, cumsum(rep(2L, nrow(sf))))
  }

  # Actual open centres per month: sites the REDCap export knows about
  # (site_status$in_redcap) whose open date is on or before each month, minus
  # any that have closed or withdrawn. Set-up sites typed into the Sites tab
  # carry an open date but no trial data, and counting them overstated how
  # many centres were really open.
  actual_open <- rep(NA_integer_, nrow(sf))
  open_col <- if (is.null(sites_df)) NA_character_ else
    intersect(c("open_date", "site_open_date"), names(sites_df))[1]
  if (!is.null(sites_df) && nrow(sites_df) > 0 && !is.na(open_col)) {
    keep <- rep(TRUE, nrow(sites_df))
    if ("in_redcap" %in% names(sites_df))
      keep <- keep & !is.na(sites_df$in_redcap) & sites_df$in_redcap
    stage_col <- intersect(c("stage", "status"), names(sites_df))[1]
    if (!is.na(stage_col))
      keep <- keep & !grepl("closed|withdrawn", as.character(sites_df[[stage_col]]),
                            ignore.case = TRUE)
    sod <- suppressWarnings(as.Date(sites_df[[open_col]][keep]))
    for (i in seq_len(nrow(sf))) {
      if (sf$month_date[i] <= cur) {
        actual_open[i] <- sum(!is.na(sod) & sod <= sf$month_date[i])
      }
    }
  }

  is_future <- sf$month_date > cur
  ao_disp <- ifelse(is.na(actual_open), "\u2014", as.character(actual_open))
  var_disp <- ifelse(is.na(actual_open), "\u2014",
                     as.character(actual_open - projected_open))

  centres_tbl <- data.frame(
    Month                 = sf$month_label,
    `Projected open centres`= projected_open,
    `Actual open centres` = ao_disp,
    `Variance`            = var_disp,
    check.names = FALSE, stringsAsFactors = FALSE
  )
  ft <- tonic_ft(centres_tbl, widths = c(1.1, 1.6, 1.6, 1.0))
  ft <- align(ft, j = 2:4, align = "center", part = "all")

  current_row <- which(sf$month_date == cur)
  if (length(current_row) > 0) {
    ft <- bg(ft, i = current_row, bg = "#E6F9F5", part = "body")
    ft <- bold(ft, i = current_row, part = "body")
  }
  future_rows <- which(is_future)
  if (length(future_rows) > 0) {
    ft <- color(ft, i = future_rows, color = "#94A3B8", part = "body")
  }

  ft
} else {
  cat("*Site-opening schedule not available.*")
}
```

\newpage

**Table 2: Recruitment per site**

```{r recruitment-site-summary}
# Site / Date site opened / Date first patient randomised / Number randomised
# \u2014 one row per recruiting site. prepare_report_data() builds this from the
# Sites register scoped to the centres the REDCap export knows about, so the
# table shows the sites that have actually recruited rather than every site
# ever typed into the Sites tab.
site_tbl <- rd$open_sites

# Fallback for report data built before open_sites carried the first
# randomisation date: rebuild from the site status table and site summary.
if (is.null(site_tbl) || !nrow(site_tbl) || !"first_rand_date" %in% names(site_tbl)) {
  st <- rd$site_status
  if (!is.null(st) && nrow(st) > 0) {
    keep <- rep(TRUE, nrow(st))
    if ("in_redcap" %in% names(st)) keep <- keep & !is.na(st$in_redcap) & st$in_redcap
    if ("randomisations" %in% names(st)) keep <- keep & st$randomisations > 0
    st <- st[keep, , drop = FALSE]
    site_tbl <- data.frame(
      site_name      = st$site_name,
      open_date      = if ("open_date" %in% names(st)) st$open_date else NA_character_,
      first_rand_date = as.Date(NA),
      randomisations = if ("randomisations" %in% names(st)) st$randomisations else 0L,
      stringsAsFactors = FALSE)
    ss <- rd$site_summary
    if (!is.null(ss) && nrow(ss) > 0 && "first_rand_date" %in% names(ss)) {
      idx <- match(site_tbl$site_name, ss$site_name)
      site_tbl$first_rand_date <- as.Date(ss$first_rand_date[idx])
    }
  } else site_tbl <- NULL
}

if (is.null(site_tbl) || nrow(site_tbl) == 0) {
  manual_placeholder(
    c("Site", "Date site opened", "Date first patient randomised",
      "Number of patients randomised"),
    "No recruiting sites from the REDCap export to summarise.",
    widths = c(2.6, 1.4, 1.8, 1.2)
  )
} else {
  n_rands <- as.integer(site_tbl$randomisations)
  n_rands[is.na(n_rands)] <- 0L
  ord <- order(-n_rands, site_tbl$site_name)

  fmt_date <- function(d) {
    d <- suppressWarnings(as.Date(d))
    ifelse(is.na(d), "\u2014", format(d, "%d %b %Y"))
  }

  out <- data.frame(
    `Site`                          = site_tbl$site_name[ord],
    `Date site opened`              = fmt_date(site_tbl$open_date[ord]),
    `Date first patient randomised` = fmt_date(site_tbl$first_rand_date[ord]),
    `Number of patients randomised` = n_rands[ord],
    check.names = FALSE, stringsAsFactors = FALSE
  )

  # Total row
  out <- rbind(
    out,
    data.frame(
      `Site` = "Total",
      `Date site opened` = "",
      `Date first patient randomised` = "",
      `Number of patients randomised` = as.integer(sum(n_rands)),
      check.names = FALSE, stringsAsFactors = FALSE
    )
  )

  ft <- tonic_ft(out, widths = c(2.6, 1.4, 1.8, 1.2))
  ft <- align(ft, j = 2:4, align = "center", part = "all")
  ft <- bold(ft, i = nrow(out), part = "body")
  ft <- bg(ft,   i = nrow(out), bg = "#F4F6F8", part = "body")
  ft
}
```

**Figure 5: Randomisations by site vs monthly target**

```{r fig-site-recruitment}
if (!is.null(charts$site) && file.exists(charts$site)) {
  knitr::include_graphics(charts$site)
}
```

**Figure 6: Monthly recruitment**

```{r fig-monthly}
if (!is.null(charts$monthly) && file.exists(charts$monthly)) {
  knitr::include_graphics(charts$monthly)
}
```

```{r custom-after-recruitment}
render_custom_sections("after_recruitment")
```

\newpage

# 4. Flow diagram of participants

**Figure 4: CONSORT flow diagram**

```{r consort-diagram}
# Source the CONSORT builder (robust to folder layout)
consort_script_candidates <- c(
  "consort_flow.R",
  file.path(dirname(knitr::current_input(dir = TRUE)), "consort_flow.R"),
  file.path(dirname(knitr::current_input(dir = TRUE)), "..", "consort_flow.R"),
  file.path(dirname(knitr::current_input(dir = TRUE)), "..", "functions", "consort_flow.R")
)
consort_script <- consort_script_candidates[file.exists(consort_script_candidates)][1]
if (!is.na(consort_script)) {
  source(consort_script, local = FALSE)
  counts <- consort_counts(rd, screening_xlsx_path = params$screening_xlsx_path)
  consort_png_path <- tempfile(fileext = ".png")
  consort_png(counts, filepath = consort_png_path, width = 6.5, height = 8)
  knitr::include_graphics(consort_png_path)
} else {
  cat("*CONSORT flow diagram builder not found \u2014 add consort_flow.R to the app directory.*")
}
```

\newpage

# 5. Baseline characteristics

Participant characteristics at baseline, including the three minimisation variables used during randomisation and key demographic measures.

```{r baseline-characteristics-table, results='asis'}
# The app stages baseline_table.R beside the Rmd; a render driven from the
# repo (scripts/render_report.R) may leave it in functions/. Look in the same
# places the CONSORT chunk does rather than assuming the working directory,
# and say what went wrong instead of dropping the table silently.
bt_candidates <- c(
  "baseline_table.R",
  file.path(dirname(knitr::current_input(dir = TRUE)), "baseline_table.R"),
  file.path(dirname(knitr::current_input(dir = TRUE)), "..", "baseline_table.R"),
  file.path(dirname(knitr::current_input(dir = TRUE)), "..", "functions", "baseline_table.R")
)
bt_script <- bt_candidates[file.exists(bt_candidates)][1]

if (is.na(bt_script)) {
  cat("*Baseline characteristics builder not found \u2014 add baseline_table.R to the app directory.*\n\n")
} else {
  source(bt_script, local = FALSE)
  bl_df <- tryCatch(baseline_characteristics_df(rd), error = function(e) e)
  if (inherits(bl_df, "error")) {
    cat("*Baseline characteristics could not be built: ", conditionMessage(bl_df),
        ".*\n\n", sep = "")
  } else if (nrow(bl_df) > 0) {
    cat(knitr::knit_print(baseline_characteristics_flextable(bl_df)))
    cat("\n\n")
  } else {
    cat("*No baseline characteristics recorded for the participants in this report.*\n\n")
  }
}
```

\newpage

# 6. Screening data

Tables 3–5 break down the various reasons for exclusion during the different stages of the screening process.

**Table 3: Reason for the patient not being eligible for TONIC**

```{r screening-ineligible}
manual_placeholder(
  c("Reason for ineligibility", "N"),
  "Screening ineligibility data to be completed manually \u2014 not currently collected in REDCap.",
  widths = c(5.0, 1.5)
)
```

**Table 4: Reason the patient was not given the TONIC PIS**

```{r screening-no-pis}
manual_placeholder(
  c("Reason PIS not given", "N"),
  "Not currently collected in REDCap \u2014 to be completed manually.",
  widths = c(5.0, 1.5)
)
```

**Table 5: Reason patient was not randomised**

```{r screening-not-rand}
manual_placeholder(
  c("Reason not randomised", "N"),
  "Not currently collected in REDCap \u2014 to be completed manually.",
  widths = c(5.0, 1.5)
)
```

**Table 6: Reasons for participant withdrawal**

```{r withdrawals}
wd <- rd$withdrawals
if (!is.null(wd) && !is.null(wd$log) && nrow(wd$log) > 0) {
  wd_df <- wd$log
  # Default the log has columns (site_name, cos_label). Rename for display
  # and add a blank Reason column for the report author to populate manually
  # (free-text reason isn't currently captured in REDCap in a structured form).
  if (ncol(wd_df) >= 2) {
    names(wd_df)[1:2] <- c("Site", "Type")
  }
  wd_df$Reason <- ""   # blank — complete by hand before sharing

  tonic_ft(wd_df[, c("Site", "Type", "Reason")],
           widths = c(2.0, 1.8, 2.7))
} else {
  manual_placeholder(
    c("Site", "Type", "Reason"),
    "No withdrawals to date.",
    widths = c(2.0, 1.8, 2.7)
  )
}
```

```{r custom-after-screening}
render_custom_sections("after_screening")
```

\newpage

# 7. Data Completeness

**Table 7: Site completed CRF return rates**

```{r crf-rates}
crf <- rd$crf_data
po  <- rd$primary_outcome

# --- Primary outcome banner (always show if calculable) ------------------
if (!is.null(po)) {
  po_elig <- safe(po$eligible, 0)
  po_comp <- safe(po$complete, 0)
  po_pct  <- safe(po$pct, NA)
  thresh  <- safe(po$threshold_days, 7)
  pct_display <- if (is.na(po_pct) || po_elig == 0) "\u2014" else paste0(po_pct, "%")

  po_df <- data.frame(
    x = sprintf(
      "Primary outcome completeness (discharge form complete, op date + %s days \u2264 today): %s of %s eligible (%s)",
      thresh, po_comp, po_elig, pct_display
    ),
    stringsAsFactors = FALSE
  )
  po_ft <- flextable(po_df) |>
    delete_part(part = "header") |>
    bg(bg = "#E6F9F5", part = "body") |>
    color(color = tonic_navy_ft, part = "body") |>
    bold(part = "body") |>
    fontsize(size = 11, part = "body") |>
    padding(padding = 8, part = "body") |>
    border_outer(border = fp_border(color = "#2EC4A5", width = 1.5)) |>
    width(j = 1, width = 6.5) |>
    align(align = "left", part = "body")
  knit_print(po_ft)
}
```

```{r crf-rates-table, results='asis'}
if (!is.null(crf) && nrow(crf) > 0) {
  to_num <- function(x) suppressWarnings(as.numeric(gsub("%", "", as.character(x))))

  show_heatmap <- params$completeness_style %in% c("heatmap", "both")
  show_flat    <- params$completeness_style %in% c("flat",    "both")

  # Helper: render a flextable into Word output correctly regardless of
  # whether we're being knitted by rmarkdown or called directly. Uses
  # knit_print() so that docx_value / xml is emitted in-flow.
  render_ft <- function(ft) {
    cat(knitr::knit_print(ft))
    cat("\n\n")
  }

  if (show_heatmap) {
    crf_tbl <- data.frame(
      Event    = crf$Event,
      Form     = crf$Form,
      Expected = crf$Expected,
      Due      = crf$Due,
      Entered  = crf$Entered,
      `% Expected entered` = sapply(seq_len(nrow(crf)), function(i) {
        ex <- to_num(crf$Expected[i]); en <- to_num(crf$Entered[i])
        if (!is.na(ex) && ex > 0 && !is.na(en)) paste0(round(en / ex * 100, 1), "%") else "\u2014"
      }),
      check.names = FALSE, stringsAsFactors = FALSE
    )
    cat("\n\n**Table \u2014 CRF return rate (by event)**\n\n")
    render_ft(tonic_ft(crf_tbl, widths = c(0.9, 1.8, 0.7, 0.6, 0.7, 1.2)))
  }

  if (show_flat) {
    cat("\n\n**Table \u2014 CRF return rate (flat, protocol forms)**\n\n")
    flat_df <- flat_completeness_df(crf, rate_type = params$completeness_rate)
    render_ft(flat_completeness_flextable(flat_df, rate_type = params$completeness_rate))
    cat("*Rows marked \u2014 are forms listed in the protocol that are not yet in the current data export.*\n\n")
  }

} else {
  cat("*CRF return rate data not available.*\n\n")
  cat("*Ensure a return rates CSV is placed in `return rates/` (in the app directory) and that `crf_csv_path` is passed to `prepare_report_data()`.*")
}
```

# 8. Protocol Deviations

**Table 8: Summary of protocol deviations**

```{r deviations}
# Deviations come from prepare_report_data(): deviation_log is the per-event
# table the Data tab drills into, deviation_count its size, and
# deviation_available says whether the export carries a deviation form at all
# \u2014 so "none reported" reads differently from "not collected here".
dev_log <- rd$deviation_log
dev_n   <- if (!is.null(rd$deviation_count)) {
  as.integer(rd$deviation_count)
} else if (!is.null(dev_log)) nrow(dev_log) else 0L
dev_has_form <- !identical(rd$deviation_available, FALSE)

banner <- function(txt) {
  ft <- flextable(data.frame(x = txt, stringsAsFactors = FALSE)) |>
    delete_part(part = "header") |>
    bg(bg = "#FEF3DC", part = "body") |>
    color(color = "#8A5A0D", part = "body") |>
    bold(part = "body") |>
    fontsize(size = 11, part = "body") |>
    padding(padding = 8, part = "body") |>
    border_outer(border = fp_border(color = "#D97706", width = 1.5)) |>
    width(j = 1, width = 6.5) |>
    align(align = "left", part = "body")
  knit_print(ft)
}

if (dev_n == 0 || is.null(dev_log) || nrow(dev_log) == 0) {
  banner(if (dev_has_form)
           "Total protocol deviations reported to date: 0. No deviation details to summarise."
         else
           "This export carries no protocol deviation form, so no deviations can be summarised.")
} else {
  # Coded values (deviation type) arrive already translated through the trial's
  # codebook, so the table shows words rather than REDCap's numbers.
  col <- function(nm) if (nm %in% names(dev_log)) as.character(dev_log[[nm]]) else rep(NA_character_, nrow(dev_log))
  fmt_d <- function(x) {
    d <- suppressWarnings(as.Date(x))
    ifelse(is.na(d), "\u2014", format(d, "%d %b %Y"))
  }
  blank <- function(x) ifelse(is.na(x) | !nzchar(trimws(x)), "\u2014", trimws(x))

  descr <- col("narrative")
  term  <- col("term")
  descr <- ifelse(is.na(descr) | !nzchar(trimws(descr)), term, descr)

  dev_disp <- data.frame(
    `Participant` = blank(col("record_id")),
    `Date`        = fmt_d(col("onset_date")),
    `Site`        = blank(col("site")),
    `Description` = blank(descr),
    `Category`    = blank(col("category")),
    `Action`      = blank(col("action")),
    check.names = FALSE, stringsAsFactors = FALSE
  )

  banner(sprintf("Total protocol deviations reported to date: %d", dev_n))
  cat("\n\n")
  tonic_ft(dev_disp, widths = c(0.8, 0.9, 1.1, 1.6, 1.3, 0.8))
}
```

# 9. Safety

**Table 9: Summary of SAEs**

```{r safety}
safety <- rd$safety_summary
sae_n  <- safe(kpi$sae_count, 0)
if (!is.null(safety) && nrow(safety) > 0) {
  # Summary banner + table
  banner_df <- data.frame(
    x = sprintf("Total SAEs reported to date: %s", sae_n),
    stringsAsFactors = FALSE
  )
  banner_ft <- flextable(banner_df) |>
    delete_part(part = "header") |>
    bg(bg = "#FEF3DC", part = "body") |>
    color(color = "#8A5A0D", part = "body") |>
    bold(part = "body") |>
    fontsize(size = 11, part = "body") |>
    padding(padding = 8, part = "body") |>
    border_outer(border = fp_border(color = "#D97706", width = 1.5)) |>
    width(j = 1, width = 6.5) |>
    align(align = "left", part = "body")
  knit_print(banner_ft)
  cat("\n\n")
  tonic_ft(safety)
} else {
  manual_placeholder(
    c("Status"),
    sprintf("Total SAEs reported to date: %s. No SAE details to summarise.", sae_n),
    widths = c(6.5)
  )
}
```

```{r custom-after-safety}
render_custom_sections("after_safety")
```

\newpage

# 10. Pilot Progress Criteria

**Table 10: Pilot Progression Criteria**

```{r pilot-criteria}
pt <- if (!is.null(rd$pilot)) rd$pilot else list()
fmt_pct <- function(x) if (is.null(x) || length(x) == 0 || is.na(x)) "Not yet due" else paste0(x, "%")
rag_label <- function(s) {
  if (is.null(s) || length(s) == 0 || is.na(s)) return("Not yet due")
  switch(s,
         green = "GREEN — on track",
         amber = "AMBER — review",
         red   = "RED — action required",
         not_yet_due = "Not yet due",
         small_n = "AMBER (small n)",
         "—")
}
# Determine RAG for recruitment
rr_s <- {
  v <- safe(pt$recruit_rate, NA)
  if (is.na(v)) "not_yet_due" else if (v >= 100) "green" else if (v >= 60) "amber" else "red"
}
ri_s <- {
  v <- safe(pt$interv_rate, NA)
  if (is.na(v)) "not_yet_due" else if (v >= 100) "green" else if (v >= 75) "amber" else "red"
}
rc_s <- {
  v <- safe(pt$contam_rate, NA)
  if (is.na(v)) "not_yet_due" else if (v == 0) "green" else if (v < 25) "amber" else "red"
}
rx_s <- {
  v <- safe(pt$crossover_rate, NA)
  if (is.na(v)) "not_yet_due" else if (v == 0) "green" else if (v < 10) "amber" else "red"
}

pilot_tbl <- data.frame(
  Criterion = c("01 Recruitment rate", "02 Data completeness", "03 90-day questionnaire",
                "04 Intervention delivery", "05 Contamination", "06 Crossover rate"),
  Red      = c("<60%", "<90%", "<70%", "\u226470%", "\u226530%", "\u226510%"),
  Amber    = c("60\u201399%", "90\u201399%", "70\u201399%", "71\u201399%", "1\u201329%", "1\u20139%"),
  Green    = c("100%", "100%", "100%", "100%", "0%", "0%"),
  Current  = c(fmt_pct(safe(pt$recruit_rate, NA)), "96%",
               fmt_pct(safe(pt$fu_90_rate, NA)),
               fmt_pct(safe(pt$interv_rate, NA)),
               fmt_pct(safe(pt$contam_rate, NA)),
               fmt_pct(safe(pt$crossover_rate, NA))),
  Status   = c(rag_label(rr_s), rag_label("amber"),
               rag_label(safe(pt$fu_90_status, "not_yet_due")),
               rag_label(ri_s), rag_label(rc_s), rag_label(rx_s)),
  check.names = FALSE, stringsAsFactors = FALSE
)

# RAG codes per row (aligned with Status column text)
rag_codes <- c(rr_s, "amber", safe(pt$fu_90_status, "not_yet_due"), ri_s, rc_s, rx_s)
rag_bg    <- vapply(rag_codes, function(s) switch(s,
  green = "#D4F5EC", amber = "#FEF3DC", red = "#FDE8E8",
  not_yet_due = "#F1F5F9", small_n = "#FEF3DC", "#F1F5F9"), character(1))
rag_fg    <- vapply(rag_codes, function(s) switch(s,
  green = "#0F6E56", amber = "#8A5A0D", red = "#991B1B",
  not_yet_due = "#64748B", small_n = "#8A5A0D", "#64748B"), character(1))
current_fg <- vapply(rag_codes, function(s) switch(s,
  green = "#0F6E56", amber = "#D97706", red = "#C0392B",
  not_yet_due = "#64748B", small_n = "#D97706", "#64748B"), character(1))

pilot_ft <- flextable(pilot_tbl) |>
  bg(part = "header", bg = tonic_navy_ft) |>
  color(part = "header", color = "white") |>
  bold(part = "header") |>
  fontsize(part = "header", size = 10) |>
  padding(part = "header", padding = 7) |>
  align(part = "header", align = "center") |>
  align(j = 1, align = "left", part = "all") |>
  fontsize(part = "body", size = 10) |>
  padding(part = "body", padding = 5) |>
  align(j = 2:6, align = "center", part = "body") |>
  border_outer(border = fp_border(color = "#CBD5E1", width = 0.5)) |>
  border_inner(border = fp_border(color = "#E2E8F0", width = 0.5)) |>
  width(j = 1, width = 1.9) |>
  width(j = 2, width = 0.65) |>
  width(j = 3, width = 0.75) |>
  width(j = 4, width = 0.65) |>
  width(j = 5, width = 1.0) |>
  width(j = 6, width = 1.55) |>
  bold(j = 1, part = "body") |>
  color(j = 1, color = tonic_navy_ft, part = "body")

# Colour the Current column numbers
for (i in seq_len(nrow(pilot_tbl))) {
  pilot_ft <- color(pilot_ft, i = i, j = 5, color = current_fg[i], part = "body")
  pilot_ft <- bold(pilot_ft, i = i, j = 5, part = "body")
  # Status pill: coloured background + coloured text
  pilot_ft <- bg(pilot_ft, i = i, j = 6, bg = rag_bg[i], part = "body")
  pilot_ft <- color(pilot_ft, i = i, j = 6, color = rag_fg[i], part = "body")
  pilot_ft <- bold(pilot_ft, i = i, j = 6, part = "body")
}

pilot_ft
```

```{r pilot-guide}
# Decision guide banner underneath the pilot table
guide_df <- data.frame(
  x = paste0(
    "Decision guide \u2014 ",
    "GREEN: all criteria met, proceed. ",
    "AMBER: partially met, review and modify. ",
    "RED: not met, consider stopping."
  ),
  stringsAsFactors = FALSE
)
flextable(guide_df) |>
  delete_part(part = "header") |>
  bg(bg = "#E8F0F5", part = "body") |>
  color(color = tonic_navy_ft, part = "body") |>
  fontsize(size = 9, part = "body") |>
  padding(padding = 7, part = "body") |>
  border_outer(border = fp_border(color = tonic_navy_ft, width = 1)) |>
  width(j = 1, width = 6.5) |>
  align(align = "left", part = "body")
```

\newpage

# 10. Summary of Amendments

**Table 11: Summary of Substantial Amendments**

```{r amendments-sub}
amd <- params$amendments_substantial
if (!is.null(amd) && is.data.frame(amd) && nrow(amd) > 0) {
  names(amd) <- c("Date", "Description", "Status")
  tonic_ft(amd, widths = c(1.0, 4.5, 1.0))
} else {
  manual_placeholder(
    c("Date", "Description", "Status"),
    "No substantial amendments entered.",
    widths = c(1.0, 4.5, 1.0)
  )
}
```

**Table 12: Summary of Non-Substantial Amendments**

```{r amendments-nonsub}
amd2 <- params$amendments_non_substantial
if (!is.null(amd2) && is.data.frame(amd2) && nrow(amd2) > 0) {
  names(amd2) <- c("Date", "Description", "Status")
  tonic_ft(amd2, widths = c(1.0, 4.5, 1.0))
} else {
  manual_placeholder(
    c("Date", "Description", "Status"),
    "No non-substantial amendments entered.",
    widths = c(1.0, 4.5, 1.0)
  )
}
```

```{r custom-end-of-report}
render_custom_sections("end_of_report")
```

---

*TONIC TSC Report · Birmingham Clinical Trials Unit · `r params$report_date`*
