---
title: "TONIC TMG Progress Report"
output:
  html_document:
    theme: null
    highlight: null
    mathjax: null
    self_contained: true
    md_extensions: "-markdown_in_html_blocks"
params:
  report_data: NULL
  selected_sites: "All sites"
  date_from: NULL
  date_to: NULL
  include_withdrawn: false
  include_appendix: false
  report_date: !r format(Sys.Date(), "%d %B %Y")
  logo_path: NULL
  nihr_logo_path: NULL
  crf_csv_path: NULL
  screening_xlsx_path: NULL
  report_type: "TMG"
  completeness_style: "heatmap"
  report_content: NULL
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, warning=FALSE, message=FALSE, results="asis")
library(dplyr)
`%||%` <- function(a, b) if (is.null(a) || length(a) == 0) b else a
safe <- function(x, fallback = NA) if (is.null(x) || length(x) == 0) fallback else x
esc  <- function(s) htmltools::htmlEscape(as.character(s))
fmt_pct <- function(x, dp = 0) if (is.null(x) || length(x) == 0 || is.na(x)) "—" else
  paste0(formatC(x, format = "f", digits = dp), "%")
fmt_int <- function(x) if (is.null(x) || length(x) == 0 || is.na(x)) "—" else
  format(as.integer(x), big.mark = ",")
fmt_date <- function(d, f = "%b %Y") {
  d <- suppressWarnings(as.Date(d))
  if (is.na(d)) "—" else format(d, f)
}

rd <- params$report_data %||% list()
rc <- params$report_content %||% list()
kpi <- rd$kpis %||% list()
pilot <- rd$pilot %||% list()
demo  <- rd$demographics %||% list()
wd    <- rd$withdrawals %||% list(n = 0, rate = 0, log = NULL)
wd_log <- wd$log
n_wd   <- if (!is.null(wd_log) && nrow(wd_log) > 0) nrow(wd_log) else safe(wd$n, 0)
wd_reason_col <- intersect(
  c("reason", "wd_reason", "withdrawal_reason", "reason_text", "cos_label"),
  names(wd_log)
)[1]

# ── Trial identity / project meta ─────────────────────────────────────────────
trial_short  <- safe(rc$short_name,    "TONIC")
trial_title  <- safe(rc$trial_title,   "Timing Of Nutrition In emergenCy laparotomy")
chief_inv    <- safe(rc$ci,            "Mr Matthew Lee")
sponsor      <- safe(rc$sponsor,       "University of Birmingham")
funder       <- safe(rc$funder,        "NIHR HTA")
funder_ref   <- safe(rc$funder_ref,    "NIHR155875")
isrctn       <- safe(rc$isrctn,        "ISRCTN59200516")
sample_size  <- safe(rc$sample_size,   safe(kpi$trial_target, 898))
n_sites_plan <- safe(rc$sites_planned, 25)
proj_start   <- safe(rc$project_start, "Apr 2026")
proj_end     <- safe(rc$project_end,   "Feb 2028")
proj_months  <- safe(rc$project_months, 45)
pilot_target <- safe(rc$pilot_target,  60)
pilot_end    <- safe(rc$pilot_end,     "Sep 2026")
full_end     <- safe(rc$full_recruitment_end, "Jun 2028")

report_date_str <- params$report_date %||% format(Sys.Date(), "%d %B %Y")
rep_from <- safe(rc$reporting_period_start, "01 May 2025")
rep_to   <- format(Sys.Date(), "%d %b %Y")

# ── Logos (base64) ────────────────────────────────────────────────────────────
encode_logo <- function(path) {
  if (is.null(path) || !nzchar(path) || !file.exists(path) ||
      !requireNamespace("base64enc", quietly = TRUE)) return("")
  ext  <- tolower(tools::file_ext(path))
  mime <- switch(ext, png = "image/png", jpg = "image/jpeg", jpeg = "image/jpeg",
                 svg = "image/svg+xml", "image/png")
  tryCatch(
    paste0("data:", mime, ";base64,", base64enc::base64encode(path)),
    error = function(e) "")
}

logo_b64      <- encode_logo(params$logo_path)
# BCTU brand logo. The report knits in a temp intermediates_dir, so the plain
# "www/..." path (relative to the app root) won't resolve here — reports_server
# stages the file alongside the Rmd, so try that first, then fall back to the
# in-place app paths for when the report is knitted directly.
.bctu_candidates <- c(
  "BlackText-landscape.png",                                                  # staged next to the Rmd
  file.path("www", "BlackText-landscape.png"),                                # app root (in-place render)
  file.path(dirname(knitr::current_input(dir = TRUE)), "BlackText-landscape.png")
)
.bctu_hit     <- .bctu_candidates[file.exists(.bctu_candidates)]
bctu_logo_b64 <- if (length(.bctu_hit)) encode_logo(.bctu_hit[1]) else ""
# NIHR "Funded by" logo — same staging logic as the BCTU mark, with an
# optional explicit param override.
.nihr_candidates <- c(
  params$nihr_logo_path %||% "",
  "NIHR_Acknowledgement_Funded by_Logo_RGB.png",
  file.path("www", "NIHR_Acknowledgement_Funded by_Logo_RGB.png"),
  file.path(dirname(knitr::current_input(dir = TRUE)), "NIHR_Acknowledgement_Funded by_Logo_RGB.png")
)
.nihr_candidates <- .nihr_candidates[nzchar(.nihr_candidates)]
.nihr_hit     <- .nihr_candidates[file.exists(.nihr_candidates)]
nihr_logo_b64 <- if (length(.nihr_hit)) encode_logo(.nihr_hit[1]) else ""

# ── Snapshot KPIs ─────────────────────────────────────────────────────────────
n_rand    <- safe(kpi$total_randomised, 0)
n_target  <- safe(kpi$trial_target, sample_size)
n_sites_active <- safe(kpi$n_sites_active, 0)
exp_to_date    <- safe(kpi$expected_to_date, 0)
rec_pct        <- safe(kpi$recruitment_pct, NA)
sae_count      <- safe(kpi$sae_count, 0)
pilot_pct      <- if (!is.na(pilot_target) && pilot_target > 0)
                    round(n_rand / pilot_target * 100, 1) else NA
pct_of_target  <- if (!is.na(n_target) && n_target > 0)
                    round(n_rand / n_target * 100, 1) else NA
# Recruitment-rate pilot card: the percentage is derived from the exact
# numbers shown inside the box (randomised ÷ expected to date), so the value
# and its caption can never disagree.
recruit_rate_box <- if (!is.na(exp_to_date) && exp_to_date > 0)
                      round(n_rand / exp_to_date * 100, 1) else
                      safe(pilot$recruit_rate, NA)

# Site bucketing from pipeline / site_status
pipeline <- rd$pipeline %||% data.frame()
site_status <- rd$site_status %||% data.frame()
is_open <- function(s) grepl("recruit", tolower(s)) | grepl("^open", tolower(s))
is_setup <- function(s) grepl("set[- ]?up", tolower(s)) | grepl("capacity", tolower(s))
is_ident <- function(s) grepl("identif", tolower(s)) | grepl("feasib", tolower(s))

n_open_sites  <- if (nrow(pipeline) && "stage" %in% names(pipeline))
                   sum(is_open(pipeline$stage), na.rm = TRUE) else n_sites_active
n_setup_sites <- if (nrow(pipeline) && "stage" %in% names(pipeline))
                   sum(is_setup(pipeline$stage), na.rm = TRUE) else 0
n_ident_sites <- if (nrow(pipeline) && "stage" %in% names(pipeline))
                   sum(is_ident(pipeline$stage), na.rm = TRUE) else 0
n_sites_total <- n_open_sites + n_setup_sites + n_ident_sites
if (n_sites_total == 0) n_sites_total <- safe(n_sites_plan, 0)

# Recruitment colour band
rec_band <- if (is.na(rec_pct)) "amber" else
  if (rec_pct >= 95) "green" else if (rec_pct >= 70) "amber" else "red"

# Pilot criterion colour helper (status → green/amber/red/none)
crit_class <- function(status) switch(as.character(status),
  green = "g", amber = "a", red = "r", "n")
crit_label <- function(status) switch(as.character(status),
  green = "GREEN", amber = "AMBER", red = "RED", "PENDING")

# ── Milestones ────────────────────────────────────────────────────────────────
# rc$key_milestones is a list of lists: list(name=, date=, status= "complete"|"upcoming"|"estimated", group=)
ms <- rc$key_milestones %||% list(
  list(name = "Grant activation", date = "Jun 2024", status = "complete", group = "Set-up & trial activation"),
  list(name = "REC favourable opinion (E&W) — 25/0268, Essex", date = "14 Jan 2026", status = "complete", group = "Set-up & trial activation"),
  list(name = "HRA / HCRW approval", date = "16 Jan 2026", status = "complete", group = "Set-up & trial activation"),
  list(name = "Protocol v2 finalised", date = "14 Feb 2026", status = "complete", group = "Set-up & trial activation"),
  list(name = "REC favourable opinion (Scotland) — 26/SS/0001, Scotland A", date = "06 Mar 2026", status = "complete", group = "Set-up & trial activation"),
  list(name = "First site opened", date = "01 Apr 2026", status = "complete", group = "Set-up & trial activation"),
  list(name = "First participant randomised", date = "01 Apr 2026", status = "complete", group = "Set-up & trial activation"),
  list(name = "Pilot end (6-month)",   date = pilot_end,    status = "upcoming",  group = "Pilot · recruitment · close-out"),
  list(name = "Full recruitment end",  date = full_end,     status = "estimated", group = "Pilot · recruitment · close-out"),
  list(name = "Follow-up complete",    date = "Sep 2028",   status = "estimated", group = "Pilot · recruitment · close-out"),
  list(name = "Database lock",         date = "Nov 2028",   status = "estimated", group = "Pilot · recruitment · close-out"),
  list(name = "Analysis complete",     date = "Jan 2029",   status = "estimated", group = "Pilot · recruitment · close-out"),
  list(name = "Trial close-out",       date = "Feb 2029",   status = "estimated", group = "Pilot · recruitment · close-out")
)
ms_complete <- Filter(function(m) identical(m$status, "complete"),  ms)
ms_future   <- Filter(function(m) !identical(m$status, "complete"), ms)
next_ms_lbl <- if (length(ms_future) > 0) {
  sprintf("%d of %d complete · next: %s · %s",
          length(ms_complete), length(ms), ms_future[[1]]$name, ms_future[[1]]$date)
} else {
  sprintf("%d of %d complete", length(ms_complete), length(ms))
}

# CRF return rates — derive a tidy stage summary if crf_data is present
crf <- rd$crf_data
crf_overall_pct <- NA_real_
crf_stage_rows  <- NULL
if (!is.null(crf) && nrow(crf) > 0) {
  # Use whatever columns exist; common shape: Forms, Expected, Due, Entered, Pct
  guess <- function(pat) {
    m <- grep(pat, names(crf), ignore.case = TRUE, value = TRUE)
    if (length(m)) crf[[m[1]]] else NULL
  }
  st <- list(
    event    = guess("^(event|timepoint|time.?point|visit)"),
    stage    = guess("^(stage|form|instrument)"),
    forms    = guess("^forms$|^count"),
    expected = guess("expected"),
    due      = guess("^due"),
    entered  = guess("entered|received"),
    pct      = guess("pct|%|percent")
  )
  if (!is.null(st$stage)) {
    n_rows <- length(st$stage)
    crf_stage_rows <- data.frame(
      event    = if (!is.null(st$event)) as.character(st$event) else rep(NA_character_, n_rows),
      stage    = as.character(st$stage),
      forms    = if (!is.null(st$forms))    as.integer(st$forms)    else rep(NA_integer_, n_rows),
      expected = if (!is.null(st$expected)) as.integer(st$expected) else rep(NA_integer_, n_rows),
      due      = if (!is.null(st$due))      as.integer(st$due)      else rep(NA_integer_, n_rows),
      entered  = if (!is.null(st$entered))  as.integer(st$entered)  else rep(NA_integer_, n_rows),
      stringsAsFactors = FALSE)

    # Return rate is entered ÷ DUE, never ÷ expected. TONIC is longitudinal
    # (Baseline, Discharge, Day 30, Day 90); "expected" counts participants who
    # will eventually reach a timepoint, so windows that have not yet opened
    # (e.g. Day 90, 0 due) would otherwise deflate the figure. Rows with 0 due
    # are "not yet due" and contribute nothing to the denominator.
    #
    # Numerator is capped at due (min(entered, due)) so that early entries —
    # forms submitted before the formal due window fires — cannot inflate the
    # rate above 100%. e.g. Barthel Discharge: 12 entered, 10 due → 100%, not 120%.
    crf_stage_rows$pct <- ifelse(crf_stage_rows$due > 0,
                                 pmin(crf_stage_rows$entered, crf_stage_rows$due) /
                                   crf_stage_rows$due * 100,
                                 NA_real_)

    # Order timepoints chronologically when an event column is present
    if (!all(is.na(crf_stage_rows$event))) {
      tp_levels <- c("Baseline", "Discharge", "Day 30", "Day 90")
      crf_stage_rows$event <- factor(crf_stage_rows$event,
                                     levels = union(tp_levels, unique(crf_stage_rows$event)))
      crf_stage_rows <- crf_stage_rows[order(crf_stage_rows$event), , drop = FALSE]
    }

    # Overall rate: cap entered at due per row before summing so aggregate
    # cannot exceed 100% either.
    tot_due <- sum(crf_stage_rows$due, na.rm = TRUE)
    tot_ent <- sum(pmin(crf_stage_rows$entered, crf_stage_rows$due), na.rm = TRUE)
    crf_overall_pct <- if (tot_due > 0) round(tot_ent / tot_due * 100, 1) else NA
  }
}

# 90-day questionnaire return — same source and logic as the return-rates
# table: denominator = forms due in the Day 90 window, numerator = forms
# entered (capped at due so early entries cannot push the rate above 100%).
d90_rows <- if (!is.null(crf_stage_rows) && !all(is.na(crf_stage_rows$event)))
  crf_stage_rows[grepl("90", as.character(crf_stage_rows$event)) &
                 !grepl("30", as.character(crf_stage_rows$event)), , drop = FALSE] else NULL
fu90_due     <- if (!is.null(d90_rows) && nrow(d90_rows) > 0) sum(d90_rows$due, na.rm = TRUE) else 0
fu90_entered <- if (!is.null(d90_rows) && nrow(d90_rows) > 0)
  sum(pmin(d90_rows$entered, d90_rows$due), na.rm = TRUE) else 0
fu90_rate_csv <- if (fu90_due > 0) round(fu90_entered / fu90_due * 100, 1) else NA_real_

# ── Pilot thresholds (criteria text + bands) ──────────────────────────────────
thr <- rc$pilot_thresholds %||% list(
  list(name = "Recruitment rate per open centre",
       det  = "Average of 2 participants per month at each open site during the pilot.",
       stop_lbl = "< 60% of sites at rate", mod_lbl = "60 – 99% of sites at rate",
       go_lbl   = "100% of sites at rate"),
  list(name = "Primary-outcome data completeness",
       det  = "Discharge forms entered as a proportion of discharge forms due — same forms-due logic as the CRF return rates by timepoint & form.",
       stop_lbl = "< 90% complete", mod_lbl = "90 – 99% complete",
       go_lbl   = "100% complete"),
  list(name = "90-day questionnaire return rate",
       det  = "Proportion of due 90-day post-op questionnaires returned by participants.",
       stop_lbl = "< 70% returned", mod_lbl = "70 – 99% returned",
       go_lbl   = "100% returned"),
  list(name = "Intervention delivery — intervention arm",
       det  = "Early parenteral-nutrition started within 48 hours of randomisation, intervention-arm participants.",
       stop_lbl = "< 70% within 48 h", mod_lbl = "75 – 99% within 48 h",
       go_lbl   = "100% within 48 h"),
  list(name = "Contamination — control arm",
       det  = "Control-arm participants who actually received early parenteral nutrition within 48 hours.",
       stop_lbl = "≥ 30% contaminated", mod_lbl = "1 – 25% contaminated",
       go_lbl   = "0% contaminated"),
  list(name = "Cross-over between trial arms",
       det  = "Participants randomised to one arm who instead received the other arm's intervention.",
       stop_lbl = "> 10% crossed over", mod_lbl = "1 – 9% crossed over",
       go_lbl   = "0% crossed over")
)

# Map current values onto each threshold band (stop|mod|go|NA)
band_for <- function(idx) {
  v <- switch(idx,
    recruit_rate_box,   # 1 — same figure as shown in the card (n randomised ÷ expected)
    NA,                  # 2 data completeness — we approximate below
    fu90_rate_csv,       # 3 — from the return-rates CSV (entered ÷ due)
    NA_real_,            # 4 — not derivable: REDCap export lacks the data (see pc_cards)
    pilot$contam_rate,   # 5
    pilot$crossover_rate # 6
  )
  if (idx == 2) {
    po <- rd$primary_outcome %||% list()
    v  <- po$pct
  }
  if (is.null(v) || is.na(v)) return(list(band = NA_character_, val = NA))
  band <- switch(idx,
    if (v < 60)   "stop" else if (v < 100) "mod" else "go",     # 1
    if (v < 90)   "stop" else if (v < 100) "mod" else "go",     # 2
    if (v < 70)   "stop" else if (v < 100) "mod" else "go",     # 3
    if (v < 75)   "stop" else if (v < 100) "mod" else "go",     # 4
    if (v >= 30)  "stop" else if (v >= 1)  "mod" else "go",     # 5
    if (v > 10)   "stop" else if (v >= 1)  "mod" else "go"      # 6
  )
  list(band = band, val = v)
}

# Pilot criteria — six cards on page 1
pc_cards <- list(
  list(title = "Recruitment rate",            val = recruit_rate_box,     sub = sprintf("%s / %s expected", fmt_int(n_rand), fmt_int(exp_to_date)), fmt = "pct"),
  list(title = "Data completeness",           val = (rd$primary_outcome %||% list())$pct, sub = "primary outcome forms", fmt = "pct"),
  # Denominator and numerator come from the return-rates CSV (Day 90 rows),
  # matching the CRF return-rates table: entered ÷ due.
  list(title = "90-day questionnaire return", val = fu90_rate_csv,        sub = if (fu90_due == 0) "not yet due" else sprintf("%s / %s due", fmt_int(fu90_entered), fmt_int(fu90_due)), fmt = "pct"),
  # The REDCap export does not carry the data needed to derive intervention
  # delivery (no allocation field; PN timing incomplete), so this criterion is
  # shown as pending with an explanatory caption rather than a misleading 0%.
  list(title = "Intervention delivery <48 h", val = NA_real_,             sub = "cannot be calculated from the REDCap export", fmt = "pct"),
  list(title = "Contamination",               val = pilot$contam_rate,    sub = "target 0% in control", fmt = "pct"),
  list(title = "Crossover rate",              val = pilot$crossover_rate, sub = "target 0%", fmt = "pct")
)

# Map a value to GREEN/AMBER/RED status using the same rules as the bands
status_for_card <- function(i, v) {
  if (is.null(v) || is.na(v)) return("pending")
  b <- band_for(i)$band
  switch(b %||% "pending", stop = "red", mod = "amber", go = "green", "pending")
}


# ── Outlook chart data: from schedule_full + actuals ──────────────────────────
sched <- rd$schedule_full %||% data.frame()
chart_labels <- character(0); chart_target <- numeric(0); chart_actual <- list()
if (nrow(sched) > 0) {
  chart_labels <- format(sched$month_date, "%b %y")
  chart_target <- sched$cumulative_target
  ca <- sched$cumulative_actual %||% rep(NA_real_, nrow(sched))
  # Show actuals only up to current month (rest as null)
  cutoff_idx <- which(sched$month_date > as.Date(format(Sys.Date(), "%Y-%m-01")))
  if (length(cutoff_idx)) ca[cutoff_idx] <- NA
  chart_actual <- ca
}

# JSON helper
j <- function(x) {
  if (requireNamespace("jsonlite", quietly = TRUE)) {
    jsonlite::toJSON(x, na = "null", null = "null", auto_unbox = TRUE)
  } else {
    paste0("[", paste(ifelse(is.na(x), "null", x), collapse = ","), "]")
  }
}

# Always an array, even for a single element — Chart.js datasets need a list.
ja <- function(x) {
  if (requireNamespace("jsonlite", quietly = TRUE)) {
    jsonlite::toJSON(x, na = "null", null = "null", auto_unbox = FALSE)
  } else {
    paste0("[", paste(ifelse(is.na(x), "null", paste0('"', x, '"')), collapse = ","), "]")
  }
}

# Ethnicity bar segments (top groups only, others combined)
eth_tbl <- (demo$ethnicity %||% list())$table
if (!is.null(eth_tbl) && nrow(eth_tbl) > 0) {
  eth_tbl <- eth_tbl[order(-eth_tbl$n), ]
  if (nrow(eth_tbl) > 5) {
    other <- data.frame(ethnicity = "Other",
                        n   = sum(eth_tbl$n[6:nrow(eth_tbl)]),
                        pct = sum(eth_tbl$pct[6:nrow(eth_tbl)]),
                        stringsAsFactors = FALSE)
    eth_tbl <- rbind(eth_tbl[1:5, ], other)
  }
}
# Shorten the REDCap ethnicity labels so they fit a chart legend, e.g.
# "White - English, Welsh, Scottish, Northern Irish or British" -> "White — British".
eth_short <- function(x) {
  x <- as.character(x)
  x <- sub("^Other ethnic group - Any other ethnic group$", "Other ethnic group", x)
  x <- sub("^Asian or Asian British - ", "Asian \u2014 ", x)
  x <- sub("^Black, Black British, Caribbean or African - ", "Black \u2014 ", x)
  x <- sub("^Mixed or multiple ethnic groups - ", "Mixed \u2014 ", x)
  x <- sub("^Other ethnic group - ", "Other \u2014 ", x)
  x <- sub("^White - ", "White \u2014 ", x)
  x <- sub("English, Welsh, Scottish, Northern Irish or British", "British", x)
  x <- sub("Any other (Asian|Black|White|Mixed) background", "other background", x)
  x <- sub("Any other ", "other ", x)
  x
}

# Canvas cannot resolve CSS custom properties, so the donut needs literal hex.
eth_hex <- c("#01344F", "#12A192", "#f3b860", "#9bd07a", "#9bc3da", "#e587a8")
eth_labels_js <- character(0); eth_n_js <- numeric(0)
if (!is.null(eth_tbl) && nrow(eth_tbl) > 0) {
  eth_labels_js <- eth_short(eth_tbl$ethnicity)
  eth_n_js      <- as.numeric(eth_tbl$n)
  eth_hex       <- eth_hex[((seq_len(nrow(eth_tbl)) - 1) %% length(eth_hex)) + 1]
}
# Headline for the middle of the donut: % from an ethnic-minority background.
eth_min_pct <- local({
  e <- demo$ethnicity
  if (is.null(e) || safe(e$total, 0) == 0) NA else round(safe(e$minority, 0) / e$total * 100)
})
```

<style>
:root{
  --navy:#01344F; --navy-2:#0a4f70; --navy-tint:#eaf1f5; --navy-tint-2:#f4f7f9;
  --teal:#12A192; --teal-tint:#e3f6f3; --teal-tint-2:#f1faf8;
  --ink:#1a2b36; --ink-2:#3d5363; --muted:#6a7d8a;
  --line:#dfe7ec; --line-soft:#eef2f5;
  --green:#0F8A5F; --green-tint:#dbf2e7;
  --amber:#C77518; --amber-tint:#fcecd5;
  --red:#B4321E; --red-tint:#fadcd6;
  --grey:#7c8a93; --grey-tint:#eef1f3;
  --pad-page:14mm; --gap-sec:14px; --fs-base:10pt;
}
*{box-sizing:border-box}
html,body{margin:0;padding:0;font-family:Calibri,'Segoe UI',-apple-system,system-ui,sans-serif;color:var(--ink);background:#e8eef2;font-size:var(--fs-base);-webkit-print-color-adjust:exact;print-color-adjust:exact}
body{padding:24px 0}
.doc{max-width:210mm;margin:0 auto}
.page{background:#fff;width:210mm;min-height:297mm;margin:0 auto 18px;padding:var(--pad-page);position:relative;box-shadow:0 1px 2px rgba(0,0,0,.08),0 8px 24px rgba(15,40,60,.08);border-radius:2px;display:flex;flex-direction:column}
@page{size:A4;margin:11mm 12mm 12mm}
@media print{
  /* Tighter section rhythm on paper — screens keep the roomier preview. */
  :root{--gap-sec:10px}
  body{background:#fff;padding:0}
  .doc{max-width:none}
  /* Real @page margins frame every sheet — including table continuation
     sheets — so the fixed 297mm canvas and its 14mm padding go. The flex
     column with min-height keeps each footer at the base of a full page;
     1mm slack below the 274mm printable height avoids rounding spilling a
     blank sheet. */
  .page{box-shadow:none;margin:0;border-radius:0;width:auto;min-height:273mm;padding:0;page-break-after:always}
  .page:last-child{page-break-after:auto}
  /* Blocks never split mid-element: anything that will not fit in the space
     left on the current page starts on the next one instead. */
  .ph,.ph-info,.card,.row2,.row3,.sw-cell,.pc,.meta-strip,.pilot-strip,.timeline-wrap,
  .ol-chart-wrap,.ol-status,.milestones,.ml-grp,.chart-wrap,
  .demo,.note,.scale-key,.eth-split,.eth-legend,svg{
    break-inside:avoid;page-break-inside:avoid}
  /* Headings and table captions stay with the content they introduce. */
  h2.sec,p.lab{break-after:avoid-page;page-break-after:avoid;break-inside:avoid}
  /* Long tables may span pages: rows never split, and the header row is
     re-printed at the top of every continuation sheet. Timepoint group rows
     stay attached to their first form row. */
  table.rt{break-inside:auto;page-break-inside:auto}
  table.rt thead{display:table-header-group}
  table.rt tr{break-inside:avoid;page-break-inside:avoid}
  table.rt tr.grp{break-after:avoid-page;page-break-after:avoid}
  .pf{break-inside:avoid;page-break-inside:avoid}
}
/* Header — 1a: trial mark + title tag left · BCTU + report meta right */
.ph{display:flex;align-items:center;justify-content:space-between;gap:16px;padding-bottom:10px;border-bottom:2px solid var(--navy);margin-bottom:12px}
.ph .brand{display:flex;align-items:center;gap:14px;min-width:0}
.ph .ph-trial-logo{height:50px;width:auto;display:block}
.ph .ph-trial-name{font-family:'Source Serif 4',serif;font-size:20pt;font-weight:700;color:var(--navy);letter-spacing:-.5px;line-height:1}
.ph .brand .tag{font-size:8.5pt;color:var(--muted);line-height:1.35;font-weight:500;border-left:1px solid var(--line);padding-left:14px}
.ph .brand .tag b{color:var(--navy);font-weight:600;display:block;font-size:9.5pt}
.ph .meta{display:flex;flex-direction:column;align-items:flex-end;gap:4px;text-align:right;font-size:8.5pt;color:var(--muted);line-height:1.4;flex-shrink:0}
.ph .ph-bctu-logo{height:30px;width:auto;display:block}
.ph .meta b{color:var(--navy);font-weight:600}

.meta-strip{display:grid;grid-template-columns:repeat(5,minmax(0,1fr));gap:0;background:var(--navy-tint-2);border:1px solid var(--line);border-radius:6px;padding:7px 12px;margin:0 0 12px}
.meta-strip .mi{padding:0 8px;border-right:1px solid var(--line)}
.meta-strip .mi:last-child{border-right:0}
.meta-strip .mk{font-size:7.5pt;color:var(--muted);font-weight:600;text-transform:uppercase;letter-spacing:.06em}
.meta-strip .mv{font-size:9.5pt;color:var(--navy);font-weight:600;line-height:1.2;margin-top:1px}
.meta-strip .mv small{font-weight:500;color:var(--muted);font-size:8.5pt}

.pf{display:flex;justify-content:space-between;align-items:center;border-top:1px solid var(--line);padding-top:6px;margin-top:auto;font-size:8pt;color:var(--muted)}
.pf .pn{color:var(--navy);font-weight:600}
.pf .pf-nihr{height:14px;width:auto;display:block}

h1.title{font-family:'Source Serif 4',serif;font-size:26pt;font-weight:700;color:var(--navy);margin:0 0 6px;letter-spacing:-.5px;line-height:1.1;background:#E6F7F5;padding:4px 12px;border-radius:4px}
.sub{font-size:11pt;color:var(--ink-2);margin:0 0 12px;font-weight:500}
.sub b{color:var(--navy)}

h2.sec{font-family:Calibri,'Segoe UI',sans-serif;font-size:11pt;font-weight:700;color:var(--navy);margin:var(--gap-sec) 0 6px;letter-spacing:.04em;text-transform:uppercase;display:flex;align-items:baseline;gap:8px;flex-wrap:wrap;padding-bottom:4px;border-bottom:1px solid var(--line);white-space:nowrap}
h2.sec .num{font-size:8.5pt;color:#fff;background:var(--teal);padding:1px 6px;border-radius:3px;font-weight:700;letter-spacing:0;flex-shrink:0}
h2.sec .hint{margin-left:auto;font-size:8.5pt;color:var(--muted);font-weight:500;text-transform:none;letter-spacing:0;white-space:normal}

.lab{font-size:8pt;color:var(--muted);font-weight:600;text-transform:uppercase;letter-spacing:.06em;margin:8px 0 4px}

.snap{display:grid;grid-template-columns:repeat(4,1fr);gap:8px;margin:0 0 4px}
.snap .cell{border:1px solid var(--line);border-radius:6px;padding:10px 12px;background:#fff;position:relative;overflow:hidden}
.snap .cell::before{content:"";position:absolute;left:0;top:0;bottom:0;width:3px;background:var(--teal)}
.snap .cell.amber::before{background:var(--amber)}
.snap .cell.green::before{background:var(--green)}
.snap .cell.red::before{background:var(--red)}
.snap .cell.navy::before{background:var(--navy)}
.snap .k{font-size:7.5pt;color:var(--muted);font-weight:600;text-transform:uppercase;letter-spacing:.06em}
.snap .v{font-size:22pt;line-height:1;font-weight:700;color:var(--navy);font-family:'Source Serif 4',serif;letter-spacing:-.02em;margin-top:3px}
.snap .v small{font-size:11pt;color:var(--muted);font-weight:500;font-family:Calibri,'Segoe UI',sans-serif;letter-spacing:0}
.snap .s{font-size:8pt;color:var(--ink-2);margin-top:2px;line-height:1.25}

.milestones .lane-head{display:grid;grid-template-columns:1fr 110px 110px;gap:8px;font-size:7.5pt;color:var(--muted);font-weight:600;text-transform:uppercase;letter-spacing:.06em;padding:4px 12px 4px 14px;margin-top:2px}
.ml-grp{border:1px solid var(--line);border-radius:6px;overflow:hidden;background:#fff;margin-top:4px}
.ml-grp + .ml-grp{margin-top:6px}
.ml-grp-h{display:flex;align-items:center;gap:10px;padding:6px 12px;background:var(--navy-tint-2);border-bottom:1px solid var(--line);font-size:8.5pt;font-weight:700;color:var(--navy);letter-spacing:.04em;text-transform:uppercase}
.ml-grp-h .pill{font-size:7.5pt}
.ml-grp-h .gpcnt{margin-left:auto;font-weight:500;color:var(--muted);letter-spacing:0;text-transform:none}
.ml-row{display:grid;grid-template-columns:1fr 110px 110px;gap:8px;align-items:center;padding:6px 12px;border-top:1px solid var(--line-soft)}
.ml-grp-h + .ml-row{border-top:0}
.ml-row:nth-child(odd){background:#fcfdfe}
.ml-name{font-size:9.5pt;color:var(--navy);font-weight:500;display:flex;align-items:center;gap:8px}
.ml-name .seq{width:18px;height:18px;border-radius:4px;background:var(--navy-tint);color:var(--navy);font-size:7.5pt;font-weight:700;display:inline-flex;align-items:center;justify-content:center;flex-shrink:0}
.ml-date{font-size:9pt;color:var(--ink-2);font-variant-numeric:tabular-nums}
.ml-date.est::before{content:"≈ ";color:var(--muted)}
.ml-st{justify-self:end}

.pilot-strip{display:grid;grid-template-columns:repeat(6,1fr);gap:6px;margin-top:4px}
.pc{border:1px solid var(--line);border-radius:6px;padding:8px 9px 9px;background:#fff}
.pc .pcn{font-size:7.5pt;font-weight:700;color:var(--muted);letter-spacing:.06em}
.pc .pct{font-size:9pt;font-weight:600;color:var(--navy);line-height:1.25;margin:2px 0 6px;min-height:30px}
.pc .pcv{font-size:14pt;font-weight:700;line-height:1;font-family:'Source Serif 4',serif;letter-spacing:-.02em}
.pc .pcb{font-size:7.5pt;color:var(--muted);margin-top:3px}
.pc .pcs{display:inline-block;margin-top:6px;font-size:7.5pt;font-weight:700;padding:1px 6px;border-radius:3px;letter-spacing:.04em}
.pc.g{background:var(--green-tint)} .pc.g .pcv,.pc.g .pcs{color:var(--green)} .pc.g .pcs{background:rgba(15,138,95,.16)}
.pc.a{background:var(--amber-tint)} .pc.a .pcv,.pc.a .pcs{color:var(--amber)} .pc.a .pcs{background:rgba(199,117,24,.18)}
.pc.r{background:var(--red-tint)} .pc.r .pcv,.pc.r .pcs{color:var(--red)} .pc.r .pcs{background:rgba(180,50,30,.16)}
.pc.n{background:var(--grey-tint)} .pc.n .pcv,.pc.n .pcs{color:var(--grey)} .pc.n .pcs{background:rgba(124,138,147,.2)}

.timeline-wrap{margin-top:6px;padding:12px 12px 8px;border:1px solid var(--line);border-radius:6px;background:#fff}
.legend{display:flex;gap:14px;font-size:8pt;color:var(--muted);margin-bottom:6px;flex-wrap:wrap}
.legend .lg{display:inline-flex;align-items:center;gap:5px}
.legend .sw{width:11px;height:7px;border-radius:2px}

table.rt{width:100%;border-collapse:collapse;font-size:9pt;margin-top:4px}
table.rt th{background:var(--navy);color:#fff;text-align:left;padding:6px 10px;font-weight:600;font-size:8.5pt;letter-spacing:.02em}
table.rt th:not(:first-child){text-align:right}
table.rt th.l{text-align:left}
table.rt td{padding:6px 10px;border-bottom:1px solid var(--line-soft)}
table.rt td:not(:first-child){text-align:right}
table.rt td.l{text-align:left}
table.rt tr:nth-child(even) td{background:var(--navy-tint-2)}
table.rt tr:last-child td{border-bottom:0}
table.rt td.sn{color:var(--navy);font-weight:500}
table.rt tr.tot td{background:var(--navy-tint);font-weight:700;color:var(--navy);border-top:2px solid var(--navy)}

.pill{display:inline-flex;align-items:center;gap:4px;font-size:8pt;padding:1px 8px;border-radius:11px;font-weight:600;letter-spacing:.02em}
.pill .dot{width:6px;height:6px;border-radius:50%}
.p-g{background:var(--green-tint);color:var(--green)} .p-g .dot{background:var(--green)}
.p-a{background:var(--amber-tint);color:var(--amber)} .p-a .dot{background:var(--amber)}
.p-r{background:var(--red-tint);color:var(--red)} .p-r .dot{background:var(--red)}
.p-n{background:var(--grey-tint);color:var(--grey)} .p-n .dot{background:var(--grey)}
.p-i{background:#dbeafa;color:#0c558a} .p-i .dot{background:#0c558a}

.pb{display:flex;align-items:center;gap:8px}
.pb .track{flex:1;height:6px;background:var(--line-soft);border-radius:20px;overflow:hidden}
.pb .fill{height:100%;background:var(--teal);border-radius:20px}
.pb .lbl{font-size:8pt;font-weight:600;color:var(--navy);min-width:38px;text-align:right}

.row2{display:grid;grid-template-columns:1fr 1fr;gap:14px}
.row3{display:grid;grid-template-columns:1fr 1fr 1fr;gap:14px}

.card{border:1px solid var(--line);border-radius:6px;padding:10px 12px;background:#fff}
.card .ct{font-size:8.5pt;color:var(--navy);font-weight:700;text-transform:uppercase;letter-spacing:.06em;margin-bottom:4px}
.chart-wrap{position:relative;height:140px}
.chart-wrap-lg{position:relative;height:360px}

.demo{display:flex;gap:6px;margin-top:4px}
.demo .chip{flex:1;text-align:center;padding:8px 6px;border-radius:6px;background:var(--navy-tint-2);border:1px solid var(--line)}
.demo .chip b{display:block;font-size:18pt;font-weight:700;color:var(--navy);font-family:'Source Serif 4',serif;letter-spacing:-.02em;line-height:1}
.demo .chip span{display:block;font-size:8pt;color:var(--muted);margin-top:3px}

.keyline{display:flex;gap:16px;align-items:baseline;font-size:9pt;background:var(--teal-tint-2);border-left:3px solid var(--teal);padding:6px 12px;border-radius:0 4px 4px 0;margin:6px 0 2px;flex-wrap:wrap}
.keyline span b{color:var(--navy);font-weight:600}
.keyline span{color:var(--muted)}

.note{font-size:8pt;color:var(--muted);font-style:italic;margin-top:6px;line-height:1.4}
.scale-key{display:flex;gap:10px;font-size:8pt;color:var(--muted);margin-top:6px;flex-wrap:wrap}
.scale-key b{font-weight:600}

.sw-grid{display:grid;grid-template-columns:1fr 2.1fr;gap:12px;margin-top:4px}
.sw-cell{border:1px solid var(--line);border-radius:6px;padding:12px;background:#fff;display:flex;flex-direction:column;gap:4px}
.sw-cell .lab2{font-size:7.5pt;color:var(--muted);font-weight:600;text-transform:uppercase;letter-spacing:.06em}
.sw-cell .big{font-size:30pt;font-weight:700;font-family:'Source Serif 4',serif;line-height:1;letter-spacing:-.02em}
.sw-cell.safe{background:var(--green-tint);border-color:#bce6cf}
.sw-cell.safe .big{color:var(--green)}
.sw-cell.wd{background:var(--amber-tint);border-color:#f0d6a4}
.sw-cell.wd .big{color:var(--amber)}
.sw-cell.wd .big small{font-size:14pt;color:var(--muted);font-family:Calibri,'Segoe UI',sans-serif;font-weight:500}
.sw-cell .det{font-size:9pt;color:var(--ink-2);margin-top:4px;line-height:1.45}
.sw-cell .det b{color:var(--navy);font-weight:600}

.eth-split{display:grid;grid-template-columns:180px 1fr;gap:16px;align-items:center;margin-top:6px}
.eth-donut{position:relative;height:170px}
.eth-legend{display:flex;flex-direction:column;gap:4px;margin-top:0;font-size:8.5pt;color:var(--ink-2)}
.eth-legend .row{display:flex;align-items:center;gap:8px}
.eth-legend .sw{width:12px;height:12px;border-radius:3px;flex-shrink:0}
.eth-legend .nm{flex:1;color:var(--navy);font-weight:500}
.eth-legend .vl{color:var(--muted);font-variant-numeric:tabular-nums}
.eth-legend .vl b{color:var(--navy);font-weight:600}

.thr-row{display:grid;grid-template-columns:1fr 1.4fr;gap:14px;align-items:center;padding:10px 0;border-bottom:1px solid var(--line-soft)}
.thr-row:last-child{border-bottom:0}
.thr-name{font-size:10pt;color:var(--navy);font-weight:600;line-height:1.3}
.thr-name .det{font-size:8.5pt;color:var(--muted);font-weight:400;margin-top:2px;line-height:1.4;display:block}
.thr-bands{display:grid;grid-template-columns:1fr 1fr 1fr;gap:4px}
.thr-band{padding:6px 8px;border-radius:4px;font-size:8.5pt;font-weight:600;text-align:center;line-height:1.25}
.thr-band .lb{font-size:7pt;display:block;text-transform:uppercase;letter-spacing:.06em;opacity:.85;font-weight:700;margin-bottom:1px}
.thr-band.stop{background:var(--red-tint);color:var(--red)}
.thr-band.mod{background:var(--amber-tint);color:var(--amber)}
.thr-band.go{background:var(--green-tint);color:var(--green)}
.thr-band.now{outline:2px solid var(--navy);outline-offset:1px;font-weight:700}

.ol-status{display:flex;align-items:center;gap:14px;border-radius:6px;padding:10px 14px;margin:6px 0 10px}
.ol-status.green{background:var(--green-tint);border:1px solid #bce6cf;border-left:4px solid var(--green)}
.ol-status.amber{background:var(--amber-tint);border:1px solid #f0d6a4;border-left:4px solid var(--amber)}
.ol-status.red{background:var(--red-tint);border:1px solid #f0bcb1;border-left:4px solid var(--red)}
.ol-status .icon{width:32px;height:32px;border-radius:50%;color:#fff;display:flex;align-items:center;justify-content:center;flex-shrink:0;font-weight:700}
.ol-status.green .icon{background:var(--green)}
.ol-status.amber .icon{background:var(--amber)}
.ol-status.red .icon{background:var(--red)}
.ol-status .txt{flex:1}
.ol-status .h{font-size:10.5pt;font-weight:700;letter-spacing:.02em}
.ol-status.green .h{color:var(--green)} .ol-status.amber .h{color:var(--amber)} .ol-status.red .h{color:var(--red)}
.ol-status .s{font-size:9pt;color:var(--ink-2);margin-top:1px}

.ol-chart{border:1px solid var(--line);border-radius:6px;background:#fff;padding:10px 12px}
.ol-chart .h{display:flex;justify-content:space-between;align-items:baseline;margin-bottom:6px;font-size:9pt;color:var(--muted)}
.ol-chart .h b{color:var(--navy);font-weight:600}
.ol-chart-wrap{position:relative;height:300px}
.ol-leg{display:flex;gap:18px;font-size:8.5pt;color:var(--muted);margin-top:6px;flex-wrap:wrap}
.ol-leg .lg{display:inline-flex;align-items:center;gap:6px}
.ol-leg .sw{width:14px;height:8px;border-radius:2px}
.ol-leg .ln{width:14px;border-top:2px solid var(--navy);height:1px}

</style>

<link rel="preconnect" href="https://fonts.googleapis.com"> <link rel="preconnect" href="https://fonts.gstatic.com" crossorigin> <link href="https://fonts.googleapis.com/css2?family=Source+Serif+4:wght@600;700&display=swap" rel="stylesheet">

<script src="https://cdn.jsdelivr.net/npm/chart.js@4.4.1/dist/chart.umd.min.js"></script>

<div class="doc">
```{r page-header-helper}
ph_header <- function(page_label) {
  # 1a layout — trial mark + title tag left; BCTU logo stacked above the
  # report meta on the right.
  trial_logo_html <- if (nchar(logo_b64) > 0)
    sprintf('<img class="ph-trial-logo" src="%s" alt="%s logo">',
            logo_b64, esc(trial_short))
  else
    sprintf('<span class="ph-trial-name">%s</span>', esc(trial_short))

  bctu_logo_html <- if (nchar(bctu_logo_b64) > 0)
    sprintf('<img class="ph-bctu-logo" src="%s" alt="Birmingham Clinical Trials Unit">',
            bctu_logo_b64) else ""

  meta_line <- if (nzchar(page_label))
    sprintf('<b>%s</b> · %s', esc(report_date_str), esc(page_label))
  else
    sprintf('<b>%s</b> · <span style="color:var(--teal);font-weight:600">Confidential</span>',
            esc(report_date_str))

  cat(sprintf(
'<header class="ph">
  <div class="brand">%s
    <div class="tag"><b>%s</b>Trial Management Group · Progress Report</div>
  </div>
  <div class="meta">%s<div>%s</div></div>
</header>',
    trial_logo_html, esc(trial_title), bctu_logo_html, meta_line))
}
pf_footer <- function(n_page, n_total = 6) {
  rt <- safe(params$report_type, "TMG")
  ver <- safe(rc$version, "1.0")
  nihr_html <- if (nchar(nihr_logo_b64) > 0)
    sprintf('<img class="pf-nihr" src="%s" alt="Funded by NIHR">', nihr_logo_b64) else "<span></span>"
  cat(sprintf('<footer class="pf"><span>%s %s Progress Report v%s (%s)</span>%s<span class="pn">Page %d of %d</span></footer>',
              esc(trial_short), esc(rt), esc(ver), format(Sys.Date(), "%d-%b-%Y"), nihr_html, n_page, n_total))
}
```

<!-- ============================================================
     PAGE 1 — KEY MILESTONES · PILOT PROGRESSION · TIMELINE
============================================================== -->

<section class="page">

```{r page1-header}
ph_header("")
```

<div class="meta-strip">
<div class="mi">
<div class="mk">
Chief Investigator
</div>

<div class="mv">
`r esc(chief_inv)`
</div>
</div>

<div class="mi">
<div class="mk">
Sponsor · Funder
</div>

<div class="mv">
`r esc(sponsor)` <small>· `r esc(funder)`</small>
</div>
</div>

<div class="mi">
<div class="mk">
Funder ref · Registration
</div>

<div class="mv">
`r esc(funder_ref)` <small>· `r esc(isrctn)`</small>
</div>
</div>

<div class="mi">
<div class="mk">
Sample · Sites
</div>

<div class="mv">
`r fmt_int(sample_size)` <small>(`r fmt_int(round(as.numeric(sample_size)/2))`/arm)</small> · `r fmt_int(n_sites_plan)` UK
</div>
</div>

<div class="mi">
<div class="mk">
Project dates
</div>

<div class="mv">
`r esc(proj_start)` → `r esc(proj_end)` <small>(`r fmt_int(proj_months)` mo)</small>
</div>
</div>
</div>

<h1 class="title">

Trial Overview

</h1>

<p class="sub">

`r fmt_int(n_rand)` participant`r if (!is.na(n_rand) && n_rand == 1) "" else "s"` randomised across `r fmt_int(n_open_sites)` active site`r if (!is.na(n_open_sites) && n_open_sites == 1) "" else "s"` — pilot opened <b>`r esc(proj_start)`</b>, `r if (rec_band == "green") "on protocol target" else if (rec_band == "amber") "near protocol target" else "behind protocol target"`.

</p>

<div class="snap">
<div class="cell navy">
<div class="k">Participants randomised</div>
<div class="v">`r fmt_int(n_rand)`<small> / `r fmt_int(n_target)`</small></div>
<div class="s">`r if (!is.na(pct_of_target)) sprintf("%.1f%% of trial target", pct_of_target) else "—"` · pilot `r if (!is.na(pilot_pct)) sprintf("%.0f%%", pilot_pct) else "—"`</div>
</div>

<div class="cell">
<div class="k">Sites open · recruiting</div>
<div class="v">`r fmt_int(n_open_sites)`<small> / `r fmt_int(n_sites_plan)`</small></div>
<div class="s">`r fmt_int(n_setup_sites + n_ident_sites)` in set-up / identified</div>
</div>

<div class="cell `r rec_band`">
<div class="k">Recruitment vs. protocol</div>
<div class="v">`r fmt_pct(rec_pct, 0)`</div>
<div class="s">`r fmt_int(n_rand)` actual vs `r fmt_int(exp_to_date)` expected (`r format(Sys.Date(), "%b %y")`)</div>
</div>

<div class="cell `r if (sae_count == 0) "green" else "amber"`">

<div class="k">
SAEs to date
</div>

<div class="v">`r fmt_int(sae_count)`</div>
<div class="s">`r if (sae_count == 0) "No safety signals reported" else "See section 07 for detail"`</div>
</div>

</div>

<h2 class="sec">

<span class="num">01</span> Key milestones <span class="hint">`r esc(next_ms_lbl)`</span>

</h2>

<div class="milestones">
<div class="lane-head"><span>Milestone</span><span style="text-align:right">Planned / actual</span><span style="text-align:right">Status</span></div>

```{r milestones}
render_ms_group <- function(items, pill_class, pill_label, group_label, status_only_dates_estimated = FALSE) {
  if (length(items) == 0) return(invisible())
  cat(sprintf('<div class="ml-grp"><div class="ml-grp-h"><span class="pill %s"><span class="dot"></span>%s</span>%s<span class="gpcnt">%d milestones</span></div>',
              pill_class, pill_label, esc(group_label), length(items)))
  # Number sequentially within group, but keep an overall seq number across groups
  for (i in seq_along(items)) {
    m <- items[[i]]
    seq_n <- m$seq
    is_est <- identical(m$status, "estimated")
    date_cls <- if (is_est) "ml-date est" else "ml-date"
    status_pill <- switch(as.character(m$status),
      complete  = '<span class="pill p-g"><span class="dot"></span>Complete</span>',
      upcoming  = '<span class="pill p-a"><span class="dot"></span>Pending</span>',
      estimated = '<span class="pill p-n"><span class="dot"></span>Estimated</span>',
      '<span class="pill p-n"><span class="dot"></span>—</span>')
    cat(sprintf('<div class="ml-row"><div class="ml-name"><span class="seq">%s</span>%s</div><div class="%s">%s</div><div class="ml-st">%s</div></div>',
                seq_n, esc(m$name), date_cls, esc(m$date), status_pill))
  }
  cat('</div>')
}

# attach sequential numbers
ms_seq <- ms
for (i in seq_along(ms_seq)) ms_seq[[i]]$seq <- i
ms_complete2 <- Filter(function(m) identical(m$status, "complete"),  ms_seq)
ms_future2   <- Filter(function(m) !identical(m$status, "complete"), ms_seq)

render_ms_group(ms_complete2, "p-g", "Complete", "Set-up & trial activation")
render_ms_group(ms_future2,   "p-a", "Upcoming", "Pilot · recruitment · close-out")
```
</div>

<h2 class="sec">

<span class="num">02</span> Internal pilot progression <span class="hint">6-month pilot · review `r esc(pilot_end)`</span>

</h2>

<div class="pilot-strip">
```{r pilot-cards}
for (i in seq_along(pc_cards)) {
  card <- pc_cards[[i]]
  v <- card$val
  s <- status_for_card(i, v)
  cls <- crit_class(s)
  vstr <- if (is.null(v) || length(v) == 0 || is.na(v)) "—" else fmt_pct(v, 0)
  cat(sprintf('<div class="pc %s"><div class="pcn">%02d</div><div class="pct">%s</div><div class="pcv">%s</div><div class="pcb">%s</div><div class="pcs">%s</div></div>',
              cls, i, esc(card$title), vstr, esc(card$sub), crit_label(s)))
}
```
</div>

<div class="note">
Decision rule — <b style="color:var(--green)">GREEN</b> proceed · <b style="color:var(--amber)">AMBER</b> modify and review · <b style="color:var(--red)">RED</b> consider stopping. Full thresholds and recruitment outlook on page 4.
</div>

```{r page1-footer}
pf_footer(1)
```

</section>

<!-- ============================================================
     PAGE 2 — PROJECT TIMELINE · RECRUITMENT VS TARGET
============================================================== -->

<section class="page">

```{r page2-header}
ph_header("Page 2 — Timeline & recruitment")
```

<h2 class="sec" style="margin-top:0">

<span class="num">03</span> Project timeline <span class="hint">`r esc(proj_start)` → `r esc(safe(rc$timeline_end, "Feb 2029"))` · `r fmt_int(safe(rc$timeline_months, 57))` mo end-to-end</span>

</h2>

<div class="timeline-wrap">
<div class="legend">
<span class="lg"><span class="sw" style="background:#9bc3da"></span>Study set-up</span>
<span class="lg"><span class="sw" style="background:var(--navy)"></span>6-mo pilot</span>
<span class="lg"><span class="sw" style="background:var(--teal)"></span>Full recruitment</span>
<span class="lg"><span class="sw" style="background:#f3b860"></span>Treatment &amp; follow-up</span>
<span class="lg"><span class="sw" style="background:#9bd07a"></span>Data cleaning</span>
<span class="lg"><span class="sw" style="background:#f29278"></span>Analysis &amp; writeup</span>
<span class="lg"><span class="sw" style="background:#e587a8"></span>Close-out</span>
<span class="lg" style="margin-left:auto"><span style="width:10px;border-left:1.5px dashed var(--red);height:10px;display:inline-block"></span>&nbsp;Now (`r format(Sys.Date(), "%b %y")`)</span>
</div>

  <svg viewBox="0 0 816 258" width="100%" style="display:block">
    <g fill="#f6f9fb">
      <rect x="90" y="18" width="144" height="214"/>
      <rect x="378" y="18" width="144" height="214"/>
      <rect x="666" y="18" width="108" height="214"/>
    </g>
    <g font-family="Calibri, Segoe UI, sans-serif" font-size="9" fill="#6a7d8a">
      <text x="90" y="12" text-anchor="middle">Jun 24</text>
      <text x="162" y="12" text-anchor="middle">Dec 24</text>
      <text x="234" y="12" text-anchor="middle">Jun 25</text>
      <text x="306" y="12" text-anchor="middle">Dec 25</text>
      <text x="378" y="12" text-anchor="middle">Jun 26</text>
      <text x="450" y="12" text-anchor="middle">Dec 26</text>
      <text x="522" y="12" text-anchor="middle">Jun 27</text>
      <text x="594" y="12" text-anchor="middle">Dec 27</text>
      <text x="666" y="12" text-anchor="middle">Jun 28</text>
      <text x="738" y="12" text-anchor="middle">Dec 28</text>
    </g>
    <line x1="90" y1="18" x2="774" y2="18" stroke="#dfe7ec" stroke-width="1"/>
    <g font-family="Calibri, Segoe UI, sans-serif" font-size="10.5" fill="#3d5363" font-weight="500">
      <text x="0" y="42">Study set-up</text>
      <rect x="90" y="28" width="252" height="20" rx="3" fill="#9bc3da"/>
      <text x="216" y="42" text-anchor="middle" font-size="8.5" font-weight="600" fill="#01344F">21 mo</text>
      <text x="347" y="42" font-size="7" font-weight="500" fill="#6a7d8a">Feb 26</text>
      <text x="0" y="72">6-mo pilot</text>
      <rect x="354" y="58" width="72" height="20" rx="3" fill="#01344F"/>
      <text x="390" y="72" text-anchor="middle" font-size="8.5" font-weight="600" fill="#ffffff">6 mo</text>
      <text x="431" y="72" font-size="7" font-weight="500" fill="#6a7d8a">Sep 26</text>
      <text x="0" y="102">Full recruitment</text>
      <rect x="426" y="88" width="252" height="20" rx="3" fill="#12A192" opacity=".95"/>
      <text x="552" y="102" text-anchor="middle" font-size="8.5" font-weight="600" fill="#ffffff">21 mo</text>
      <text x="683" y="102" font-size="7" font-weight="500" fill="#6a7d8a">Jun 28</text>
      <text x="0" y="132">Treatment &amp; follow-up</text>
      <rect x="354" y="118" width="360" height="20" rx="3" fill="#f3b860"/>
      <text x="534" y="132" text-anchor="middle" font-size="8.5" font-weight="600" fill="#01344F">30 mo</text>
      <text x="719" y="132" font-size="7" font-weight="500" fill="#6a7d8a">Sep 28</text>
      <text x="0" y="162">Data cleaning</text>
      <rect x="714" y="148" width="24" height="20" rx="3" fill="#9bd07a"/>
      <text x="743" y="162" font-size="7" font-weight="500" fill="#6a7d8a">Nov 28</text>
      <text x="0" y="192">Analysis &amp; writeup</text>
      <rect x="738" y="178" width="24" height="20" rx="3" fill="#f29278"/>
      <text x="767" y="192" font-size="7" font-weight="500" fill="#6a7d8a">Jan 29</text>
      <text x="0" y="222">Close-out</text>
      <rect x="762" y="208" width="12" height="20" rx="3" fill="#e587a8"/>
      <text x="779" y="222" font-size="7" font-weight="500" fill="#6a7d8a">Feb 29</text>
    </g>
```{r now-marker, results="asis"}
# Compute x for "now" marker: months since Jun 2024 * 12, anchored at x=90
mo_now <- as.integer(round(as.numeric(difftime(Sys.Date(), as.Date("2024-06-01"), units = "days")) / 30.44))
mo_now <- max(0, min(57, mo_now))
xn <- 90 + mo_now * 12
cat(sprintf('<g><line x1="%d" y1="18" x2="%d" y2="234" stroke="#B4321E" stroke-width="1.5" stroke-dasharray="4 3"/><text x="%d" y="246" font-family="Calibri, Segoe UI, sans-serif" font-size="9" font-weight="700" fill="#B4321E" text-anchor="middle">%s · NOW</text></g>',
            xn, xn, xn, format(Sys.Date(), "%b %y")))
```
  </svg>
</div>

<h2 class="sec">

<span class="num">04</span> Recruitment vs. protocol target

</h2>

<div class="keyline">
  <span>Total randomised: <b>`r fmt_int(n_rand)`</b></span>
  <span>Cumulative target (`r format(Sys.Date(), "%b %y")`): <b>`r fmt_int(exp_to_date)`</b></span>
  <span>Variance: <b style="color:var(--`r rec_band`)">`r fmt_pct(rec_pct, 0)`</b></span>
  <span>Pilot target (`r esc(pilot_end)`): <b>`r fmt_int(pilot_target)`</b></span>
  <span>Full target: <b>`r fmt_int(n_target)` by `r esc(full_end)`</b></span>
</div>

<div class="card" style="margin-top:8px">
  <div class="ct">Monthly randomisations · `r if (length(chart_labels)) paste(chart_labels[1], "\u2192", chart_labels[length(chart_labels)]) else "no schedule"`</div>
  <div class="chart-wrap-lg"><canvas id="monC"></canvas></div>
  <div class="note">Solid bars are participants randomised in each month, labelled with the count. Pale bars behind them are the protocol's target for that month.</div>
</div>

```{r page2-footer}
pf_footer(2)
```

</section>

<!-- ============================================================
     PAGE 3 — SITE PERFORMANCE
============================================================== -->

<section class="page">

```{r page3-header}
ph_header("Page 3 — Site performance")
```

<h2 class="sec" style="margin-top:0">

<span class="num">05</span> Site performance <span class="hint">`r fmt_int(n_sites_total)` UK hospitals · `r fmt_int(n_open_sites)` recruiting · `r fmt_int(n_setup_sites)` in set-up · `r fmt_int(n_ident_sites)` identified</span>

</h2>

<div class="row3" style="margin-top:2px">
<div class="card" style="text-align:center;background:var(--green-tint);border-color:#bce6cf">
<div class="ct" style="color:var(--green)">Open · recruiting</div>
<div style="font-size:22pt;font-weight:700;color:var(--green);font-family:'Source Serif 4',serif;line-height:1">`r fmt_int(n_open_sites)`</div>
<div class="note" style="margin-top:2px">

```{r open-sites-note}
open_names <- if (nrow(pipeline) && "stage" %in% names(pipeline))
  pipeline$site_name[is_open(pipeline$stage)] else character(0)
cat(esc(if (length(open_names)) paste(open_names, collapse = " · ") else "—"))
```

</div>
</div>

<div class="card" style="text-align:center;background:var(--amber-tint);border-color:#f0d6a4">
<div class="ct" style="color:var(--amber)">In set-up</div>
<div style="font-size:22pt;font-weight:700;color:var(--amber);font-family:'Source Serif 4',serif;line-height:1">`r fmt_int(n_setup_sites)`</div>
<div class="note" style="margin-top:2px">Capacity &amp; capability in progress</div>
</div>

<div class="card" style="text-align:center;background:#e6effa;border-color:#bcd2ec">
<div class="ct" style="color:#0c558a">Identified — pending</div>
<div style="font-size:22pt;font-weight:700;color:#0c558a;font-family:'Source Serif 4',serif;line-height:1">`r fmt_int(n_ident_sites)`</div>
<div class="note" style="margin-top:2px">Feasibility &amp; local info pack</div>
</div>
</div>

<p class="lab" style="margin-top:10px">

All sites — status & recruitment

</p>

<table class="rt">
  <thead><tr>
    <th class="l">Site</th><th class="l">Status</th>
    <th>Opened</th><th>Rand.</th><th>Avg / mo</th><th>Target</th>
    <th class="l" style="width:20%">Progress</th>
  </tr></thead>
  <tbody>
```{r site-table}
ss <- site_status
if (nrow(ss) == 0 && nrow(pipeline) > 0) ss <- pipeline
if (nrow(ss) > 0) {
  # normalise columns
  if (!"randomisations" %in% names(ss)) ss$randomisations <- 0L
  if (!"target"         %in% names(ss)) ss$target <- 42L
  if (!"open_date"      %in% names(ss)) ss$open_date <- NA
  if (!"stage"          %in% names(ss)) ss$stage <- "—"
  # Sort: recruiting first, then set-up, then identified, then by name
  rank_stage <- function(s) {
    if (is_open(s))  1L else if (is_setup(s)) 2L else if (is_ident(s)) 3L else 4L
  }
  ss$.rank <- vapply(as.character(ss$stage), rank_stage, integer(1))
  ss <- ss[order(ss$.rank, -ss$randomisations, ss$site_name), ]
  for (i in seq_len(nrow(ss))) {
    r <- ss[i, ]
    pill_cls <- if (is_open(r$stage)) "p-g" else
                if (is_setup(r$stage)) "p-a" else
                if (is_ident(r$stage)) "p-i" else "p-n"
    stage_lbl <- if (is_open(r$stage)) "Recruiting" else
                 if (is_setup(r$stage)) "Set-up" else
                 if (is_ident(r$stage)) "Identified" else as.character(r$stage)
    opened <- if (!is.na(r$open_date) && nzchar(as.character(r$open_date)))
                fmt_date(r$open_date, "%b %Y") else "—"
    rand <- as.integer(r$randomisations %||% 0)
    tgt  <- as.integer(r$target %||% 42)
    # Average randomisations per month since this site opened. The denominator
    # is floored at one month so a site open a fortnight cannot report a rate
    # extrapolated far above what it has actually achieved. Only meaningful for
    # a recruiting site with a known open date; anything else reads "—".
    mo_open <- if (!is.na(r$open_date) && nzchar(as.character(r$open_date))) {
      d <- suppressWarnings(as.Date(r$open_date))
      if (is.na(d)) NA_real_ else
        max(1, as.numeric(difftime(Sys.Date(), d, units = "days")) / 30.44)
    } else NA_real_
    avg_mo   <- if (!is.na(mo_open) && is_open(r$stage)) rand / mo_open else NA_real_
    avg_cell <- if (is.na(avg_mo)) "\u2014" else sprintf("%.1f", avg_mo)
    pct  <- if (tgt > 0) round(rand/tgt*100, 1) else 0
    progress_html <- if (is_open(r$stage))
      sprintf('<div class="pb"><div class="track"><div class="fill" style="width:%.0f%%"></div></div><span class="lbl">%d/%d</span></div>', pct, rand, tgt)
      else sprintf('<span class="note" style="margin:0">%s</span>', esc(r$stage))
    cat(sprintf('<tr><td class="sn">%s</td><td class="l"><span class="pill %s"><span class="dot"></span>%s</span></td><td>%s</td><td>%d</td><td>%s</td><td>%d</td><td class="l">%s</td></tr>',
                esc(r$site_name), pill_cls, esc(stage_lbl), esc(opened), rand, avg_cell, tgt, progress_html))
  }
} else {
  cat('<tr><td colspan="7" style="color:var(--muted);text-align:center;padding:14px">No site data available.</td></tr>')
}
```
  </tbody>
</table>

```{r page3-footer}
pf_footer(3)
```

</section>

<!-- ============================================================
     PAGE 4 — DATA · SAFETY & WITHDRAWALS · DEMOGRAPHICS
============================================================== -->

<section class="page">

```{r page4-header}
ph_header("Page 4 — Data, safety & outcomes")
```

<h2 class="sec" style="margin-top:0">

<span class="num">06</span> CRF return rates <span class="hint">Forms entered ÷ forms due in each timepoint window · n = `r fmt_int(n_rand)` randomised</span>

</h2>

<div class="row2">
<div class="card" style="background:var(--teal-tint-2);border-color:#bfe2dd">
<div class="ct" style="color:var(--teal)">Primary outcome completeness</div>
<div style="display:flex;gap:18px;align-items:baseline;margin-top:4px">
  <div style="font-size:24pt;font-weight:700;color:var(--navy);font-family:'Source Serif 4',serif;line-height:1">`r fmt_pct((rd$primary_outcome %||% list())$pct, 0)`</div>
  <div class="note" style="margin:0">`r if (identical((rd$primary_outcome %||% list())$source, "crf_due")) "Due" else "Eligible"`: <b>`r fmt_int(safe((rd$primary_outcome %||% list())$eligible, 0))`</b> · `r if (identical((rd$primary_outcome %||% list())$source, "crf_due")) "Entered" else "Complete"`: <b>`r fmt_int(safe((rd$primary_outcome %||% list())$complete, 0))`</b><br>`r if (identical((rd$primary_outcome %||% list())$source, "crf_due")) "Discharge form · entered ÷ due, as per return rates below" else "Discharge form, ≥7&nbsp;d post-op"`</div>
</div>
</div>

<div class="card" style="background:var(--navy-tint-2)">
<div class="ct">Overall — all events combined</div>
<div style="display:flex;gap:14px;align-items:baseline;margin-top:4px">
  <div style="font-size:24pt;font-weight:700;color:`r if (!is.na(crf_overall_pct) && crf_overall_pct < 70) "var(--red)" else if (!is.na(crf_overall_pct) && crf_overall_pct < 90) "var(--amber)" else "var(--green)"`;font-family:'Source Serif 4',serif;line-height:1">`r fmt_pct(crf_overall_pct, 1)`</div>
  <div class="note" style="margin:0">

```{r crf-summary}
if (!is.null(crf_stage_rows)) {
  e <- sum(crf_stage_rows$expected, na.rm = TRUE)
  d <- sum(crf_stage_rows$due,      na.rm = TRUE)
  en <- sum(crf_stage_rows$entered, na.rm = TRUE)
  cat(sprintf("Expected: <b>%d</b> · Due: <b>%d</b> · Entered: <b>%d</b>", e, d, en))
} else cat("No CRF return-rate data available.")
```

  </div>
</div>
</div>
</div>

<p class="lab" style="margin-top:8px">

Return rates by timepoint & form

</p>

<table class="rt">
  <thead><tr><th class="l">Timepoint / Form</th><th>Forms</th><th>Expected</th><th>Due</th><th>Entered</th><th>% Entered<small style="font-weight:400">&nbsp;(of due)</small></th></tr></thead>
  <tbody>
```{r crf-rows}
# Render one row per form, grouped under a heading for each timepoint so it is
# clear that a repeated form (e.g. EQ-5D) is a *separate* visit each time.
# The % column is entered ÷ due; a window not yet open (0 due) reads "not due".
pct_cell <- function(pct_v) {
  col <- if (is.na(pct_v)) "var(--grey)" else if (pct_v >= 90) "var(--green)" else if (pct_v >= 70) "var(--amber)" else "var(--red)"
  pct_s <- if (is.na(pct_v)) "—" else sprintf("%.1f%%", pct_v)
  list(col = col, s = pct_s)
}

if (!is.null(crf_stage_rows) && nrow(crf_stage_rows) > 0) {
  has_event <- !all(is.na(crf_stage_rows$event))
  groups <- if (has_event) split(crf_stage_rows, crf_stage_rows$event, drop = TRUE) else
                           list(`All forms` = crf_stage_rows)

  for (gname in names(groups)) {
    g <- groups[[gname]]

    # Timepoint heading row — anchors the forms beneath it to a visit
    if (has_event) {
      g_due <- sum(g$due, na.rm = TRUE)
      g_ent <- sum(g$entered, na.rm = TRUE)
      # Same capped numerator as the overall rate: early entries can't push
      # a timepoint above 100%.
      g_pct <- if (g_due > 0)
        sum(pmin(g$entered, g$due), na.rm = TRUE) / g_due * 100 else NA_real_
      g_note <- if (g_due == 0) " <span style=\"font-weight:400;color:var(--muted)\">— window not yet due</span>" else ""
      cat(sprintf('<tr class="grp"><td class="l" colspan="5" style="font-weight:700;color:var(--navy);background:var(--navy-tint)">%s%s</td><td style="font-weight:700;background:var(--navy-tint)">%s</td></tr>',
                  esc(gname), g_note, if (is.na(g_pct)) "—" else sprintf("%.1f%%", g_pct)))
    }

    for (i in seq_len(nrow(g))) {
      r <- g[i, ]
      pc <- pct_cell(r$pct)
      cat(sprintf('<tr><td class="sn"%s>%s</td><td>%s</td><td>%s</td><td>%s</td><td>%s</td><td style="color:%s;font-weight:700">%s</td></tr>',
                  if (has_event) ' style="padding-left:18px"' else "",
                  esc(r$stage),
                  if (is.na(r$forms)) "—" else r$forms,
                  if (is.na(r$expected)) "—" else r$expected,
                  if (is.na(r$due)) "—" else r$due,
                  if (is.na(r$entered)) "—" else r$entered,
                  pc$col, pc$s))
    }
  }

  e  <- sum(crf_stage_rows$expected, na.rm = TRUE)
  d  <- sum(crf_stage_rows$due,      na.rm = TRUE)
  en <- sum(crf_stage_rows$entered,  na.rm = TRUE)
  # Show raw entered count in the table (transparent) but rate uses capped numerator
  cat(sprintf('<tr class="tot"><td>Total — all timepoints</td><td>%d</td><td>%d</td><td>%d</td><td>%d</td><td>%s</td></tr>',
              sum(crf_stage_rows$forms, na.rm = TRUE), e, d, en, fmt_pct(crf_overall_pct, 1)))
} else {
  cat('<tr><td colspan="6" style="color:var(--muted);text-align:center;padding:14px">No return-rate CSV loaded.</td></tr>')
}
```
  </tbody>
</table>

<div class="scale-key">
  <span><b style="color:var(--green)">≥90%</b> on track</span>
  <span><b style="color:var(--amber)">70–89%</b> attention</span>
  <span><b style="color:var(--red)">&lt;70%</b> action required</span>
  <span><b style="color:var(--grey)">—</b> not yet due</span>
</div>

<h2 class="sec">

<span class="num">07</span> Safety & withdrawals <span class="hint">`r if (sae_count == 0) "No safety signals since trial start" else sprintf("%d SAE(s) reported", sae_count)`</span>

</h2>

<div class="sw-grid">
<div class="sw-cell `r if (sae_count == 0) "safe" else ""`">

<div class="lab2">
Serious adverse events (SAE)
</div>

<div class="big">`r fmt_int(sae_count)`</div>
<div class="det">`r if (sae_count == 0) sprintf("SAEs reported since trial start.<br><b>No SUSARs · no urgent safety measures.</b>") else "See SAE log for detail."`</div>
</div>

<div class="sw-cell wd">
<div class="lab2">Participant withdrawals</div>
<div class="big">`r fmt_int(n_wd)`<small> / `r fmt_int(n_rand)`</small></div>
<div class="det">

```{r wd-detail}
if (!is.null(wd_log) && nrow(wd_log) > 0) {
  fmt_wd_date <- function(x) {
    d <- suppressWarnings(as.Date(as.character(x)))
    ifelse(is.na(d),
           ifelse(is.na(x) | !nzchar(trimws(as.character(x))), "—",
                  trimws(as.character(x))),
           format(d, "%d %b %Y"))
  }
  dates   <- if ("cos_date" %in% names(wd_log)) fmt_wd_date(wd_log$cos_date)
             else rep("—", nrow(wd_log))
  types <- if (!is.na(wd_reason_col)) as.character(wd_log[[wd_reason_col]]) else rep("Withdrawal", nrow(wd_log))
  types[is.na(types) | !nzchar(types)] <- "Type not recorded"
  # Free-text withdrawal reason (REDCap cos_withdraw_rsn_oth via
  # change_of_status_reason) — shown alongside the coded type.
  reasons <- if ("cos_reason" %in% names(wd_log)) as.character(wd_log$cos_reason)
             else rep(NA_character_, nrow(wd_log))
  has_reason <- any(!is.na(reasons) & nzchar(trimws(reasons)))
  reasons[is.na(reasons) | !nzchar(trimws(reasons))] <- "—"
  sites <- if ("site_name" %in% names(wd_log)) as.character(wd_log$site_name) else rep("", nrow(wd_log))
  has_site <- any(nzchar(sites) & !is.na(sites))
  cat('<table class="rt" style="margin-top:2px"><thead><tr><th class="l">Date withdrawn</th><th class="l">Type</th>',
      if (has_reason) '<th class="l">Reason</th>' else "",
      if (has_site) '<th class="l">Site</th>' else "", '</tr></thead><tbody>', sep = "")
  for (i in seq_len(nrow(wd_log))) {
    cat(sprintf('<tr><td class="sn">%s</td><td class="l">%s</td>%s%s</tr>',
                esc(dates[i]), esc(types[i]),
                if (has_reason) sprintf('<td class="l">%s</td>', esc(reasons[i])) else "",
                if (has_site) sprintf('<td class="l">%s</td>', esc(sites[i])) else ""))
  }
  cat("</tbody></table>")
  cat('<div style="margin-top:6px"><b>Full consent retained for outcome data collection.</b></div>')
} else cat("No withdrawals to date.")
```

</div>
</div>

</div>

```{r sae-log}
sl <- rd$sae_log
if (!is.null(sl) && nrow(sl) > 0) {
  cols <- c(record_id = "Participant", site_name = "Site",
            reported = "Reported", diagnosis = "Diagnosis",
            soc = "System organ class", category = "Category",
            severity = "Severity", outcome = "Outcome",
            related = "Causality", expected = "Expectedness",
            death_yn = "Death", death = "Death date")
  # Columns carrying at least one value render (keeps the table narrow);
  # if no detail column has data yet, show them all with "—" placeholders.
  present  <- names(cols)[names(cols) %in% names(sl)]
  has_data <- present[vapply(present, function(cc)
    any(!is.na(sl[[cc]]) & nzchar(trimws(as.character(sl[[cc]])))), logical(1))]
  if (length(setdiff(has_data, c("record_id", "site_name"))) > 0)
    present <- has_data
  if (length(present) > 0) {
    fmt_cell <- function(x) {
      x <- trimws(as.character(x))
      ifelse(is.na(x) | !nzchar(x), "—", x)
    }
    cat('<p class="lab" style="margin-top:8px">SAE log — TMG export</p>')
    cat('<table class="rt"><thead><tr>',
        paste(sprintf('<th class="l">%s</th>', cols[present]), collapse = ""),
        '</tr></thead><tbody>', sep = "")
    for (i in seq_len(nrow(sl))) {
      vals <- vapply(present, function(cc) esc(fmt_cell(sl[[cc]][i])), character(1))
      cat(sprintf('<tr>%s</tr>',
                  paste(sprintf('<td class="l">%s</td>', vals), collapse = "")))
    }
    cat("</tbody></table>")
  }
}
```

<h2 class="sec">

<span class="num">08</span> Demographics <span class="hint">n = `r fmt_int(n_rand)` participants randomised</span>

</h2>

<div class="row2">
<div class="card">
<div class="ct">Age at operation</div>
<div class="demo">

```{r age-chips}
ad <- demo$age
if (!is.null(ad)) {
  u70 <- safe(ad$under_70, 0); o70 <- safe(ad$over_70, 0); tot <- u70 + o70
  pu <- if (tot > 0) round(u70/tot*100) else 0
  po <- if (tot > 0) round(o70/tot*100) else 0
  cat(sprintf('<div class="chip" style="background:var(--teal-tint)"><b style="color:var(--teal)">%d</b><span>Under 70 (%d%%)</span></div>', u70, pu))
  cat(sprintf('<div class="chip"><b>%d</b><span>70 and over (%d%%)</span></div>', o70, po))
} else cat('<div class="chip"><b>—</b><span>No age data</span></div>')
```

</div>
<div class="note" style="margin-top:8px">Median age at randomisation broadly mirrors NELA emergency-laparotomy population.</div>
</div>

<div class="card">
<div class="ct">NELA 30-day predicted mortality</div>
<div class="demo">

```{r nela-chips}
nd <- demo$nela
if (!is.null(nd)) {
  u5 <- safe(nd$under_5, 0); o5 <- safe(nd$over_5, 0); tot <- u5 + o5
  pu <- if (tot > 0) round(u5/tot*100) else 0
  po <- if (tot > 0) round(o5/tot*100) else 0
  cat(sprintf('<div class="chip" style="background:var(--teal-tint)"><b style="color:var(--teal)">%d</b><span>Under 5%% (%d%%)</span></div>', u5, pu))
  cat(sprintf('<div class="chip"><b>%d</b><span>5%% and over (%d%%)</span></div>', o5, po))
} else cat('<div class="chip"><b>—</b><span>No NELA data</span></div>')
```

</div>
<div class="note" style="margin-top:8px">Even split across the standard NELA risk stratum — monitoring for balance at randomisation.</div>
</div>

</div>

<div class="card" style="margin-top:14px">
  <div class="ct">Ethnicity</div>
  <div class="eth-split">
    <div class="eth-donut"><canvas id="ethC"></canvas></div>
    <div class="eth-legend">
```{r eth-legend}
if (!is.null(eth_tbl) && nrow(eth_tbl) > 0) {
  for (i in seq_len(nrow(eth_tbl))) {
    col <- eth_hex[((i-1) %% length(eth_hex)) + 1]
    cat(sprintf('<div class="row"><span class="sw" style="background:%s"></span><span class="nm">%s</span><span class="vl"><b>%d</b> · %.0f%%</span></div>',
                col, esc(eth_short(eth_tbl$ethnicity[i])), eth_tbl$n[i], eth_tbl$pct[i]))
  }
} else cat('<div class="note">No ethnicity data available.</div>')
```
    </div>
  </div>
```{r eth-note}
eth <- demo$ethnicity
if (!is.null(eth)) {
  w <- safe(eth$white, 0); m <- safe(eth$minority, 0)
  if (m > 0) {
    g <- round(w/m, 1)
    cat(sprintf('<div class="note" style="margin-top:8px">White : ethnic-minority ratio <b style="color:var(--navy);font-style:normal">%g : 1</b> · representative spread will be re-reviewed at pilot end.</div>', g))
  }
}
```
</div>

```{r page4-footer}
pf_footer(4)
```

</section>

<!-- ============================================================
     PAGE 5 — PILOT PROGRESSION THRESHOLDS
============================================================== -->

<section class="page">

```{r page5-header}
ph_header("Page 5 — Pilot thresholds")
```

<h2 class="sec" style="margin-top:0">

<span class="num">09</span> Pilot progression thresholds <span class="hint">Decisions reviewed at 6-month pilot end · `r esc(pilot_end)`</span>

</h2>

<p class="note" style="font-style:normal;color:var(--ink-2);margin:2px 0 6px;font-size:9pt;line-height:1.5">

Six pre-specified criteria. Performance against each lands in one of three bands — <b style="color:var(--red)">Stop</b>, <b style="color:var(--amber)">Modify</b>, or <b style="color:var(--green)">Proceed</b>. The TMG and oversight committee use this together to decide whether to continue, adapt, or stop the trial after the pilot phase.

</p>

<div class="card" style="padding:6px 14px">
```{r thresholds}
for (i in seq_along(thr)) {
  t <- thr[[i]]
  bv <- band_for(i)
  current_band <- bv$band
  val <- bv$val
  val_note <- if (!is.na(val))
    sprintf(' <span style="display:block;font-size:8pt;font-weight:500;margin-top:1px">(%s to date)</span>', fmt_pct(val, 0)) else ""
  is_now <- function(b) identical(current_band, b)
  band_html <- function(b, lbl, txt, extra = "") {
    now_cls <- if (is_now(b)) " now" else ""
    lb_txt  <- if (is_now(b)) sprintf("%s · current", lbl) else lbl
    sprintf('<div class="thr-band %s%s"><span class="lb">%s</span>%s%s</div>',
            b, now_cls, esc(lb_txt), txt, if (is_now(b)) extra else "")
  }
  cat(sprintf('<div class="thr-row"><div class="thr-name">%d · %s<span class="det">%s</span></div><div class="thr-bands">%s%s%s</div></div>',
              i, esc(t$name), esc(t$det),
              band_html("stop", "Stop",   esc(t$stop_lbl), val_note),
              band_html("mod",  "Modify", esc(t$mod_lbl),  val_note),
              band_html("go",   "Proceed",esc(t$go_lbl),   val_note)))
}
```
</div>

```{r page5-footer}
pf_footer(5)
```

</section>

<!-- ============================================================
     PAGE 6 — RECRUITMENT OUTLOOK
============================================================== -->

<section class="page">

```{r page6-header}
ph_header("Page 6 — Recruitment outlook")
```

<h2 class="sec" style="margin-top:0">

<span class="num">10</span> Recruitment outlook <span class="hint">Protocol projection · `r format(Sys.Date(), "%b %Y")` → `r esc(full_end)`</span>

</h2>

<div class="ol-status `r rec_band`">
<div class="icon">
`r if (rec_band == "green") "✓" else if (rec_band == "amber") "!" else "×"`
</div>

<div class="txt">
<div class="h">
`r if (rec_band == "green") sprintf("On track — %.0f%% of protocol target at this point", safe(rec_pct, 0)) else if (rec_band == "amber") sprintf("Near track — %.0f%% of protocol target", safe(rec_pct, 0)) else sprintf("Behind track — %.0f%% of protocol target", safe(rec_pct, 0))`
</div>

<div class="s">
<b style="color:var(--navy)">`r fmt_int(n_rand)` randomised</b> against <b style="color:var(--navy)">`r fmt_int(exp_to_date)` expected</b> by `r esc(format(Sys.Date(), "%d %b %Y"))` · `r fmt_int(n_open_sites)` site`r if (n_open_sites == 1) "" else "s"` open.
</div>
</div>
</div>

<div class="ol-chart">
<div class="h"><span>Cumulative recruitment · `r format(Sys.Date(), "%b %Y")` → `r esc(full_end)` <b>(`r fmt_int(n_target)` target)</b></span><span>Source: protocol schedule</span></div>

<div class="ol-chart-wrap">
<canvas id="outlookC">

</canvas>
</div>

<div class="ol-leg"><span class="lg"><span class="ln"></span>Cumulative target (protocol)</span><span class="lg"><span class="sw" style="background:var(--teal)"></span>Actual randomised</span></div>
</div>


<p class="note" style="margin-top:8px">

Projections from the original application. Project month re-baselined to the current timeline; monthly targets unchanged at this stage. Follow-up runs to Sep 2028, database lock Nov 2028, analysis Jan 2029, close-out Feb 2029 — see milestones on page 1.

</p>

```{r page6-footer}
pf_footer(6)
```

</section>
</div>

<script>
(function(){
  if (typeof Chart === 'undefined') return;
  const navy = '#01344F', muted = '#6a7d8a', teal = '#12A192';
  Chart.defaults.font.family = 'Calibri, Segoe UI, system-ui, sans-serif';
  Chart.defaults.font.size = 10;
  Chart.defaults.color = muted;

  const labels = `r j(chart_labels)`;
  const target = `r j(chart_target)`;
  const actual = `r j(chart_actual)`;

  // Value labels drawn above bars. chart.js ships no datalabels plugin and the
  // report loads a single CDN bundle, so this is a local, per-chart plugin.
  const valueLabels = (dsIndex) => ({
    id: 'valueLabels',
    afterDatasetsDraw(chart) {
      const ctx = chart.ctx, ds = chart.data.datasets[dsIndex];
      const meta = chart.getDatasetMeta(dsIndex);
      if (!ds || meta.hidden) return;
      meta.data.forEach((el, i) => {
        const v = ds.data[i];
        if (v === null || v === undefined) return;
        ctx.save();
        ctx.font = '700 9.5px ' + Chart.defaults.font.family;
        ctx.fillStyle = navy;
        ctx.textAlign = 'center';
        ctx.textBaseline = 'bottom';
        ctx.fillText(v, el.x, el.y - 3);
        ctx.restore();
      });
    }
  });

  // Headline figure in the middle of a doughnut.
  const centreText = (big, small, colour) => ({
    id: 'centreText',
    afterDraw(chart) {
      const ctx = chart.ctx, a = chart.chartArea;
      const x = (a.left + a.right) / 2, y = (a.top + a.bottom) / 2;
      ctx.save();
      ctx.textAlign = 'center';
      ctx.textBaseline = 'middle';
      ctx.fillStyle = colour;
      ctx.font = "700 22px 'Source Serif 4', Georgia, serif";
      ctx.fillText(big, x, y - 4);
      ctx.fillStyle = muted;
      ctx.font = '600 8.5px ' + Chart.defaults.font.family;
      ctx.fillText(small, x, y + 11);
      ctx.restore();
    }
  });

  // Page 2: monthly randomisations across the whole recruitment window.
  // Cumulative recruitment is not repeated here — section 10 carries it.
  const monEl = document.getElementById('monC');
  if (monEl) {
    const diffs = (xs) => xs.map((v, i) => {
      if (v == null) return null;
      const prev = i > 0 ? (xs[i-1] || 0) : 0;
      return v - prev;
    });
    new Chart(monEl, {
      type:'bar',
      data:{
        labels: labels,
        datasets:[
          {label:'Randomised', data: diffs(actual), backgroundColor: teal, borderRadius:3, maxBarThickness:22, order:1},
          {label:'Monthly target (protocol)', data: diffs(target), backgroundColor:'#eef2f5', borderRadius:3, maxBarThickness:22, order:2}
        ]
      },
      plugins:[valueLabels(0)],
      options:{
        responsive:true, maintainAspectRatio:false, layout:{padding:{top:18}},
        plugins:{
          legend:{display:true,labels:{boxWidth:12,boxHeight:12,padding:10,font:{size:9.5}}},
          tooltip:{callbacks:{label:c=>c.dataset.label+': '+(c.parsed.y||0)}}
        },
        scales:{
          x:{grid:{display:false},border:{display:false},ticks:{maxRotation:60,minRotation:60,autoSkip:false,font:{size:7.5}}},
          y:{beginAtZero:true,grid:{color:'#eef2f5'},border:{display:false},title:{display:true,text:'Participants randomised',font:{size:9.5,weight:600}},ticks:{padding:4}}
        }
      }
    });
  }

  // Page 4: ethnicity doughnut
  const ethEl = document.getElementById('ethC');
  if (ethEl) {
    const ethLabels = `r ja(eth_labels_js)`;
    const ethCounts = `r ja(eth_n_js)`;
    const ethCols   = `r ja(eth_hex)`;
    const ethMinPct = `r if (is.na(eth_min_pct)) "null" else eth_min_pct`;
    if (ethCounts.length) {
      new Chart(ethEl, {
        type:'doughnut',
        data:{labels: ethLabels, datasets:[{data: ethCounts, backgroundColor: ethCols, borderColor:'#fff', borderWidth:2}]},
        plugins: ethMinPct === null ? [] : [centreText(ethMinPct + '%', 'ethnic minority', teal)],
        options:{
          responsive:true, maintainAspectRatio:false, cutout:'58%',
          plugins:{legend:{display:false},tooltip:{callbacks:{label:c=>c.label+': '+c.parsed}}}
        }
      });
    }
  }

  // Page 6: outlook chart
  const outlookEl = document.getElementById('outlookC');
  if (outlookEl) {
    new Chart(outlookEl, {
      data:{
        labels: labels,
        datasets:[
          {type:'line', label:'Target', data: target, borderColor: navy, borderWidth:2, borderDash:[6,4], pointRadius:0, fill:false, tension:.2, order:2},
          {type:'line', label:'Actual', data: actual, borderColor: teal, backgroundColor:'rgba(18,161,146,.18)', borderWidth:2.5, pointBackgroundColor: teal, pointBorderColor:'#fff', pointBorderWidth:1.5, pointRadius:4, fill:'origin', tension:.3, spanGaps:false, order:1}
        ]
      },
      options:{
        responsive:true, maintainAspectRatio:false,
        interaction:{mode:'index', intersect:false},
        plugins:{legend:{display:false}},
        scales:{
          x:{grid:{display:false},border:{display:false},ticks:{maxRotation:0,autoSkip:true,font:{size:8.5}}},
          y:{beginAtZero:true,grid:{color:'#eef2f5'},border:{display:false},title:{display:true,text:'Cumulative randomised',color: muted,font:{size:9,weight:600}},ticks:{padding:4,font:{size:9}}}
        }
      }
    });
  }
})();
</script>
