---
title: "PANORAMA WP4 TMG Progress Report"
output:
  html_document:
    theme: null
    highlight: null
    mathjax: null
    self_contained: true
    md_extensions: "-markdown_in_html_blocks"
params:
  report_data: NULL
  selected_sites: "All sites"
  date_from: NULL
  date_to: NULL
  include_withdrawn: false
  include_appendix: false
  report_date: !r format(Sys.Date(), "%d %B %Y")
  logo_path: NULL
  nihr_logo_path: NULL
  crf_csv_path: NULL
  screening_xlsx_path: NULL
  report_type: "TMG"
  completeness_style: "heatmap"
  report_content: NULL
  column_labels: NULL
  work_package: NULL
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, results = "asis")

`%||%` <- function(a, b) if (is.null(a) || length(a) == 0) b else a
safe  <- function(x, fallback = NA) if (is.null(x) || length(x) == 0) fallback else x
esc   <- function(s) htmltools::htmlEscape(as.character(s))
num   <- function(x) stats::setNames(
  suppressWarnings(as.numeric(as.character(x))), names(x))
blank <- function(x) is.na(x) | !nzchar(trimws(as.character(x)))
# Formatters are vectorised and NA-safe: every one returns an em dash where a
# value is missing, so a partially populated export never breaks a table.
fmt_pct <- function(x, dp = 0) {
  v <- suppressWarnings(as.numeric(x))
  if (length(v) == 0) return("—")
  ifelse(is.na(v), "—", paste0(formatC(v, format = "f", digits = dp), "%"))
}
fmt_int <- function(x) {
  v <- suppressWarnings(as.numeric(x))
  if (length(v) == 0) return("—")
  ifelse(is.na(v), "—", formatC(round(v), format = "d", big.mark = ","))
}
fmt_num <- function(x, dp = 1) {
  v <- suppressWarnings(as.numeric(x))
  if (length(v) == 0) return("—")
  ifelse(is.na(v), "—", formatC(v, format = "f", digits = dp))
}
fmt_date <- function(d, f = "%d %b %Y") {
  d <- suppressWarnings(as.Date(d))
  if (length(d) == 0) return("—")
  ifelse(is.na(d), "—", format(d, f))
}
pctg <- function(n, d) if (is.null(d) || length(d) == 0 || is.na(d) || d <= 0)
  NA_real_ else round(n / d * 100, 1)
j <- function(x) {
  if (requireNamespace("jsonlite", quietly = TRUE))
    jsonlite::toJSON(x, na = "null", null = "null", auto_unbox = TRUE)
  else paste0("[", paste(ifelse(is.na(x), "null", x), collapse = ","), "]")
}

rd  <- params$report_data    %||% list()
rc  <- params$report_content %||% list()
kpi <- rd$kpis %||% list()

# ── Study identity ───────────────────────────────────────────────────────────
# Work-package context: which WP this report covers, and its own target,
# follow-up length and outcome measures. Supplied by the dashboard from the
# active WP pill; falls back to WP4, the cohort study.
wp <- params$work_package %||% list()
trial_short  <- safe(rc$short_name, "PANORAMA")
wp_code      <- safe(wp$code,  safe(rc$work_package_code, "WP4"))
wp_name      <- safe(wp$label, safe(rc$work_package_name, "Cohort study"))
wp_design    <- safe(wp$design, safe(rc$work_package_design,
                                     "Prospective observational cohort"))
wp_outcomes  <- wp$outcomes %||% (rc$work_package_outcomes %||% character(0))
wp_interv    <- safe(wp$interventions, safe(rc$work_package_interventions, ""))
wp_label     <- sprintf("%s · %s", wp_code, wp_name)
wp_long      <- sprintf("Work package %s — %s",
                        sub("^WP", "", wp_code), tolower(wp_name))
trial_title  <- safe(rc$trial_title,
  "oPtimising post-dischArge care pathways after acute paNcreatitis: evaluatiOn of health seRvice utilisAtion, outcoMes")
trial_sub    <- safe(rc$trial_subtitle, sprintf("%s (%s)", wp_long, tolower(wp_design)))
chief_inv    <- safe(rc$ci, "Mr Matthew Lee")
study_mgr    <- safe(rc$study_manager, "Dr Michala Pettitt")
sponsor      <- safe(rc$sponsor, "University of Birmingham")
sponsor_ref  <- safe(rc$sponsor_ref, "RG_25-105")
funder       <- safe(rc$funder, "NIHR HSDR")
funder_ref   <- safe(rc$funder_ref, "NIHR165210")
iras         <- safe(rc$iras, "349680")
cpms         <- safe(rc$cpms, "64883")
protocol_v   <- safe(rc$protocol_version, "v1.1 (11-May-2026)")
fu_months    <- safe(wp$follow_up_months, safe(rc$follow_up_months, 6))
sample_size  <- suppressWarnings(as.integer(
  safe(wp$target, safe(rc$sample_size, safe(kpi$trial_target, 1017)))))
if (is.na(sample_size)) sample_size <- 1017L
sites_plan   <- suppressWarnings(as.integer(safe(rc$sites_planned, NA)))

report_date_str <- params$report_date %||% format(Sys.Date(), "%d %B %Y")
today <- Sys.Date()

# ── Logos (base64) ───────────────────────────────────────────────────────────
encode_logo <- function(path) {
  if (is.null(path) || !nzchar(path) || !file.exists(path) ||
      !requireNamespace("base64enc", quietly = TRUE)) return("")
  ext  <- tolower(tools::file_ext(path))
  mime <- switch(ext, png = "image/png", jpg = "image/jpeg", jpeg = "image/jpeg",
                 svg = "image/svg+xml", "image/png")
  tryCatch(paste0("data:", mime, ";base64,", base64enc::base64encode(path)),
           error = function(e) "")
}
logo_b64 <- encode_logo(params$logo_path)

.this_dir <- tryCatch(dirname(knitr::current_input(dir = TRUE)),
                      error = function(e) ".")
if (is.null(.this_dir) || !length(.this_dir) || is.na(.this_dir)) .this_dir <- "."

.bctu_candidates <- c(
  "BlackText-landscape.png",
  file.path("www", "BlackText-landscape.png"),
  file.path(.this_dir, "BlackText-landscape.png"))
.bctu_hit     <- .bctu_candidates[file.exists(.bctu_candidates)]
bctu_logo_b64 <- if (length(.bctu_hit)) encode_logo(.bctu_hit[1]) else ""

.nihr_candidates <- c(
  params$nihr_logo_path %||% "",
  "NIHR_Acknowledgement_Funded by_Logo_RGB.png",
  file.path("www", "NIHR_Acknowledgement_Funded by_Logo_RGB.png"),
  file.path(.this_dir, "NIHR_Acknowledgement_Funded by_Logo_RGB.png"))
.nihr_candidates <- .nihr_candidates[nzchar(.nihr_candidates)]
.nihr_hit     <- .nihr_candidates[file.exists(.nihr_candidates)]
nihr_logo_b64 <- if (length(.nihr_hit)) encode_logo(.nihr_hit[1]) else ""

# ── Source data ──────────────────────────────────────────────────────────────
# The WP4 metrics are screening- and PROM-based, so they are derived here from
# the REDCap export itself (report_data$raw_df) rather than from the
# randomisation-centric summaries the shared pipeline produces.
raw <- rd$raw_df
if (!is.data.frame(raw) || nrow(raw) == 0) raw <- rd$filtered_df
if (is.null(raw) || !is.data.frame(raw)) raw <- data.frame()
nm <- names(raw)

# ── Field / event map ────────────────────────────────────────────────────────
# Defaults are the WP4 REDCap variable names; override any of them from Trial
# Settings → Report content by supplying rc$fields / rc$events.
F <- utils::modifyList(list(
  record      = "record_id",
  event       = "redcap_event_name",
  site        = c("rc_site_name", "redcap_data_access_group", "site_name"),
  # Candidates, most specific first: find_col() takes the first the export
  # has. The live WP4 export carries cae_age / base_sex / base_ethnic_gp,
  # the project codebook names age / sex / ethnicity.
  age         = c("cae_age", "age"),
  sex         = c("base_sex", "sex"),
  ethnicity   = c("base_ethnic_gp", "ethnicity"),
  aetiology   = "index_panc_aetio",
  screen_calc = "screening_calc",
  approached  = "approached_yn",
  consent     = "valid_consent",
  screen_date = c("screen_created_date", "screen_date", "screen_dt"),
  f_screening = "screening_complete",
  f_consent   = "consent_complete",
  f_demog     = "demographics_past_history_complete",
  f_index     = "index_admission_complete",
  dc_date     = "index_discharge_date",
  prom_dc     = "day_of_discharge_proms_complete",
  prom_d7     = "day7_proms_complete",
  prom_month  = "month_proms_complete",
  withdraw    = "withdraw_level"
), rc$fields %||% list())

E <- utils::modifyList(list(
  d28 = "fu_30_day_arm_1",
  m3  = "fu_3_month_arm_1",
  m6  = "fu_6_month_arm_1"
), rc$events %||% list())

# Withdrawal levels and aetiology codes come from the project codebook via
# params$column_labels; these stay only as a fallback for a report rendered
# before a codebook has been imported.

find_col <- function(...) {
  wants <- unlist(c(...))
  for (w in wants) {
    if (is.null(w) || is.na(w) || !nzchar(w)) next
    if (w %in% nm) return(w)
    hit <- nm[tolower(nm) == tolower(w)]
    if (length(hit)) return(hit[1])
    hit <- grep(paste0("^", w), nm, ignore.case = TRUE, value = TRUE)
    if (length(hit)) return(hit[1])
  }
  NULL
}

rec_col  <- find_col(F$record, "record_id", "study_id", "record_v")
ev_col   <- find_col(F$event, "redcap_event_name", "event_v")
site_col <- find_col(F$site, "rc_site_name", "redcap_data_access_group",
                     "site_name", "site_v")

if (nrow(raw) > 0 && is.null(rec_col)) {
  raw$.rec <- seq_len(nrow(raw)); nm <- names(raw); rec_col <- ".rec"
}
recs <- if (!is.null(rec_col) && nrow(raw) > 0)
  as.character(raw[[rec_col]]) else character(0)
ids  <- unique(recs[!blank(recs)])
n_ids <- length(ids)
empty_vec <- function() stats::setNames(rep(NA_character_, n_ids), ids)

# First non-blank value per record, optionally restricted to one REDCap event.
gv <- function(field, event = NULL) {
  out <- empty_vec()
  col <- find_col(field)
  if (is.null(col) || !n_ids) return(out)
  d <- raw
  if (!is.null(event) && nzchar(event)) {
    if (!is.null(ev_col)) {
      d <- d[grepl(paste0("^", event, "$"), as.character(d[[ev_col]]),
                   ignore.case = TRUE), , drop = FALSE]
    } else {
      short <- sub("_arm_[0-9]+$", "", event)
      cand  <- nm[grepl(field, nm, fixed = TRUE) &
                  (grepl(event, nm, fixed = TRUE) | grepl(short, nm, fixed = TRUE))]
      if (!length(cand)) return(out)
      col <- cand[1]
    }
  }
  if (!nrow(d)) return(out)
  v <- as.character(d[[col]]); r <- as.character(d[[rec_col]])
  keep <- !blank(v) & !blank(r)
  v <- v[keep]; r <- r[keep]
  if (!length(v)) return(out)
  first <- !duplicated(r)
  r <- r[first]; v <- v[first]
  keep2 <- r %in% ids
  out[r[keep2]] <- v[keep2]
  out
}
as_date <- function(x) stats::setNames(
  suppressWarnings(as.Date(substr(as.character(x), 1, 10))), names(x))

vlabs    <- rc$value_labels %||% list()
codebook <- params$column_labels %||% list()

# Codebook first (Trial Settings → Demographics & codebook writes it per
# column), then a report-content override, then the built-in default.
lab_for <- function(key, field = NULL, fallback = NULL) {
  col <- if (is.null(field)) NULL else find_col(field)
  if (!is.null(col) && !is.null(codebook[[col]])) {
    cb <- unlist(codebook[[col]])
    cb <- cb[nzchar(as.character(cb))]
    if (length(cb)) return(cb)
  }
  vlabs[[key]] %||% (rc[[paste0(key, "_labels")]] %||% fallback)
}

# ── Screening funnel ─────────────────────────────────────────────────────────
v_screen <- gv(F$screen_calc)
v_appr   <- gv(F$approached)
v_cons   <- gv(F$consent)
v_wd     <- gv(F$withdraw)
v_age    <- gv(F$age)
v_sex    <- gv(F$sex)
v_eth    <- gv(F$ethnicity)
v_aetio  <- gv(F$aetiology)
d_screen <- as_date(gv(F$screen_date))
d_disch  <- as_date(gv(F$dc_date))
v_site   <- if (!is.null(site_col)) gv(site_col) else empty_vec()

# Screening and consent both happen inside REDCap, so the form-completion
# flags define the funnel:
#   screening_complete = 2                          -> screened
#   screening_complete = 2 AND consent_complete = 2  -> recruited (consented)
#   screening_complete = 2, consent_complete 0/blank -> screened only
# The old rule (valid_consent = 1) stays as the fallback for an export taken
# before those flags existed.
v_scr_done  <- num(gv(F$f_screening))
v_cons_done <- num(gv(F$f_consent))
has_form_flags <- !all(is.na(v_scr_done))

has_screen_col <- !all(is.na(v_screen))
screened_ids <- if (has_form_flags) {
  ids[which(v_scr_done == 2)]
} else if (has_screen_col) ids[!is.na(v_screen)] else ids
elig_ids     <- ids[which(num(v_screen) == 4)]
appr_ids     <- ids[which(num(v_appr) == 1)]
cons_ids     <- if (has_form_flags) {
  ids[which(v_scr_done == 2 & v_cons_done == 2)]
} else ids[which(num(v_cons) == 1)]
if (!has_form_flags && !length(cons_ids) && all(is.na(v_cons)))
  cons_ids <- ids                                              # consent field absent
scr_only_ids <- setdiff(screened_ids, cons_ids)
# Withdrawal only means anything for someone who consented.
wd_ids       <- intersect(ids[!is.na(v_wd)], cons_ids)
active_ids   <- setdiff(cons_ids, wd_ids)

n_screened <- length(screened_ids)
n_elig     <- length(elig_ids)
n_inelig   <- max(0, n_screened - n_elig)
n_appr     <- length(appr_ids)
n_cons     <- length(cons_ids)
n_scr_only <- length(scr_only_ids)
n_wd       <- length(wd_ids)
n_active   <- length(active_ids)

pct_elig    <- pctg(n_elig, n_screened)
pct_appr    <- pctg(n_appr, n_elig)
pct_cons    <- pctg(n_cons, n_appr)
pct_recruit <- pctg(n_cons, n_elig)
pct_target  <- pctg(n_cons, sample_size)
wd_rate     <- pctg(n_wd, n_cons)
retention   <- if (is.na(wd_rate)) NA_real_ else round(100 - wd_rate, 1)

wd_labels <- lab_for("withdraw", F$withdraw,
                     c("1" = "No study intervention",
                       "2" = "No study-related follow-up",
                       "3" = "No further data collection"))
wd_tbl <- if (n_wd > 0) {
  code <- as.character(v_wd[wd_ids])
  lbl  <- ifelse(code %in% names(wd_labels), wd_labels[code],
                 paste("Level", code))
  tb <- as.data.frame(table(lbl), stringsAsFactors = FALSE)
  names(tb) <- c("level", "n")
  tb[order(-tb$n), , drop = FALSE]
} else NULL

# ── Sites ────────────────────────────────────────────────────────────────────
site_of <- function(v) {
  s <- as.character(v_site[v]); s[blank(s)] <- "Not recorded"; s
}
site_tbl <- NULL
if (n_screened > 0 && !all(is.na(v_site))) {
  all_sites <- sort(unique(site_of(screened_ids)))
  site_tbl <- data.frame(
    site      = all_sites,
    screened  = vapply(all_sites, function(s) sum(site_of(screened_ids) == s), integer(1)),
    eligible  = vapply(all_sites, function(s) sum(site_of(elig_ids)     == s), integer(1)),
    approached= vapply(all_sites, function(s) sum(site_of(appr_ids)     == s), integer(1)),
    consented = vapply(all_sites, function(s) sum(site_of(cons_ids)     == s), integer(1)),
    stringsAsFactors = FALSE)
  site_tbl$rate <- mapply(pctg, site_tbl$consented, site_tbl$eligible)
  last_dt <- vapply(all_sites, function(s) {
    d <- d_screen[cons_ids][site_of(cons_ids) == s]
    d <- d[!is.na(d)]
    if (!length(d)) NA_real_ else as.numeric(max(d))
  }, numeric(1))
  site_tbl$last <- as.Date(last_dt, origin = "1970-01-01")
  site_tbl <- site_tbl[order(-site_tbl$consented, -site_tbl$screened), , drop = FALSE]
}
n_sites_open <- if (!is.null(site_tbl))
  sum(site_tbl$site != "Not recorded") else safe(kpi$n_sites_active, NA)

# ── Recruitment over time ────────────────────────────────────────────────────
rec_dates <- d_screen[cons_ids]
rec_dates <- rec_dates[!is.na(rec_dates)]
first_rec <- if (length(rec_dates)) min(rec_dates) else NA
last_rec  <- if (length(rec_dates)) max(rec_dates) else NA

plan_start <- suppressWarnings(as.Date(safe(rc$recruitment_start, NA)))
if (is.na(plan_start))
  plan_start <- if (!is.na(first_rec)) as.Date(format(first_rec, "%Y-%m-01")) else
    as.Date(format(today, "%Y-%m-01"))
plan_months <- suppressWarnings(as.integer(safe(rc$recruitment_months, 18)))
if (is.na(plan_months) || plan_months < 1) plan_months <- 18L

months_seq <- seq(plan_start, by = "1 month", length.out = plan_months)
cum_target <- round(seq_len(plan_months) / plan_months * sample_size)
month_lab  <- format(months_seq, "%b %y")

month_actual <- vapply(months_seq, function(m) {
  nxt <- seq(m, by = "1 month", length.out = 2)[2]
  sum(rec_dates >= m & rec_dates < nxt)
}, integer(1))
cum_actual <- cumsum(month_actual)
cur_month  <- as.Date(format(today, "%Y-%m-01"))
cum_actual_plot <- as.numeric(cum_actual)
cum_actual_plot[months_seq > cur_month] <- NA
month_actual_plot <- as.numeric(month_actual)
month_actual_plot[months_seq > cur_month] <- NA

# Expected to date: last complete month's target plus a pro-rata share of the
# current month's increment.
past <- which(months_seq <= cur_month)
expected_to_date <- if (length(past)) {
  i <- max(past)
  prev <- if (i > 1) cum_target[i - 1] else 0
  m_days <- as.numeric(seq(months_seq[i], by = "1 month", length.out = 2)[2] - months_seq[i])
  frac <- min(1, max(0, (as.numeric(today - months_seq[i]) + 1) / m_days))
  round(prev + frac * (cum_target[i] - prev))
} else 0
pct_vs_plan <- pctg(n_cons, expected_to_date)

months_active <- length(past)
# A rate needs a period to measure over, and that comes from the registration
# dates. With none in the export, months_active falls back to the current month
# alone and every consented participant lands in it — reporting the whole
# cohort as this month's rate. Report it as unknown instead.
rate_per_month <- if (months_active > 0 && length(rec_dates))
  round(n_cons / months_active, 1) else NA
rate_site_month <- if (!is.na(rate_per_month) && !is.na(n_sites_open) &&
                       n_sites_open > 0) round(rate_per_month / n_sites_open, 2) else NA
remaining <- max(0, sample_size - n_cons)
months_to_target <- if (!is.na(rate_per_month) && rate_per_month > 0)
  ceiling(remaining / rate_per_month) else NA
# A projection more than ten years out says only that the current rate is far
# below plan, so report that rather than printing an implausible date.
if (!is.na(months_to_target) && months_to_target > 120) months_to_target <- NA
proj_end <- if (!is.na(months_to_target))
  seq(cur_month, by = "1 month", length.out = months_to_target + 1)[months_to_target + 1] else NA

# ── Demographics ─────────────────────────────────────────────────────────────
age_v <- num(v_age[cons_ids]); age_v <- age_v[!is.na(age_v)]
age_stats <- if (length(age_v)) list(
  n = length(age_v), mean = mean(age_v), median = stats::median(age_v),
  q1 = unname(stats::quantile(age_v, .25)), q3 = unname(stats::quantile(age_v, .75)),
  min = min(age_v), max = max(age_v)) else NULL
age_bands <- if (length(age_v)) {
  br <- c(-Inf, 39, 54, 69, 79, Inf)
  lb <- c("16–39", "40–54", "55–69", "70–79", "80+")
  tb <- table(cut(age_v, breaks = br, labels = lb))
  data.frame(band = names(tb), n = as.integer(tb), stringsAsFactors = FALSE)
} else NULL

# Categorical summaries. Codes are mapped through the trial's codebook
# (rc$value_labels / the *_labels lists); anything unmapped is shown as its
# raw code so a gap in the codebook is visible rather than silently dropped.
cat_tbl <- function(v, labels, who) {
  x <- as.character(v[who]); x <- x[!blank(x)]
  if (!length(x)) return(NULL)
  lbl <- if (!is.null(labels) && length(labels))
    ifelse(x %in% names(labels), labels[x], paste("Code", x)) else x
  tb <- as.data.frame(table(lbl), stringsAsFactors = FALSE)
  names(tb) <- c("label", "n")
  tb$pct <- round(tb$n / length(x) * 100, 1)
  tb[order(-tb$n), , drop = FALSE]
}

aetio_labels <- lab_for("aetiology", F$aetiology, c(
  "1" = "Gallstones", "2" = "Alcohol", "3" = "Drug related",
  "4" = "Idiopathic", "5" = "Other", "-99" = "Unknown"))
sex_labels <- lab_for("sex", F$sex, c("1" = "Female", "2" = "Male",
                                      "3" = "Not disclosed / not known"))
eth_labels <- lab_for("ethnicity", F$ethnicity, NULL)

aetio_tbl <- cat_tbl(v_aetio, aetio_labels, cons_ids)
sex_tbl   <- cat_tbl(v_sex,   sex_labels,   cons_ids)
eth_tbl   <- cat_tbl(v_eth,   eth_labels,   cons_ids)
unmapped_n <- function(tb) if (is.null(tb)) 0 else sum(grepl("^Code ", tb$label))
n_aetio_unmapped <- unmapped_n(aetio_tbl)
n_codebook_gaps  <- n_aetio_unmapped + unmapped_n(sex_tbl) + unmapped_n(eth_tbl) +
  (if (!is.null(eth_tbl) && (is.null(eth_labels) || !length(eth_labels)))
     nrow(eth_tbl) else 0)

# ── Form completion (consented participants) ─────────────────────────────────
form_defs <- list(
  list(label = "Screening",                field = F$f_screening),
  list(label = "Consent",                  field = F$f_consent),
  list(label = "Demographics & past history", field = F$f_demog),
  list(label = "Index admission",          field = F$f_index))
form_rows <- do.call(rbind, lapply(form_defs, function(f) {
  v <- num(gv(f$field)[cons_ids])
  data.frame(form = f$label, due = n_cons,
             complete   = sum(v == 2, na.rm = TRUE),
             unverified = sum(v == 1, na.rm = TRUE),
             incomplete = sum(v == 0, na.rm = TRUE),
             missing    = sum(is.na(v)),
             stringsAsFactors = FALSE)
}))
if (!is.null(form_rows)) form_rows$pct <- mapply(pctg, form_rows$complete, form_rows$due)
form_overall <- if (!is.null(form_rows))
  pctg(sum(form_rows$complete), sum(form_rows$due)) else NA

# ── PROM completion / retention ──────────────────────────────────────────────
# A timepoint counts as due once the visit window has closed for that
# participant (days since index discharge). Withdrawn participants are removed
# from the denominator from the point of withdrawal onwards.
tp_defs <- list(
  list(label = "Day of discharge", field = F$prom_dc,    event = NULL,  offset = 0,   window = 0),
  list(label = "Day 7",            field = F$prom_d7,    event = NULL,  offset = 7,   window = 3),
  list(label = "Day 28",           field = F$prom_month, event = E$d28, offset = 28,  window = 3),
  list(label = "3 months",         field = F$prom_month, event = E$m3,  offset = 91,  window = 7),
  list(label = "6 months",         field = F$prom_month, event = E$m6,  offset = 182, window = 7))

prom_rows <- do.call(rbind, lapply(tp_defs, function(t) {
  v   <- num(gv(t$field, t$event))
  dcd <- d_disch[active_ids]
  due_ids2 <- active_ids[!is.na(dcd) &
                         today >= (dcd + t$offset + t$window)]
  due <- length(due_ids2)
  comp <- sum(v[due_ids2] == 2, na.rm = TRUE)
  part <- sum(v[due_ids2] == 1, na.rm = TRUE)
  data.frame(timepoint = t$label, due = due, complete = comp, partial = part,
             outstanding = max(0, due - comp - part),
             pct = pctg(comp, due), stringsAsFactors = FALSE)
}))
prom_overall <- if (!is.null(prom_rows))
  pctg(sum(prom_rows$complete), sum(prom_rows$due)) else NA
prom_m6 <- if (!is.null(prom_rows)) prom_rows$pct[prom_rows$timepoint == "6 months"] else NA
if (length(prom_m6) == 0) prom_m6 <- NA_real_

n_no_dc_date <- sum(is.na(d_disch[cons_ids]))

# ── RAG bands ────────────────────────────────────────────────────────────────
band <- function(v, green, amber, higher_better = TRUE) {
  if (is.null(v) || length(v) == 0 || is.na(v)) return("n")
  if (higher_better) { if (v >= green) "g" else if (v >= amber) "a" else "r" }
  else { if (v <= green) "g" else if (v <= amber) "a" else "r" }
}
band_word <- function(b) switch(b, g = "ON TRACK", a = "MONITOR", r = "ACTION", "PENDING")

health_cards <- list(
  list(title = "Recruitment vs plan", val = pct_vs_plan,
       sub = sprintf("%s of %s expected", fmt_int(n_cons), fmt_int(expected_to_date)),
       b = band(pct_vs_plan, 90, 70)),
  list(title = "Eligible approached", val = pct_appr,
       sub = sprintf("%s of %s eligible", fmt_int(n_appr), fmt_int(n_elig)),
       b = band(pct_appr, 80, 60)),
  list(title = "Approached consented", val = pct_cons,
       sub = sprintf("%s of %s approached", fmt_int(n_cons), fmt_int(n_appr)),
       b = band(pct_cons, 60, 40)),
  list(title = "Form completion", val = form_overall,
       sub = "baseline CRFs, consented participants",
       b = band(form_overall, 95, 85)),
  list(title = "PROM return", val = prom_overall,
       sub = "all timepoints due to date",
       b = band(prom_overall, 80, 60)),
  list(title = "Retention", val = retention,
       sub = sprintf("%s withdrawal%s recorded", fmt_int(n_wd),
                     if (identical(n_wd, 1L)) "" else "s"),
       b = band(retention, 85, 75)))

# ── Milestones ───────────────────────────────────────────────────────────────
ms <- rc$key_milestones %||% list(
  list(name = "Funding award (NIHR165210)",        date = "2025",          status = "complete",  group = "Set-up"),
  list(name = "Protocol v1.1 finalised",           date = "11 May 2026",   status = "complete",  group = "Set-up"),
  list(name = "REC / HRA approval",                date = "TBC",           status = "upcoming",  group = "Set-up"),
  list(name = "REDCap database live",              date = "TBC",           status = "upcoming",  group = "Set-up"),
  list(name = "First site opened",                 date = "TBC",           status = "upcoming",  group = "Set-up"),
  list(name = "First participant registered",
       date = if (!is.na(first_rec)) format(first_rec, "%d %b %Y") else "TBC",
       status = if (!is.na(first_rec)) "complete" else "upcoming", group = "Recruitment & follow-up"),
  list(name = sprintf("Recruitment complete (n=%s)", format(sample_size, big.mark = ",")),
       date = if (!is.na(proj_end)) format(proj_end, "%b %Y") else
         format(months_seq[plan_months], "%b %Y"),
       status = "estimated", group = "Recruitment & follow-up"),
  list(name = sprintf("Last participant %s-month follow-up", fu_months),
       date = if (!is.na(proj_end))
         format(seq(proj_end, by = "6 months", length.out = 2)[2], "%b %Y") else "TBC",
       status = "estimated", group = "Recruitment & follow-up"),
  list(name = "Database lock",                     date = "TBC",           status = "estimated", group = "Analysis & close-out"),
  list(name = "Analysis complete",                 date = "TBC",           status = "estimated", group = "Analysis & close-out"))
ms_complete <- Filter(function(m) identical(m$status, "complete"), ms)

# ── Chart payloads ───────────────────────────────────────────────────────────
funnel_labels <- c("Screened", "Eligible", "Approached", "Consented")
funnel_values <- c(n_screened, n_elig, n_appr, n_cons)
prom_labels <- if (!is.null(prom_rows)) prom_rows$timepoint else character(0)
prom_pcts   <- if (!is.null(prom_rows)) prom_rows$pct else numeric(0)
aetio_labels_v <- if (!is.null(aetio_tbl)) aetio_tbl$label else character(0)
aetio_values_v <- if (!is.null(aetio_tbl)) aetio_tbl$n else numeric(0)
age_labels_v <- if (!is.null(age_bands)) age_bands$band else character(0)
age_values_v <- if (!is.null(age_bands)) age_bands$n else numeric(0)
```

<style>
:root{
  --lilac:#4C3A82; --lilac-2:#6B57A8; --lilac-tint:#EDE7F8; --lilac-tint-2:#F7F4FC;
  --mauve:#9B7FD4; --mauve-tint:#F0E9FB; --mauve-tint-2:#F8F4FE;
  --ink:#241F33; --ink-2:#4A4363; --muted:#7A7391;
  --line:#E3DCF1; --line-soft:#F0ECF9;
  --green:#2F7F63; --green-tint:#DCEFE7;
  --amber:#B5801F; --amber-tint:#FAECD3;
  --red:#AE3F44; --red-tint:#F8DEE0;
  --grey:#8A85A0; --grey-tint:#EEECF4;
  --pad-page:14mm; --gap-sec:14px; --fs-base:10pt;
}
*{box-sizing:border-box}
html,body{margin:0;padding:0;font-family:Calibri,'Segoe UI',-apple-system,system-ui,sans-serif;color:var(--ink);background:#EDEAF4;font-size:var(--fs-base);-webkit-print-color-adjust:exact;print-color-adjust:exact}
body{padding:24px 0}
.doc{max-width:210mm;margin:0 auto}
.page{background:#fff;width:210mm;min-height:297mm;margin:0 auto 18px;padding:var(--pad-page);position:relative;box-shadow:0 1px 2px rgba(40,25,80,.08),0 8px 24px rgba(40,25,80,.10);border-radius:2px;display:flex;flex-direction:column}
@page{size:A4;margin:11mm 12mm 12mm}
@media print{
  :root{--gap-sec:10px}
  body{background:#fff;padding:0}
  .doc{max-width:none}
  .page{box-shadow:none;margin:0;border-radius:0;width:auto;min-height:273mm;padding:0;page-break-after:always}
  .page:last-child{page-break-after:auto}
  .ph,.card,.row2,.row3,.pc,.meta-strip,.health-strip,.funnel,.ml-grp,.chart-wrap,
  .demo,.note,.keyline,.sw-cell,svg{break-inside:avoid;page-break-inside:avoid}
  h2.sec,p.lab{break-after:avoid-page;page-break-after:avoid;break-inside:avoid}
  table.rt{break-inside:auto;page-break-inside:auto}
  table.rt thead{display:table-header-group}
  table.rt tr{break-inside:avoid;page-break-inside:avoid}
  .pf{break-inside:avoid;page-break-inside:avoid}
}

/* Header / footer */
.ph{display:flex;align-items:center;justify-content:space-between;gap:16px;padding-bottom:10px;border-bottom:2px solid var(--lilac);margin-bottom:12px}
.ph .brand{display:flex;align-items:center;gap:14px;min-width:0}
.ph .ph-trial-logo{height:50px;width:auto;display:block}
.ph .ph-trial-name{font-family:'Source Serif 4',Charter,Georgia,serif;font-size:20pt;font-weight:700;color:var(--lilac);letter-spacing:-.5px;line-height:1}
.ph .brand .tag{font-size:8.5pt;color:var(--muted);line-height:1.35;font-weight:500;border-left:1px solid var(--line);padding-left:14px;max-width:78mm}
.ph .brand .tag b{color:var(--lilac);font-weight:600;display:block;font-size:9.5pt}
.ph .meta{display:flex;flex-direction:column;align-items:flex-end;gap:4px;text-align:right;font-size:8.5pt;color:var(--muted);line-height:1.4;flex-shrink:0}
.ph .ph-bctu-logo{height:30px;width:auto;display:block}
.ph .meta b{color:var(--lilac);font-weight:600}
.pf{display:flex;justify-content:space-between;align-items:center;border-top:1px solid var(--line);padding-top:6px;margin-top:auto;font-size:8pt;color:var(--muted)}
.pf .pn{color:var(--lilac);font-weight:600}
.pf .pf-nihr{height:14px;width:auto;display:block}

.wp-chip{display:inline-block;background:var(--mauve);color:#fff;font-size:7.5pt;font-weight:700;letter-spacing:.08em;text-transform:uppercase;padding:2px 7px;border-radius:3px;vertical-align:middle}

.meta-strip{display:grid;grid-template-columns:repeat(5,minmax(0,1fr));gap:0;background:var(--lilac-tint-2);border:1px solid var(--line);border-radius:6px;padding:7px 12px;margin:0 0 12px}
.meta-strip .mi{padding:0 8px;border-right:1px solid var(--line)}
.meta-strip .mi:last-child{border-right:0}
.meta-strip .mk{font-size:7.5pt;color:var(--muted);font-weight:600;text-transform:uppercase;letter-spacing:.06em}
.meta-strip .mv{font-size:9.5pt;color:var(--lilac);font-weight:600;line-height:1.2;margin-top:1px}
.meta-strip .mv small{font-weight:500;color:var(--muted);font-size:8.5pt}

h1.title{font-family:'Source Serif 4',Charter,Georgia,serif;font-size:24pt;font-weight:700;color:var(--lilac);margin:0 0 6px;letter-spacing:-.5px;line-height:1.1;background:var(--mauve-tint);padding:5px 12px;border-radius:4px}
.sub{font-size:10.5pt;color:var(--ink-2);margin:0 0 12px;font-weight:500}
.sub b{color:var(--lilac)}
h2.sec{font-size:11pt;font-weight:700;color:var(--lilac);margin:var(--gap-sec) 0 6px;letter-spacing:.04em;text-transform:uppercase;display:flex;align-items:baseline;gap:8px;flex-wrap:wrap;padding-bottom:4px;border-bottom:1px solid var(--line)}
h2.sec .num{font-size:8.5pt;color:#fff;background:var(--mauve);padding:1px 6px;border-radius:3px;font-weight:700;letter-spacing:0;flex-shrink:0}
h2.sec .hint{margin-left:auto;font-size:8.5pt;color:var(--muted);font-weight:500;text-transform:none;letter-spacing:0}
p.lab{font-size:8pt;color:var(--muted);font-weight:600;text-transform:uppercase;letter-spacing:.06em;margin:8px 0 4px}

.snap{display:grid;grid-template-columns:repeat(4,1fr);gap:8px;margin:0 0 4px}
.snap .cell{border:1px solid var(--line);border-radius:6px;padding:10px 12px;background:#fff;position:relative;overflow:hidden}
.snap .cell::before{content:"";position:absolute;left:0;top:0;bottom:0;width:3px;background:var(--mauve)}
.snap .cell.lilac::before{background:var(--lilac)}
.snap .cell.green::before{background:var(--green)}
.snap .cell.amber::before{background:var(--amber)}
.snap .cell.red::before{background:var(--red)}
.snap .k{font-size:7.5pt;color:var(--muted);font-weight:600;text-transform:uppercase;letter-spacing:.06em}
.snap .v{font-size:22pt;line-height:1;font-weight:700;color:var(--lilac);font-family:'Source Serif 4',Charter,Georgia,serif;letter-spacing:-.02em;margin-top:3px}
.snap .v small{font-size:11pt;color:var(--muted);font-weight:500;font-family:Calibri,'Segoe UI',sans-serif;letter-spacing:0}
.snap .s{font-size:8pt;color:var(--ink-2);margin-top:2px;line-height:1.25}

.health-strip{display:grid;grid-template-columns:repeat(6,1fr);gap:6px;margin-top:4px}
.pc{border:1px solid var(--line);border-radius:6px;padding:8px 9px 9px;background:#fff}
.pc .pct{font-size:8.5pt;font-weight:600;color:var(--lilac);line-height:1.25;margin:0 0 6px;min-height:24px}
.pc .pcv{font-size:15pt;font-weight:700;line-height:1;font-family:'Source Serif 4',Charter,Georgia,serif;letter-spacing:-.02em}
.pc .pcb{font-size:7.5pt;color:var(--muted);margin-top:3px;line-height:1.3;min-height:20px}
.pc .pcs{display:inline-block;margin-top:6px;font-size:7pt;font-weight:700;padding:1px 6px;border-radius:3px;letter-spacing:.06em}
.pc.g{background:var(--green-tint)} .pc.g .pcv,.pc.g .pcs{color:var(--green)} .pc.g .pcs{background:rgba(47,127,99,.16)}
.pc.a{background:var(--amber-tint)} .pc.a .pcv,.pc.a .pcs{color:var(--amber)} .pc.a .pcs{background:rgba(181,128,31,.18)}
.pc.r{background:var(--red-tint)} .pc.r .pcv,.pc.r .pcs{color:var(--red)} .pc.r .pcs{background:rgba(174,63,68,.16)}
.pc.n{background:var(--grey-tint)} .pc.n .pcv,.pc.n .pcs{color:var(--grey)} .pc.n .pcs{background:rgba(138,133,160,.2)}

.funnel{display:grid;grid-template-columns:repeat(4,1fr);gap:0;margin-top:6px;border:1px solid var(--line);border-radius:6px;overflow:hidden}
.fn-step{padding:10px 12px;background:#fff;position:relative;border-right:1px solid var(--line)}
.fn-step:last-child{border-right:0}
.fn-step .fk{font-size:7.5pt;color:var(--muted);font-weight:600;text-transform:uppercase;letter-spacing:.06em}
.fn-step .fv{font-size:20pt;font-weight:700;color:var(--lilac);font-family:'Source Serif 4',Charter,Georgia,serif;line-height:1;margin-top:2px}
.fn-step .fs{font-size:8pt;color:var(--ink-2);margin-top:3px}
.fn-step .fbar{height:5px;border-radius:20px;background:var(--line-soft);margin-top:7px;overflow:hidden}
.fn-step .fbar span{display:block;height:100%;background:var(--mauve);border-radius:20px}
.fn-step:nth-child(1) .fbar span{background:var(--lilac)}
.fn-step:nth-child(2) .fbar span{background:var(--lilac-2)}
.fn-step:nth-child(4) .fbar span{background:var(--green)}

table.rt{width:100%;border-collapse:collapse;font-size:9pt;margin-top:4px}
table.rt th{background:var(--lilac);color:#fff;text-align:left;padding:6px 10px;font-weight:600;font-size:8.5pt;letter-spacing:.02em}
table.rt th:not(:first-child){text-align:right}
table.rt th.l{text-align:left}
table.rt td{padding:6px 10px;border-bottom:1px solid var(--line-soft)}
table.rt td:not(:first-child){text-align:right}
table.rt td.l{text-align:left}
table.rt tr:nth-child(even) td{background:var(--lilac-tint-2)}
table.rt tr:last-child td{border-bottom:0}
table.rt td.sn{color:var(--lilac);font-weight:500}
table.rt tr.tot td{background:var(--lilac-tint);font-weight:700;color:var(--lilac);border-top:2px solid var(--lilac)}

.pill{display:inline-flex;align-items:center;gap:4px;font-size:8pt;padding:1px 8px;border-radius:11px;font-weight:600}
.pill .dot{width:6px;height:6px;border-radius:50%}
.p-g{background:var(--green-tint);color:var(--green)} .p-g .dot{background:var(--green)}
.p-a{background:var(--amber-tint);color:var(--amber)} .p-a .dot{background:var(--amber)}
.p-r{background:var(--red-tint);color:var(--red)} .p-r .dot{background:var(--red)}
.p-n{background:var(--grey-tint);color:var(--grey)} .p-n .dot{background:var(--grey)}
.p-i{background:var(--mauve-tint);color:var(--lilac)} .p-i .dot{background:var(--mauve)}

.pb{display:flex;align-items:center;gap:8px}
.pb .track{flex:1;height:6px;background:var(--line-soft);border-radius:20px;overflow:hidden}
.pb .fill{height:100%;background:var(--mauve);border-radius:20px}
.pb .lbl{font-size:8pt;font-weight:600;color:var(--lilac);min-width:38px;text-align:right}

.row2{display:grid;grid-template-columns:1fr 1fr;gap:14px}
.row3{display:grid;grid-template-columns:1fr 1fr 1fr;gap:14px}
.card{border:1px solid var(--line);border-radius:6px;padding:10px 12px;background:#fff}
.card .ct{font-size:8.5pt;color:var(--lilac);font-weight:700;text-transform:uppercase;letter-spacing:.06em;margin-bottom:4px}
.chart-wrap{position:relative;height:150px}
.chart-wrap.tall{height:210px}

.demo{display:flex;gap:6px;margin-top:4px}
.demo .chip{flex:1;text-align:center;padding:8px 6px;border-radius:6px;background:var(--lilac-tint-2);border:1px solid var(--line)}
.demo .chip b{display:block;font-size:17pt;font-weight:700;color:var(--lilac);font-family:'Source Serif 4',Charter,Georgia,serif;letter-spacing:-.02em;line-height:1}
.demo .chip span{display:block;font-size:8pt;color:var(--muted);margin-top:3px}

.keyline{display:flex;gap:16px;align-items:baseline;font-size:9pt;background:var(--mauve-tint-2);border-left:3px solid var(--mauve);padding:6px 12px;border-radius:0 4px 4px 0;margin:6px 0 2px;flex-wrap:wrap}
.keyline span{color:var(--muted)}
.keyline span b{color:var(--lilac);font-weight:600}
.note{font-size:8pt;color:var(--muted);font-style:italic;margin-top:6px;line-height:1.4}

.sw-grid{display:grid;grid-template-columns:1fr 2.1fr;gap:12px;margin-top:4px}
.sw-cell{border:1px solid var(--line);border-radius:6px;padding:12px;background:#fff;display:flex;flex-direction:column;gap:4px}
.sw-cell .lab2{font-size:7.5pt;color:var(--muted);font-weight:600;text-transform:uppercase;letter-spacing:.06em}
.sw-cell .big{font-size:28pt;font-weight:700;font-family:'Source Serif 4',Charter,Georgia,serif;line-height:1;letter-spacing:-.02em;color:var(--lilac)}
.sw-cell .big small{font-size:13pt;color:var(--muted);font-family:Calibri,'Segoe UI',sans-serif;font-weight:500}
.sw-cell.ok{background:var(--green-tint);border-color:#bfe0d1} .sw-cell.ok .big{color:var(--green)}
.sw-cell.wd{background:var(--amber-tint);border-color:#eed7a8} .sw-cell.wd .big{color:var(--amber)}
.sw-cell .det{font-size:9pt;color:var(--ink-2);margin-top:4px;line-height:1.45}
.sw-cell .det b{color:var(--lilac);font-weight:600}

.ml-grp{border:1px solid var(--line);border-radius:6px;overflow:hidden;background:#fff;margin-top:4px}
.ml-grp + .ml-grp{margin-top:6px}
.ml-grp-h{display:flex;align-items:center;gap:10px;padding:6px 12px;background:var(--lilac-tint-2);border-bottom:1px solid var(--line);font-size:8.5pt;font-weight:700;color:var(--lilac);letter-spacing:.04em;text-transform:uppercase}
.ml-grp-h .gpcnt{margin-left:auto;font-weight:500;color:var(--muted);letter-spacing:0;text-transform:none}
.ml-row{display:grid;grid-template-columns:1fr 120px 110px;gap:8px;align-items:center;padding:6px 12px;border-top:1px solid var(--line-soft)}
.ml-grp-h + .ml-row{border-top:0}
.ml-row:nth-child(odd){background:#FCFBFE}
.ml-name{font-size:9.5pt;color:var(--lilac);font-weight:500;display:flex;align-items:center;gap:8px}
.ml-name .seq{width:18px;height:18px;border-radius:4px;background:var(--lilac-tint);color:var(--lilac);font-size:7.5pt;font-weight:700;display:inline-flex;align-items:center;justify-content:center;flex-shrink:0}
.ml-date{font-size:9pt;color:var(--ink-2);font-variant-numeric:tabular-nums}
.ml-date.est::before{content:"≈ ";color:var(--muted)}
.ml-st{justify-self:end}
</style>

<link rel="preconnect" href="https://fonts.googleapis.com"> <link rel="preconnect" href="https://fonts.gstatic.com" crossorigin> <link href="https://fonts.googleapis.com/css2?family=Source+Serif+4:wght@600;700&display=swap" rel="stylesheet">

<script src="https://cdn.jsdelivr.net/npm/chart.js@4.4.1/dist/chart.umd.min.js"></script>

<div class="doc">

```{r page-helpers}
ph_header <- function(page_label) {
  trial_logo_html <- if (nchar(logo_b64) > 0)
    sprintf('<img class="ph-trial-logo" src="%s" alt="%s logo">', logo_b64, esc(trial_short))
  else
    sprintf('<span class="ph-trial-name">%s</span>', esc(trial_short))
  bctu_logo_html <- if (nchar(bctu_logo_b64) > 0)
    sprintf('<img class="ph-bctu-logo" src="%s" alt="Birmingham Clinical Trials Unit">',
            bctu_logo_b64) else ""
  meta_line <- if (nzchar(page_label))
    sprintf('<b>%s</b> · %s', esc(report_date_str), esc(page_label))
  else
    sprintf('<b>%s</b> · <span style="color:var(--mauve);font-weight:600">Confidential</span>',
            esc(report_date_str))
  cat(sprintf(
'<header class="ph">
  <div class="brand">%s
    <div class="tag"><b>%s Study</b><span class="wp-chip">%s</span> Trial Management Group · Progress Report</div>
  </div>
  <div class="meta">%s<div>%s</div></div>
</header>',
    trial_logo_html, esc(trial_short), esc(wp_label), bctu_logo_html, meta_line))
}

pf_footer <- function(n_page, n_total = 5) {
  rt  <- safe(params$report_type, "TMG")
  ver <- safe(rc$version, "1.0")
  nihr_html <- if (nchar(nihr_logo_b64) > 0)
    sprintf('<img class="pf-nihr" src="%s" alt="Funded by NIHR">', nihr_logo_b64) else "<span></span>"
  cat(sprintf('<footer class="pf"><span>%s %s %s Progress Report v%s (%s)</span>%s<span class="pn">Page %d of %d</span></footer>',
              esc(trial_short), esc(wp_code), esc(rt), esc(ver),
              format(Sys.Date(), "%d-%b-%Y"), nihr_html, n_page, n_total))
}

meta_strip <- function() {
  cells <- list(
    c("Chief Investigator", esc(chief_inv)),
    c("Sponsor · ref", sprintf('%s <small>· %s</small>', esc(sponsor), esc(sponsor_ref))),
    c("Funder · ref", sprintf('%s <small>· %s</small>', esc(funder), esc(funder_ref))),
    c("IRAS · CPMS", sprintf('%s <small>· %s</small>', esc(iras), esc(cpms))),
    c("Target · follow-up", sprintf('%s <small>· %s months</small>',
                                    fmt_int(sample_size), esc(fu_months))))
  cat('<div class="meta-strip">')
  for (c1 in cells)
    cat(sprintf('<div class="mi"><div class="mk">%s</div><div class="mv">%s</div></div>',
                c1[1], c1[2]))
  cat('</div>')
}

snap_cell <- function(k, v, s, cls = "") {
  cat(sprintf('<div class="cell %s"><div class="k">%s</div><div class="v">%s</div><div class="s">%s</div></div>',
              cls, esc(k), v, s))
}

sec <- function(num, title, hint = "") {
  cat(sprintf('<h2 class="sec"><span class="num">%s</span> %s%s</h2>', num, esc(title),
              if (nzchar(hint)) sprintf('<span class="hint">%s</span>', esc(hint)) else ""))
}

rt_table <- function(headers, rows, align_left = 1, total_row = NULL) {
  cat('<table class="rt"><thead><tr>')
  for (i in seq_along(headers))
    cat(sprintf('<th class="%s">%s</th>', if (i %in% align_left) "l" else "", headers[i]))
  cat('</tr></thead><tbody>')
  for (r in rows) {
    cat('<tr>')
    for (i in seq_along(r))
      cat(sprintf('<td class="%s">%s</td>', if (i %in% align_left) "l sn" else "", r[[i]]))
    cat('</tr>')
  }
  if (!is.null(total_row)) {
    cat('<tr class="tot">')
    for (i in seq_along(total_row))
      cat(sprintf('<td class="%s">%s</td>', if (i %in% align_left) "l" else "", total_row[[i]]))
    cat('</tr>')
  }
  cat('</tbody></table>')
}
```

<!-- ==========================  PAGE 1 — SUMMARY  ========================== -->

<section class="page">

```{r page1}
ph_header("")
meta_strip()

cat(sprintf('<h1 class="title">%s</h1>', esc(sprintf("%s %s — %s progress report",
  trial_short, wp_code, safe(params$report_type, "TMG")))))
cat(sprintf('<p class="sub">%s<br><b>%s:</b> %s &nbsp;·&nbsp; <b>Reporting date:</b> %s &nbsp;·&nbsp; <b>Protocol:</b> %s &nbsp;·&nbsp; <b>Sites reported:</b> %s</p>',
            esc(trial_title), esc(wp_long), esc(wp_design), esc(report_date_str),
            esc(protocol_v), esc(safe(params$selected_sites, "All sites"))))

sec("01", "Recruitment snapshot")
cat('<div class="snap">')
snap_cell("Consented", fmt_int(n_cons),
          sprintf("of %s target · %s", fmt_int(sample_size), fmt_pct(pct_target, 1)), "lilac")
snap_cell("Screened", fmt_int(n_screened),
          sprintf("%s eligible (%s)", fmt_int(n_elig), fmt_pct(pct_elig)), "")
snap_cell("Open sites", fmt_int(n_sites_open),
          sprintf("%s per site per month", fmt_num(rate_site_month, 2)), "")
snap_cell("In follow-up", fmt_int(n_active),
          sprintf("%s withdrawn (%s)", fmt_int(n_wd), fmt_pct(wd_rate, 1)),
          band(retention, 85, 75))
cat('</div>')

sec("02", "Study health", "RAG thresholds are set in Trial Settings → Report content")
cat('<div class="health-strip">')
for (h in health_cards) {
  cat(sprintf('<div class="pc %s"><div class="pct">%s</div><div class="pcv">%s</div><div class="pcb">%s</div><div class="pcs">%s</div></div>',
              h$b, esc(h$title), fmt_pct(h$val, 1), esc(h$sub), band_word(h$b)))
}
cat('</div>')

sec("03", "Screening funnel",
    if (has_form_flags) {
      "screening_complete = 2 is screened; with consent_complete = 2 it is recruited"
    } else "screening_calc = 4 defines eligibility")
cat('<div class="funnel">')
fn_max <- max(c(funnel_values, 1))
fn_subs <- c(
  if (has_form_flags) {
    sprintf("%s with the screening form complete", fmt_int(n_screened))
  } else sprintf("%s records with screening data", fmt_int(n_screened)),
  sprintf("%s of screened · %s ineligible", fmt_pct(pct_elig), fmt_int(n_inelig)),
  sprintf("%s of eligible", fmt_pct(pct_appr)),
  if (has_form_flags) {
    sprintf("%s of approached · %s screened only (consent not complete)",
            fmt_pct(pct_cons), fmt_int(n_scr_only))
  } else sprintf("%s of approached · %s of eligible",
                 fmt_pct(pct_cons), fmt_pct(pct_recruit)))
for (i in seq_along(funnel_labels)) {
  cat(sprintf('<div class="fn-step"><div class="fk">%s</div><div class="fv">%s</div><div class="fs">%s</div><div class="fbar"><span style="width:%.1f%%"></span></div></div>',
              esc(funnel_labels[i]), fmt_int(funnel_values[i]), fn_subs[i],
              100 * funnel_values[i] / fn_max))
}
cat('</div>')
cat(sprintf('<p class="note">Consent is the point of entry to WP4 — there is no randomisation. A participant counts as recruited only when <code>%s</code> and <code>%s</code> are both 2; screened with consent incomplete or blank counts as screened only (%s to date). Registration date is taken from <code>%s</code>; participants with no screening record are excluded from the funnel denominators.</p>',
            esc(F$f_screening), esc(F$f_consent), fmt_int(n_scr_only),
            esc(F$screen_date)))

sec("04", "Key milestones",
    sprintf("%d of %d complete", length(ms_complete), length(ms)))
groups <- unique(vapply(ms, function(m) safe(m$group, "Milestones"), character(1)))
seq_n <- 0
for (g in groups) {
  items <- Filter(function(m) identical(safe(m$group, "Milestones"), g), ms)
  done  <- sum(vapply(items, function(m) identical(m$status, "complete"), logical(1)))
  cat(sprintf('<div class="ml-grp"><div class="ml-grp-h">%s<span class="gpcnt">%d of %d complete</span></div>',
              esc(g), done, length(items)))
  for (m in items) {
    seq_n <- seq_n + 1
    st <- safe(m$status, "upcoming")
    pill <- switch(st, complete = '<span class="pill p-g"><span class="dot"></span>Complete</span>',
                       upcoming = '<span class="pill p-i"><span class="dot"></span>Upcoming</span>',
                       '<span class="pill p-n"><span class="dot"></span>Estimated</span>')
    cat(sprintf('<div class="ml-row"><div class="ml-name"><span class="seq">%d</span>%s</div><div class="ml-date %s">%s</div><div class="ml-st">%s</div></div>',
                seq_n, esc(safe(m$name, "")),
                if (identical(st, "estimated")) "est" else "",
                esc(safe(m$date, "TBC")), pill))
  }
  cat('</div>')
}

pf_footer(1)
```

</section>

<!-- =======================  PAGE 2 — RECRUITMENT  ========================= -->

<section class="page">

```{r page2}
ph_header("Recruitment")
sec("05", "Recruitment against plan")

cat(sprintf('<div class="keyline"><span>Consented: <b>%s</b></span><span>Expected by %s: <b>%s</b></span><span>Against plan: <b>%s</b></span><span>Rate: <b>%s per month</b> (%s per site)</span><span>First registration: <b>%s</b></span><span>Most recent: <b>%s</b></span></div>',
            fmt_int(n_cons), format(today, "%b %y"), fmt_int(expected_to_date),
            fmt_pct(pct_vs_plan, 1), fmt_num(rate_per_month, 1),
            fmt_num(rate_site_month, 2), fmt_date(first_rec), fmt_date(last_rec)))

cat('<div class="row2" style="margin-top:8px">')
cat('<div class="card"><div class="ct">Cumulative recruitment · actual vs plan</div><div class="chart-wrap tall"><canvas id="cumC"></canvas></div></div>')
cat('<div class="card"><div class="ct">Monthly registrations</div><div class="chart-wrap tall"><canvas id="monC"></canvas></div></div>')
cat('</div>')

cat(sprintf('<p class="note">The plan line is a linear ramp to %s over %d months from %s. Set <code>recruitment_start</code>, <code>recruitment_months</code> and <code>sample_size</code> in Trial Settings → Report content to match the agreed recruitment schedule.</p>',
            fmt_int(sample_size), plan_months, format(plan_start, "%b %Y")))

sec("06", "Projection")
proj_txt <- if (!is.na(months_to_target)) {
  sprintf("At the current rate of %s per month, the remaining %s participants would be recruited by <b>%s</b>.",
          fmt_num(rate_per_month, 1), fmt_int(remaining), format(proj_end, "%b %Y"))
} else {
  paste("At the current rate the target would not be reached within ten years,",
        "so no completion date is projected.")
}
cat('<div class="sw-grid">')
cat(sprintf('<div class="sw-cell"><div class="lab2">Recruited to date</div><div class="big">%s<small> / %s</small></div><div class="det">%s of the WP4 target.</div></div>',
            fmt_int(n_cons), fmt_int(sample_size), fmt_pct(pct_target, 1)))
cat(sprintf('<div class="sw-cell"><div class="lab2">Projection</div><div class="det">%s</div><div class="det">Months recruiting: <b>%s</b> · Remaining to target: <b>%s</b> · Sites open: <b>%s</b></div></div>',
            proj_txt, fmt_int(months_active), fmt_int(remaining), fmt_int(n_sites_open)))
cat('</div>')

sec("07", "Recruitment by month")
mt_rows <- list()
show_idx <- which(months_seq <= cur_month)
if (length(show_idx) > 12) show_idx <- tail(show_idx, 12)
for (i in show_idx) {
  mt_rows[[length(mt_rows) + 1]] <- list(
    month_lab[i], fmt_int(month_actual[i]), fmt_int(cum_actual[i]),
    fmt_int(cum_target[i]), fmt_pct(pctg(cum_actual[i], cum_target[i]), 0))
}
if (length(mt_rows)) {
  rt_table(c("Month", "Registered", "Cumulative", "Plan", "% of plan"), mt_rows,
           align_left = 1,
           total_row = list("Total", fmt_int(sum(month_actual)), fmt_int(n_cons),
                            fmt_int(expected_to_date), fmt_pct(pct_vs_plan, 0)))
} else {
  cat('<p class="note">No registrations recorded yet.</p>')
}

pf_footer(2)
```

</section>

<!-- ==================  PAGE 3 — SITES & PARTICIPANTS  ===================== -->

<section class="page">

```{r page3}
ph_header("Sites & participants")
sec("08", "Screening and recruitment by site")

if (!is.null(site_tbl) && nrow(site_tbl) > 0) {
  rows <- lapply(seq_len(nrow(site_tbl)), function(i) list(
    esc(site_tbl$site[i]), fmt_int(site_tbl$screened[i]), fmt_int(site_tbl$eligible[i]),
    fmt_int(site_tbl$approached[i]), fmt_int(site_tbl$consented[i]),
    fmt_pct(site_tbl$rate[i], 0), fmt_date(site_tbl$last[i], "%d %b %y")))
  rt_table(c("Site", "Screened", "Eligible", "Approached", "Consented",
             "Eligible → consented", "Last registration"), rows, align_left = 1,
           total_row = list("All sites", fmt_int(sum(site_tbl$screened)),
                            fmt_int(sum(site_tbl$eligible)),
                            fmt_int(sum(site_tbl$approached)),
                            fmt_int(sum(site_tbl$consented)),
                            fmt_pct(pct_recruit, 0), fmt_date(last_rec, "%d %b %y")))
} else {
  cat('<p class="note">No site identifier in the export — map a site field in Trial Settings → Field mapping to break recruitment down by site.</p>')
}

sec("09", "Participant characteristics", "consented participants")
cat('<div class="demo">')
if (!is.null(age_stats)) {
  cat(sprintf('<div class="chip"><b>%s</b><span>Median age (IQR %s–%s)</span></div>',
              fmt_num(age_stats$median, 0), fmt_num(age_stats$q1, 0), fmt_num(age_stats$q3, 0)))
  cat(sprintf('<div class="chip"><b>%s</b><span>Mean age (range %s–%s)</span></div>',
              fmt_num(age_stats$mean, 1), fmt_num(age_stats$min, 0), fmt_num(age_stats$max, 0)))
} else {
  cat('<div class="chip"><b>—</b><span>Age not available</span></div>')
}
if (!is.null(sex_tbl)) {
  top <- sex_tbl[1, ]
  cat(sprintf('<div class="chip"><b>%s</b><span>%s</span></div>',
              fmt_pct(top$pct, 0), esc(top$label)))
}
cat(sprintf('<div class="chip"><b>%s</b><span>With discharge date recorded</span></div>',
            fmt_int(n_cons - n_no_dc_date)))
cat('</div>')

cat('<div class="row2" style="margin-top:10px">')
cat('<div class="card"><div class="ct">Age distribution</div><div class="chart-wrap"><canvas id="ageC"></canvas></div></div>')
cat('<div class="card"><div class="ct">Aetiology of acute pancreatitis</div><div class="chart-wrap"><canvas id="aetC"></canvas></div></div>')
cat('</div>')

if (!is.null(aetio_tbl)) {
  cat('<p class="lab">Aetiology detail</p>')
  rows <- lapply(seq_len(nrow(aetio_tbl)), function(i) list(
    esc(aetio_tbl$label[i]), fmt_int(aetio_tbl$n[i]), fmt_pct(aetio_tbl$pct[i], 1)))
  rt_table(c("Cause", "n", "% of consented"), rows, align_left = 1)
  if (n_codebook_gaps > 0)
    cat(sprintf('<p class="note">%d coded value(s) on this page have no codebook entry and are shown as raw codes. Add them in Trial Settings → Codebook so they read as labels here.</p>',
                n_codebook_gaps))
}

if (!is.null(eth_tbl)) {
  cat('<p class="lab">Ethnic group</p>')
  rows <- lapply(seq_len(nrow(eth_tbl)), function(i) list(
    esc(eth_tbl$label[i]), fmt_int(eth_tbl$n[i]), fmt_pct(eth_tbl$pct[i], 1)))
  rt_table(c("Ethnic group", "n", "% of consented"), rows, align_left = 1)
}

pf_footer(3)
```

</section>

<!-- ==================  PAGE 4 — DATA COMPLETENESS  ======================== -->

<section class="page">

```{r page4}
ph_header("Data completeness")
sec("10", "CRF completion", "REDCap form status: 2 = complete, 1 = unverified, 0 = incomplete")

cat(sprintf('<div class="keyline"><span>Overall completion: <b>%s</b></span><span>Consented participants: <b>%s</b></span><span>Forms assessed: <b>%s</b></span></div>',
            fmt_pct(form_overall, 1), fmt_int(n_cons),
            if (is.null(form_rows)) "0" else fmt_int(nrow(form_rows))))

if (!is.null(form_rows) && nrow(form_rows) > 0) {
  rows <- lapply(seq_len(nrow(form_rows)), function(i) {
    p <- form_rows$pct[i]
    bar <- sprintf('<div class="pb"><div class="track"><div class="fill" style="width:%.0f%%"></div></div><div class="lbl">%s</div></div>',
                   if (is.na(p)) 0 else p, fmt_pct(p, 0))
    list(esc(form_rows$form[i]), fmt_int(form_rows$due[i]),
         fmt_int(form_rows$complete[i]), fmt_int(form_rows$unverified[i]),
         fmt_int(form_rows$incomplete[i]), fmt_int(form_rows$missing[i]), bar)
  })
  rt_table(c("Form", "Expected", "Complete", "Unverified", "Incomplete",
             "Not started", "% complete"), rows, align_left = 1,
           total_row = list("All forms", fmt_int(sum(form_rows$due)),
                            fmt_int(sum(form_rows$complete)),
                            fmt_int(sum(form_rows$unverified)),
                            fmt_int(sum(form_rows$incomplete)),
                            fmt_int(sum(form_rows$missing)),
                            fmt_pct(form_overall, 0)))
} else {
  cat('<p class="note">No form status fields found in the export.</p>')
}

sec("11", "Withdrawals")
cat('<div class="sw-grid">')
cat(sprintf('<div class="sw-cell %s"><div class="lab2">Retention</div><div class="big">%s</div><div class="det">%s of %s consented participants remain in follow-up.</div></div>',
            if (identical(band(retention, 85, 75), "g")) "ok" else "wd",
            fmt_pct(retention, 1), fmt_int(n_active), fmt_int(n_cons)))
wd_detail <- if (!is.null(wd_tbl)) paste(
  sprintf("<b>%s</b> — %s", vapply(wd_tbl$level, esc, character(1)), fmt_int(wd_tbl$n)),
  collapse = " &nbsp;·&nbsp; ") else "No withdrawals recorded."
cat(sprintf('<div class="sw-cell"><div class="lab2">Withdrawals by level</div><div class="det">%s</div><div class="det">Withdrawal is any non-blank value in <code>%s</code>. Withdrawn participants are removed from PROM denominators from the point of withdrawal.</div></div>',
            wd_detail, esc(F$withdraw)))
cat('</div>')

sec("12", "Data queries and actions")
actions <- list()
if (!is.na(form_overall) && form_overall < 95)
  actions[[length(actions) + 1]] <- sprintf(
    "CRF completion is %s — chase the %s outstanding baseline forms with sites.",
    fmt_pct(form_overall, 1),
    fmt_int(sum(form_rows$due) - sum(form_rows$complete)))
if (n_no_dc_date > 0)
  actions[[length(actions) + 1]] <- sprintf(
    "%s consented participant(s) have no index discharge date, so their follow-up windows cannot be calculated.",
    fmt_int(n_no_dc_date))
if (!is.na(prom_overall) && prom_overall < 80)
  actions[[length(actions) + 1]] <- sprintf(
    "PROM return is %s across all timepoints due — review reminder scheduling (SMS, email, postal).",
    fmt_pct(prom_overall, 1))
if (!is.na(pct_vs_plan) && pct_vs_plan < 90)
  actions[[length(actions) + 1]] <- sprintf(
    "Recruitment is %s of plan — %s behind the expected %s.",
    fmt_pct(pct_vs_plan, 1), fmt_int(max(0, expected_to_date - n_cons)),
    fmt_int(expected_to_date))
if (n_codebook_gaps > 0)
  actions[[length(actions) + 1]] <- sprintf(
    "%d coded value(s) have no codebook entry — add them in Trial Settings → Codebook so reports read as labels.",
    n_codebook_gaps)
if (!length(actions))
  actions[[1]] <- "No actions outstanding: recruitment, data completeness and PROM return are all within threshold."
rows <- lapply(seq_along(actions), function(i) list(sprintf("%d", i), actions[[i]]))
cat('<table class="rt"><thead><tr><th class="l" style="width:28px">#</th><th class="l">Action</th></tr></thead><tbody>')
for (r in rows)
  cat(sprintf('<tr><td class="l sn">%s</td><td class="l">%s</td></tr>', r[[1]], r[[2]]))
cat('</tbody></table>')

pf_footer(4)
```

</section>

<!-- =============  PAGE 5 — FOLLOW-UP, PROMs AND RETENTION  ================ -->

<section class="page">

```{r page5}
ph_header("Follow-up & PROMs")
sec("13", "PROM completion by timepoint",
    "denominator = participants whose window has closed")

cat(sprintf('<div class="keyline"><span>Overall PROM return: <b>%s</b></span><span>6-month return: <b>%s</b></span><span>In follow-up: <b>%s</b></span><span>Follow-up ends at <b>%s months</b> post discharge</span></div>',
            fmt_pct(prom_overall, 1), fmt_pct(prom_m6, 1), fmt_int(n_active),
            esc(fu_months)))

if (!is.null(prom_rows) && nrow(prom_rows) > 0) {
  rows <- lapply(seq_len(nrow(prom_rows)), function(i) {
    p <- prom_rows$pct[i]
    bar <- sprintf('<div class="pb"><div class="track"><div class="fill" style="width:%.0f%%"></div></div><div class="lbl">%s</div></div>',
                   if (is.na(p)) 0 else p, fmt_pct(p, 0))
    list(esc(prom_rows$timepoint[i]),
         if (prom_rows$due[i] == 0) "not yet due" else fmt_int(prom_rows$due[i]),
         fmt_int(prom_rows$complete[i]), fmt_int(prom_rows$partial[i]),
         fmt_int(prom_rows$outstanding[i]), bar)
  })
  rt_table(c("Timepoint", "Due", "Complete", "Partial", "Outstanding", "% returned"),
           rows, align_left = 1,
           total_row = list("All timepoints", fmt_int(sum(prom_rows$due)),
                            fmt_int(sum(prom_rows$complete)),
                            fmt_int(sum(prom_rows$partial)),
                            fmt_int(sum(prom_rows$outstanding)),
                            fmt_pct(prom_overall, 0)))
}

cat('<div class="card" style="margin-top:10px"><div class="ct">PROM return by timepoint</div><div class="chart-wrap tall"><canvas id="promC"></canvas></div></div>')

if (length(wp_outcomes)) {
  sec("14", sprintf("Outcome measures — %s", wp_name),
      if (nzchar(wp_interv)) sprintf("Intervention: %s", wp_interv) else "")
  cat('<table class="rt"><thead><tr><th class="l" style="width:28px">#</th><th class="l">Outcome measure</th></tr></thead><tbody>')
  for (i in seq_along(wp_outcomes))
    cat(sprintf('<tr><td class="l sn">%d</td><td class="l">%s</td></tr>',
                i, esc(wp_outcomes[[i]])))
  cat('</tbody></table>')
}

sec(if (length(wp_outcomes)) "15" else "14", "How these figures are derived")
cat('<table class="rt"><thead><tr><th class="l">Metric</th><th class="l">Definition</th></tr></thead><tbody>')
defs <- list(
  c("Screened", sprintf("Records with a value in <code>%s</code>.", esc(F$screen_calc))),
  c("Eligible", sprintf("<code>%s</code> = 4.", esc(F$screen_calc))),
  c("Approached", sprintf("<code>%s</code> = 1.", esc(F$approached))),
  c("Consented", sprintf("<code>%s</code> = 1 — the point of entry to the cohort.", esc(F$consent))),
  c("Registration date", sprintf("<code>%s</code>, the date the REDCap record was created.", esc(F$screen_date))),
  c("Withdrawn", sprintf("Any non-blank value in <code>%s</code>.", esc(F$withdraw))),
  c("Form complete", "REDCap form status = 2 (complete); 1 counts as unverified, 0 as incomplete, blank as not started."),
  c("PROM due", sprintf("Index discharge date (<code>%s</code>) + timepoint offset + window: day 7 &plusmn;3, day 28 &plusmn;3, 3 and 6 months &plusmn;7 days.", esc(F$dc_date))),
  c("PROM complete", sprintf("Completion flag = 2 in the timepoint's event (<code>%s</code>, <code>%s</code>, <code>%s</code>).",
                             esc(E$d28), esc(E$m3), esc(E$m6))))
for (d in defs)
  cat(sprintf('<tr><td class="l sn">%s</td><td class="l">%s</td></tr>', d[1], d[2]))
cat('</tbody></table>')

cat(sprintf('<p class="note">Prepared by the %s study office (%s) for the Trial Management Group. Figures are drawn from the REDCap export loaded into the dashboard on %s and cover %s. Participants who withdrew are excluded from follow-up denominators; all other percentages use the denominators stated above.</p>',
            esc(trial_short), esc(study_mgr), esc(report_date_str),
            esc(safe(params$selected_sites, "all sites"))))

pf_footer(5)
```

</section>

</div>

<script>
(function(){
  if (typeof Chart === 'undefined') return;
  const lilac = '#4C3A82', mauve = '#9B7FD4', muted = '#7A7391', grid = '#F0ECF9';
  Chart.defaults.font.family = 'Calibri, Segoe UI, system-ui, sans-serif';
  Chart.defaults.font.size = 10;
  Chart.defaults.color = muted;

  const labels = `r j(month_lab)`;
  const target = `r j(cum_target)`;
  const actual = `r j(cum_actual_plot)`;
  const monthly = `r j(month_actual_plot)`;

  const cumEl = document.getElementById('cumC');
  if (cumEl) new Chart(cumEl, {
    type:'line',
    data:{labels: labels, datasets:[
      {label:'Plan', data: target, borderColor:'#CFC4E8', borderDash:[5,4], borderWidth:1.5, pointRadius:0, fill:false, tension:.2},
      {label:'Actual', data: actual, borderColor: lilac, backgroundColor:'rgba(155,127,212,.20)', fill:true, borderWidth:2, pointBackgroundColor: lilac, pointRadius:2.5, tension:.3, spanGaps:false}
    ]},
    options:{responsive:true, maintainAspectRatio:false,
      plugins:{legend:{display:true,labels:{boxWidth:10,boxHeight:10,padding:8,font:{size:9}}}},
      scales:{x:{grid:{display:false},border:{display:false},ticks:{maxRotation:0,autoSkip:true,maxTicksLimit:12}},
              y:{beginAtZero:true,grid:{color:grid},border:{display:false},ticks:{padding:4}}}}
  });

  const monEl = document.getElementById('monC');
  if (monEl) new Chart(monEl, {
    type:'bar',
    data:{labels: labels, datasets:[{data: monthly, backgroundColor: ctx => (ctx.parsed && ctx.parsed.y) ? mauve : '#EFEAF8', borderRadius:4, maxBarThickness:22}]},
    options:{responsive:true, maintainAspectRatio:false,
      plugins:{legend:{display:false},tooltip:{callbacks:{label:c=>(c.parsed.y||0)+' registered'}}},
      scales:{x:{grid:{display:false},border:{display:false},ticks:{maxRotation:0,autoSkip:true,maxTicksLimit:12}},
              y:{beginAtZero:true,grid:{color:grid},border:{display:false},ticks:{stepSize:1,padding:4}}}}
  });

  const ageEl = document.getElementById('ageC');
  if (ageEl) new Chart(ageEl, {
    type:'bar',
    data:{labels: `r j(age_labels_v)`, datasets:[{data: `r j(age_values_v)`, backgroundColor: lilac, borderRadius:4, maxBarThickness:34}]},
    options:{responsive:true, maintainAspectRatio:false, plugins:{legend:{display:false}},
      scales:{x:{grid:{display:false},border:{display:false}},
              y:{beginAtZero:true,grid:{color:grid},border:{display:false},ticks:{stepSize:1,precision:0}}}}
  });

  const aetEl = document.getElementById('aetC');
  if (aetEl) new Chart(aetEl, {
    type:'bar',
    data:{labels: `r j(aetio_labels_v)`, datasets:[{data: `r j(aetio_values_v)`, backgroundColor: mauve, borderRadius:4, maxBarThickness:22}]},
    options:{indexAxis:'y', responsive:true, maintainAspectRatio:false, plugins:{legend:{display:false}},
      scales:{x:{beginAtZero:true,grid:{color:grid},border:{display:false},ticks:{precision:0}},
              y:{grid:{display:false},border:{display:false}}}}
  });

  const promEl = document.getElementById('promC');
  if (promEl) new Chart(promEl, {
    type:'bar',
    data:{labels: `r j(prom_labels)`, datasets:[{data: `r j(prom_pcts)`, backgroundColor: ctx => {
      const v = ctx.parsed ? ctx.parsed.y : null;
      if (v == null) return '#EFEAF8';
      return v >= 80 ? '#2F7F63' : (v >= 60 ? '#B5801F' : '#AE3F44');
    }, borderRadius:4, maxBarThickness:44}]},
    options:{responsive:true, maintainAspectRatio:false,
      plugins:{legend:{display:false},tooltip:{callbacks:{label:c=>(c.parsed.y==null?'not due':c.parsed.y+'% returned')}}},
      scales:{x:{grid:{display:false},border:{display:false}},
              y:{beginAtZero:true,max:100,grid:{color:grid},border:{display:false},ticks:{callback:v=>v+'%'}}}}
  });
})();
</script>
